### 2022-04-04 draft.tex
Deploy to GitHub Pages

%!TEX TS-program = xelatex
\documentclass[11pt]{article}

\usepackage[english]{babel}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stix}
\usepackage[scaled]{helvet}
\usepackage[scaled]{inconsolata}

\usepackage{lastpage}

\usepackage{setspace}

\usepackage{ccicons}

\usepackage[hang,flushmargin]{footmisc}

\usepackage{geometry}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}

\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0pt}\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\makeatletter
\newcounter{tableno}
\newenvironment{tablenos:no-prefix-table-caption}{
  \caption@ifcompatibility{}{
    \let\oldthetable\thetable
    \let\oldtheHtable\theHtable
    \renewcommand{\thetable}{tableno:\thetableno}
    \renewcommand{\theHtable}{tableno:\thetableno}
    \stepcounter{tableno}
    \captionsetup{labelformat=empty}
  }
}{
  \caption@ifcompatibility{}{
    \captionsetup{labelformat=default}
    \let\thetable\oldthetable
    \let\theHtable\oldtheHtable
    \addtocounter{table}{-1}
  }
}
\makeatother

\usepackage{array}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\let\PBS=\PreserveBackslash

\usepackage[breaklinks=true]{hyperref}
\hypersetup{colorlinks,%
citecolor=blue,%
filecolor=blue,%
linkcolor=blue,%
urlcolor=blue}
\usepackage{url}

\usepackage{caption}
\setcounter{secnumdepth}{0}
\usepackage{cleveref}

\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}

\usepackage{longtable}
\usepackage{booktabs}

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for \widthof, \maxof
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\maxof{\widthof{#1}}{\csllabelwidth}}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=4.5cm}

\usepackage{lineno}
\usepackage[nolists,noheads]{endfloat}

\pagestyle{plain}

\doublespacing

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\thispagestyle{empty}
{\Large\bfseries\sffamily Mismatch between IUCN range maps and species
interactions data illustrated using the Serengeti food web}
\vskip 5em

%
\href{https://orcid.org/0000-0003-2791-8383}{Gracielle\,T. Higino}%
%
\,\textsuperscript{1,2,‡}\quad %
\href{https://orcid.org/0000-0001-5030-3470}{Fredric\,M. Windsor}%
%
\,\textsuperscript{3,‡}\quad %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{4,5,6,‡}\quad %
\href{https://orcid.org/0000-0002-2212-3584}{Gabriel\,Dansereau}%
%
\,\textsuperscript{4,6,‡}\quad %
\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
%
\,\textsuperscript{4,6,‡}\quad %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{4,6,‡}

\textsuperscript{1}\,The University of British
Columbia\quad \textsuperscript{2}\,Computational Biodiversity Science
and Services\quad \textsuperscript{3}\,School of Natural and
Environmental Sciences, Newcastle
University\quad \textsuperscript{4}\,Université de
Montréal\quad \textsuperscript{5}\,Université de
Sherbrooke\quad \textsuperscript{6}\,Quebec Centre for Biodiversity
Science

\textsuperscript{‡}\,These authors contributed equally to the work\\

\textbf{Correspondance to:}\\
Gracielle T. Higino --- \texttt{graciellehigino@gmail.com}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\

\vfill
This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
Last revision: \emph{\today}

\clearpage
\thispagestyle{empty}

\vfill
\textbf{\sffamily Abstract: }Range maps are a useful tool to describe
the spatial distribution of species. However, they often need to be used
with caution, as they essentially represent a rough approximation of a
species' suitable habitats. When stacked together, the resulting
communities in each grid cell may not always be realistic, especially
when species interactions are taken into account. Here we show the
extent of the mismatch between range maps, provided by the International
Union for Conservation of Nature, and species interactions data. More
precisely, we show that local networks built from those stacked range
maps often yield unrealistic communities, where species of higher
trophic levels are completely disconnected from primary producers. We
use the well-described Serengeti food web of mammals and plants as our
case study, and provide updated range maps that take into account
food-web structure. In our analysis, most predator ranges were
restricted by the absence of herbivores. This restriction was sometimes
contradicted by GBIF occurrences, suggesting the mismatch can be due
either to the lack of information about ecological interactions or about
the geographical occurrence of preys. We finally discuss general
guidelines to help identify defective data among distributions and
interactions data, and we recommend this method as a valuable way to
assess weather the occurrence data that are being used, even if
incomplete, is ecologically accurate.
\vfill

\clearpage
\linenumbers
\pagestyle{normal}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Finding a species in a certain location is like finding an encrypted
message that travelled through time. It carries the species'
evolutionary history, migration patterns, as well as any direct and
indirect effects generated by other species (some of which we may not
even know exist). Ecologists have been trying to decode this message
with progressively more powerful tools, from their own field notes to
highly complex computational algorithms. However, to succeed in this
challenge it is important to have the right clues in hand. There are
many ways we can be misled by data - or the lack of it: taxonomic
errors, geographic inaccuracy, or sampling biases (Ladle and Hortal
2013; Hortal et al. 2015; Poisot et al. 2021). One way to identify - and
potentially fix - these errors is to combine many different pieces of
information about the occurrence of a species, so agreements and
mismatches can emerge. Here we suggest jointly analysing species
occurrence (range maps and point occurrences) and ecological
interactions to identify mismatches between datasets.

Interactions form complex networks that shape ecological structures and
maintain the essential functions of ecosystems, such as seed dispersal,
pollination, and biological control (Albrecht 2018; Fricke et al. 2022)
that ultimately affect the composition, richness, and successional
patterns of communities across biomes. Yet, the connection between
occurrence and interaction data is a frequent debate in ecology
(Blanchet, Cazelles, and Gravel 2020). For instance, macroecological
models are often used with point or range occurrence data in order to
investigate the dynamics of a species with its environment. However,
these models do not account for ecological interactions, which might
largely affect species distribution (Abrego et al., n.d.; Afkhami,
McIntyre, and Strauss 2014; Araújo, Marcondes-Machado, and Costa 2014;
Godsoe et al. 2017; Godsoe and Harmon 2012). Some researchers argue that
occurrence data can also capture real-time interactions (Roy et al.
2016; Ryan et al. 2018), and, because of that, it would not be necessary
to include ecological interaction dynamics in macroecological models. On
the other hand, many mechanistic simulation models in ecology have
considered the effect of competition and facilitation in range shifts,
whilst the use of trophic interactions in this context remains
insufficient (Cabral, Valente, and Hartig 2017).

A significant challenge in this debate is the quality and quantity of
species distribution and ecological data (Boakes et al. 2010; Ronquillo
et al. 2020; Meyer, Weigelt, and Kreft 2016) - a gap that can lead to
erroneous conclusions in macroecological research (Hortal et al. 2008).
Amongst the geographical data available are the range maps provided by
the International Union for the Conservation of Nature (IUCN). Such maps
consist of simplified polygons, often created as alpha or convex hulls
around known species locations, refined by expert knowledge about the
species (2021). These maps can be used in macroecological inferences in
the lack of more precise information (Fourcade 2016; Alhajeri and
Fourcade 2019), but it has been recommended that they are used with
caution since they tend to underestimate the distribution of species
that are not well-known (Herkt, Skidmore, and Fahr 2017), do not
represent spatial variation in species occurrence and abundance (Dallas,
Pironon, and Santini 2020), and can include inadequate areas within the
estimated range. Another source of species distribution information is
the Global Biodiversity Information Facility (GBIF), which is an online
repository of georeferenced observational records that come from various
sources, including community science programs, museum collections, and
long-term monitoring schemes. A great source of bias in these datasets
is the irregular sampling effort, with more occurrences originated from
attractive and accessible areas and observation of charismatic species
(Alhajeri and Fourcade 2019). As for ecological data, a complete
assessment is difficult and is aggravated by biased sampling methods and
data aggregation (Poisot et al. 2020; Hortal et al. 2015). Nevertheless,
we have witnessed an increase in the availability of biodiversity data
in the last decades, including those collected through community science
projects (Callaghan et al. 2019; Pocock et al. 2015) and dedicated
databases, such as Mangal (Poisot et al. 2016). This provides an
opportunity to merge species distribution and ecological interaction
data to improve our predictions of where a species may be found across
large spatial scales (e.g., continental and global).

In this context, we elaborate a method that allows us to refine
distribution data (more precisely range maps) based on interaction data,
considering the basic assumption that predators can only be present in
regions where they are connected to at least one herbivore - and thus
indirectly connected to primary producers. We used a Serengeti food web
dataset (Baskerville et al. 2011) (which comprises carnivores,
herbivores, and plants from Tanzania) to demonstrate how a mismatch
between occurrence and interaction data can highlight significant
uncertainty areas in IUCN range maps. Finally, we add the GBIF
occurrence points for the Serengeti species to the investigation,
discuss the mechanisms that can lead to the lack of agreement between
data, and build from that a vision for the next steps, reinforcing the
importance of geographically explicit interaction data.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

Organisms cannot persist unless they are directly or indirectly
connected to a primary producer within their associated food web (Power
1992). Therefore, the range of a predator (omnivore or carnivore)
depends on the overlapping ranges of its preys. If sections of a
predator's range does not overlap with at least one of its prey it will
become disconnected from primary producers, and therefore we would not
expect the predator to occur in this area. This mismatch can be the
result of different mechanisms, like the overestimation of the
predator's range, taxonomic errors, or the lack of information about
trophic links. Thus, given that herbivores are the main connection
between plant resources (directly limited by environmental conditions)
and predators (Dobson 2009; Scott et al. 2018), here we adjusted the
ranges of predators based on a simple rule: we removed any part of a
predator's range that did not intersect with the range of at least one
prey herbivore species. So, unless the range of the predator overlapped
with at least one prey item, which in turn is directly connected to a
primary producer (plants), we removed that section of the predator's
range. Finally, we calculated the difference in range size between the
original IUCN ranges and those adjusted based on species interaction
data.

\hypertarget{data}{%
\subsection{Data}\label{data}}

We investigated the mismatch between savannah species ranges and
interactions in Africa (fig.~\ref{fig:richness}). These ecosystems host
a range of different species, including the well characterized
predator-prey dynamics between iconic predators (e.g., lions, hyenas and
leopards) and large herbivores (e.g., antelopes, wildebeests and
zebras), as well as a range of herbivorous and carnivorous small
mammals. The Serengeti ecosystem has been extensively studied and its
food web is one of the most complete we have to date, including primary
producers identified to the species level. Here we focus on six groups
of herbivores and carnivores from the Serengeti Food Web Data Set
(Baskerville et al. 2011). These species exhibit direct antagonistic
(predator-prey) interactions with one another and are commonly found
across savannah ecosystems on the African continent (McNaughton 1992).
Plants in the network were included indirectly in our analyses as we do
not expect the primary producers to significantly influence the range of
herbivores for several reasons. Firstly, many savannah plants are
functionally similar (i.e., grasses, trees and shrubs) and cooccur
across the same habitats (Baskerville et al. 2011). Secondly, herbivores
in the network are broadly generalists feeding on a wide range of
different plants across habitats. Indeed, out of 129 plants in our
dataset, herbivores (n = 23) had a mean out degree (mean number of
preys) of around 22 (std = 17.5). There is also an absence of global
range maps for many plant species (Daru 2020), which prevents their
direct inclusion in our analysis. Therefore, we assume that plants
consumed by herbivores are present across their ranges, and as such the
ranges of herbivores are not expected to be significantly constrained by
the availability of food plants.

From the wider ecological network presented in Baskerville (2011), we
sampled interaction data for herbivores and carnivores. This subnetwork
contained 32 taxa (23 herbivores and 9 carnivores) and 84 interactions,
and had a connectance of 0.08. Although self-loops are informative, we
removed these interactions to allow for the original IUCN ranges of
predators with cannibalistic interactions to be adjusted. We treated
this overall network as a metaweb since it \emph{should} contain all
potential species interactions between mammalian taxa occurring across
savannah ecosystems such as the Serengeti.

We compiled IUCN range maps for the 32 species included in the metaweb
from the Spatial Data Download portal
(www.iucnredlist.org/resources/spatial-data-download), which we
rasterized at 10 arc-minute resolution (\textasciitilde19 km² at the
equator). We then combined interaction data from the metaweb and
cooccurrence data generated from species ranges to create networks for
each raster pixel. This generated a total of 84,244 pixel-level
networks. These networks describe potential predation, not actual
interactions: the former is derived information from the metaweb, and
the later is contingent to the presence of herbivores.

\hypertarget{range-overlap-measurement}{%
\subsection{Range overlap measurement}\label{range-overlap-measurement}}

We calculated the geographical overlap, i.e.~the extent to which
interacting predator and prey species cooccurred across their ranges, as
\(a/(a + c)\), where \(a\) is the number of pixels where predator and
prey cooccur and \(c\) is the number of pixels where only the focal
species occur. This index of geographical overlap can be calculated with
prey or predators as the focal species. Values vary between 0 and 1,
with values closer to 1 indicating that there is a large overlap in the
ranges of the two species and values closer to 0 indicating low
cooccurrence across their ranges. For each predator species we
calculated its generality to understand whether the level of trophic
specialization (i.e., number of prey items per predator) affects the
extent to which the ranges of the species were altered. One would assume
that predators with a greater number of prey taxa (i.e., a higher
generality) are less likely to have significant changes in their range
as it is more likely that at least one prey species is present across
most of their range.

\hypertarget{validation}{%
\subsection{Validation}\label{validation}}

For each species in the dataset we collated point observation data from
GBIF (www.gbif.org), and condensed these data into pixels representing
presence or absence of the focal taxon. These data were used to validate
the range adjustments made based on species interactions (see previous
section). To do so, we calculated the proportion of GBIF presence pixels
occurring within both the original and adjusted species ranges. We then
compared these proportions for the predators to verify if the range
adjustments removed locations with GBIF observations, hence likely true
habitats.

\hypertarget{results}{%
\section{Results}\label{results}}

Mammal species found in the Serengeti food web are widespread in Africa,
especially in grasslands and savannahs (first panel of
fig.~\ref{fig:richness}). However, most local networks (83.2\%) built
using the original IUCN range maps had at least one mammal species
without a path to a primary producer (second panel of
fig.~\ref{fig:richness}). On average, local food webs had almost the
third of their mammal species (mean = 30.5\%, median = 14.3\%)
disconnected from basal species. In addition, many networks (16.6\%)
only had disconnected mammals; these networks however all had a very low
number of mammal species, specifically between 1 and 4 (from a total of
32). As expected, the proportion of carnivores with a path to a primary
producer was conditional on the total number of mammal species in each
local network (third panel of fig.~\ref{fig:richness}).

\begin{figure}
\hypertarget{fig:richness}{%
\centering
\includegraphics{figures/richness_prop_removed.png}
\caption{(a) Spatial distribution of species richness according to the
original IUCN range maps of all 32 mammal species of the Serengeti food
web. (b) Proportion of mammal species remaining in each local network
(i.e., each pixel) after removing all species without a path to a
primary producer. (c) Proportion of mammal species remaining in each
local network as a function of the number of species given by the
original IUCN range maps.}\label{fig:richness}
}
\end{figure}

\hypertarget{specialized-predators-lose-more-range}{%
\subsection{Specialized predators lose more
range}\label{specialized-predators-lose-more-range}}

\begin{figure}
\hypertarget{fig:degree}{%
\centering
\includegraphics{figures/rel_loss-outdegree-species.png}
\caption{Negative relationship between the out degree of predator
species and their relative range loss. More specialized predators lose a
higher proportion of their ranges due to mismatches with the ranges of
their preys.}\label{fig:degree}
}
\end{figure}

Predators with less preys lose more range with our method
(fig.~\ref{fig:degree}). For instance, both \emph{Leptailurus serval}
and \emph{Canis mesomelas} have only one prey in the Serengeti food web
(tbl.~\ref{tbl:everyone}), each of them with a very small range compared
to those of their predator. This discrepancy between range sizes
promotes significant range loss. On the other hand, predators of the
genus \emph{Panthera} are some of the most connected species, and they
also lose the least proportion of their ranges. This mismatch between
predators and preys can also be a result of taxonomic disagreement
between the geographical and ecological data. Although \emph{Canis
aureus} has the same number of prey as \emph{Caracal caracal}, none of
the prey taxa of the former occurs inside its original range
(tbl.~\ref{tbl:everyone}), which results in complete range loss.

\begin{figure}
\hypertarget{fig:geo_diss}{%
\centering
\includegraphics{figures/beta-div_pred-species.png}
\caption{Geographical similarity between the original IUCN range maps of
predators and preys. Dots represent predator-prey pairs, with different
symbols corresponding to different predators. For a given pair of
species, the number \(c\) of pixels where the focal species is present
but not the other and the number \(a\) of pixels where the predator and
prey cooccur, were calculated. Geographic similarities were given by
\(a/(a+c)\), with the predator being the focal species in the predator
to prey similarity (x-axis), while the prey is the focal one in the prey
to predator similarity (y-axis). One of the predators, \emph{Canis
aureus}, is not represented in the image because it is an extreme case
(where all its range is suppressed by the absence of preys) and it would
make the interpretation of the data more difficult.}\label{fig:geo_diss}
}
\end{figure}

There was high variation in the overlap of predator and prey ranges
(fig.~\ref{fig:geo_diss}). The high density of points on left-hand side
of fig.~\ref{fig:geo_diss} indicates that most preys have small ranges
in comparison to those of the set of carnivores in the networks,
resulting in either low overlap between both ranges (bottom) or high
overlap of ranges because much of that of the prey is within predators'
range (top). The top-right side of the plot encompasses situations where
the ranges of both predator and prey are similar and overlapping, while
the bottom-right part of the plot represents a situation where the range
of the predator is smaller than that of its prey and much of it occurs
within the preys' range. For example, \emph{Panthera pardus} had many
preys occurring inside its range, with highly variable levels of overlap
(tbl.~\ref{tbl:everyone}). In general, species exhibited more consistent
values of prey-predator overlap, than predator-prey overlap -- indicated
by the spread of points along the x-axis, yet more restricted variation
on the y-axis (fig.~\ref{fig:geo_diss}). There was also no overall
relationship between the two metrics, or for any predator species.

\hypertarget{tbl:everyone}{}
\begin{longtable}[]{@{}lrrrrr@{}}
\caption{\label{tbl:everyone}List of species analyzed, their out and in
degrees, total original range size (in pixels) and proportion of their
ranges occupied by their preys and predators (values between 0 and 1).
Species are sorted according to the groups identified by Baskerville et
al. (2011). Notice how some species are isolated in the network
(\emph{Loxodonta africana}) and how \emph{Canis aureus}'s range do not
overlap with any of its preys.}\tabularnewline
\toprule
\begin{minipage}[b]{0.28\columnwidth}\raggedright
Species\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedleft
Number of preys\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedleft
Number of predators\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedleft
Total range size\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\raggedleft
Proportion of range occupied by preys\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\raggedleft
Proportion of range occupied by predators\strut
\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.28\columnwidth}\raggedright
Species\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedleft
Number of preys\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedleft
Number of predators\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedleft
Total range size\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\raggedleft
Proportion of range occupied by preys\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\raggedleft
Proportion of range occupied by predators\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.28\columnwidth}\raggedright
\textbf{Large carnivores}\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Acinonyx jubatus\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
8\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
1\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
15540\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.560\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.670\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Crocuta crocuta\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
12\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
1\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
43307\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.848\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.252\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Lycaon pictus\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
14\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
3873\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.916\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Panthera leo\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
18\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
11384\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.934\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Panthera pardus\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
22\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
68137\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.766\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
\textbf{Small carnivores}\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Canis aureus\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
4\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
1\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
7358\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.000\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.780\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Canis mesomelas\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
1\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
1\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
19872\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.190\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.995\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Caracal caracal\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
4\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
47243\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.832\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Leptailurus serval\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
1\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
1\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
38856\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.011\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.979\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
\textbf{Small herbivores}\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Damaliscus lunatus\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
4\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
5567\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
1\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Hippopotamus amphibius\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
3695\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Kobus ellipsiprymnus\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
4\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
26705\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
1\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Ourebia ourebi\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
5\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
22380\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
1\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Pedetes capensis\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
2\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
11901\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
1\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Phacochoerus africanus\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
5\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
29963\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.999\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Redunca redunca\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
5\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
17465\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
1\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Rhabdomys pumilio\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
5\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
465\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.998\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Tragelaphus oryx\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
2\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
20852\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.991\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Tragelaphus scriptus\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
3\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
36011\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.984\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
\textbf{Large grazers}\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Aepyceros melampus\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
5\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
10579\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
1\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Alcelaphus buselaphus\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
4\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
20761\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
1\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Connochaetes taurinus\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
6\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
9650\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
1\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Equus quagga\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
5\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
7070\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
1\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Eudorcas thomsonii\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
6\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
463\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
1\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Nanger granti\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
6\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
2303\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
1\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
\textbf{Hyraxes}\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Heterohyrax brucei\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
1\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
17728\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.972\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Procavia capensis\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
1\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
47697\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.647\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
\textbf{Others}\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Giraffa camelopardalis\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
1\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
5418\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.470\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Loxodonta africana\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
9654\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Madoqua kirkii\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
7\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
4002\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
1\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Papio anubis\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
1\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
23171\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.938\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.28\columnwidth}\raggedright
Syncerus caffer\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
0\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
1\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
25223\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
0.250\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{validation-with-gbif-occurrences}{%
\subsection{Validation with GBIF
occurrences}\label{validation-with-gbif-occurrences}}

The proportion of GBIF pixels (pixels with at least one GBIF occurrence)
falling in the IUCN ranges varied from low to high depending on the
species (fig.~\ref{fig:gbif}, left). The lowest proportions occurred for
species with small ranges (such as \emph{Lycaon pictus}), although some
species with small ranges showed high overlap. Species with median and
large ranges had high proportions of occurrences falling into their IUCN
range. Predators and preys displayed similar overlap variations. While
no species had all of its GBIF occurrences within its IUCN range, one
species had this proportion equal to zero, \emph{Canis aureus}, which is
also the only species whose range is not covered by any of its preys.
This result reinforces the concern raised in the literature on the use
of IUCN range maps for species that are not well known (Herkt, Skidmore,
and Fahr 2017), demonstrating how small range species are likely to have
their distribution underestimated in the IUCN database. Additionally,
the fact that \emph{Canis aureus} had none of its GBIF pixels
overlapping with IUCN maps suggests a taxonomic mismatch between both
databases, which we explore in the Discussion section.

The proportion of GBIF pixels in updated ranges can only be equal to or
lower than that of the original ranges, as our analysis removes pixels
from the original range and does not add new ones. Rather, the absence
of a difference between the two types of ranges indicates that no pixels
with GBIF observations, hence likely true habitats, were removed by our
analysis. Here this proportion was mostly similar to that of the
original IUCN ranges for most predator species (fig.~\ref{fig:gbif}).
Four species showed no difference of proportion while three species
showed only small differences (proportions of 0.01 to 0.05). On the
other hand, two species, \emph{Canis mesomelas} and \emph{Leptailurus
serval}, showed very high differences, with overlaps lower by 0.548 and
0.871 respectively. For \emph{Leptailurus serval}, none of the GBIF
observations occurred in the updated range. These two species are also
the only predators with a single prey in our metaweb. Our results
delineate how a mismatch between GBIF and IUCN databases differ greatly
with small changes in herbivore species ranges, and it is somewhat
positively related to range size for predator species. Moreover, we show
that accounting for interactions does not necessarily aggravates this
dissimilarity, but it is relevant for species with little ecological
information or specialists.

\begin{figure}
\hypertarget{fig:gbif}{%
\centering
\includegraphics{figures/gbif_panels.png}
\caption{Left panel: Distribution of the proportion of GBIF pixels
(pixels with at least one occurrence in GBIF) falling into the IUCN
range for different range sizes. Right panel: Differences between the
proportion of GBIF pixels falling into the IUCN and the updated ranges
for every predator species. Arrows go from the proportion inside the
original range to the proportion inside the updated range, which can
only be equal or lower. Overlapping markers indicate no difference
between the types of layers. Species markers are the same on both
figures, with predators presented in distinct colored markers and all
herbivores grouped in a single grey marker. Pixels represent a
resolution of 10 arc-minutes.}\label{fig:gbif}
}
\end{figure}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

The jackal is a widespread taxon in northern Africa, Europe and
Australasia, generally well adapted to local conditions due to its
largely varied diet (Tsunoda and Saito 2020; Krofel et al. 2021).
Because of that, we expected that the \emph{Canis} species in our
dataset would be the ones losing the least amount of range, with a
higher value of the proportion of GBIF pixels within their IUCN range
maps. However, the taxonomy of this group is a matter of intense
discussion, as molecular and morphological data seem to disagree in the
clustering of species and subspecies (Krofel et al. 2021; Stoyanov
2020). This debate is indeed reflected in our analysis: the GBIF
identification of the golden jackal is incompatible with the one used by
IUCN, each of them mapping its distribution in completely different
places. This led to a complete exclusion of \emph{Canis aureus} from its
original range in our analysis, despite the fact that this species has
four documented preys in our metaweb. This example illustrates how the
taxonomic, geographical and ecological data can be used to validate one
another.

Here we show that when ecological interaction data (predator-prey
interactions within food webs) are used to refine species range maps,
there are significant reductions in the IUCN range size of predatory
organisms. Despite showing the potential importance in accounting for
species interactions when estimating the range of a species, it remains
unclear the extent to which the patterns observed represent ecological
processes or a lack of data. In the following sections we discuss the
implications of our findings, in terms of species range maps,
interaction data and the next steps required to enhance understanding of
species distributions using information on ecological networks.

\hypertarget{connectivity-diversity-and-range-preservation}{%
\subsection{Connectivity, diversity and range
preservation}\label{connectivity-diversity-and-range-preservation}}

In the Serengeti food web there is a positive relationship between the
out degrees of predators and the size of their ranges
(tbl.~\ref{tbl:everyone}). In addition, our results show that there is a
negative relationship between the relative loss of predators' ranges and
their number of preys (fig.~\ref{fig:degree}), reinforcing the idea that
generalist species can preserve their distributions longer while losing
interactions. The factors limiting the geographical range of a species
in a community can vary with connectivity and richness (Svenning et al.
2014). Younger communities may be more affected by environmental
limitations because they are dominated by generalist species, while
older metacommunities are probably affected in different ways in the
centre of the distribution, at the edge of ranges and in sink and source
communities (Svenning et al. 2014; Godsoe et al. 2017; Cazelles et al.
2016; Bullock et al. 2000). Additionally, it is likely that species with
larger ranges of distribution and those that are more generalists would
co-occur with a greater number of other species (Dáttilo et al. 2020),
while dispersal capacity of competitive species modulate their
aggregation in space and the effect of interactions on their range
limits (Godsoe et al. 2017).

\hypertarget{geographical-mismatch-and-data-availability}{%
\subsection{Geographical mismatch and data
availability}\label{geographical-mismatch-and-data-availability}}

The geographical mismatch between predators and preys have ecological
consequences such as loss of ecosystem functioning and extinction of
populations (Anderson et al. 2016; Dáttilo and Rico-Gray 2018; Pringle
et al. 2016; Young et al. 2013). Climate change is one of the causes of
this, leading, for instance, to the decrease of plants populations due
to the lack of pollination (Bullock et al. 2000; Afkhami, McIntyre, and
Strauss 2014; Godsoe et al. 2017). However, this mismatch can also be
purely informational. When the distribution of predators and preys do
not superpose, it can mean we lack information about the distribution of
either species or about their interactions (e.g., predators may be
feeding on different species than the ones in our dataset outside the
Serengeti ecosystem). Here we addressed part of this problem by
comparing the IUCN range maps with GBIF occurrences, which helped us
clarify what is the shortfall for each species.

The lack of superposition between IUCN range maps and GBIF occurrences
suggests that we certainly do miss geographical information about the
distribution of a certain species, but it is not an indicative about the
completeness of the information about ecological interactions. However,
if both GBIF and IUCN occurrences tend to superpose and still the
species is locally removed, this indicates we don't have information
about all its interactions. The combination of this rationale with our
method of updating range maps based on ecological interactions allows us
to have a clearer idea of which information we are missing. For example,
the lion (\emph{Panthera leo}) was one of the species with the smallest
difference between the original and the updated ranges
(fig.~\ref{fig:degree}), but 59.5\% of the GBIF occurrences for this
species fell outside the IUCN range (fig.~\ref{fig:gbif}). In this
particular case, the IUCN maps seem to agree with species interactions
data. However, the disagreement between the IUCN and the GBIF databases
is concerning and suggests that the IUCN maps might underestimate the
lion's distribution. On the other hand, \emph{Leptailurus serval} and
\emph{Canis mesomelas} are two of the three species that lose the higher
proportion of range due to the lack of paths to a herbivore
(fig.~\ref{fig:degree}), but are also some of the species with the
higher proportion of GBIF occurrences inside IUCN range maps
(fig.~\ref{fig:gbif}). This indicates that the information we are
missing for these two species is related to either the occurrence of an
interaction or the presence of interacting species. To illustrate that,
we mapped the GBIF data for the prey of \emph{Leptailurus serval}, with
a mobility buffer around each point (fig.~\ref{fig:serval}). When
considering GBIF data, approximately 53\% of the prey's occurrences are
within the portion of the serval's range that was lost. With the buffer
area, this corresponds to 13\% of the lost range. This means that by
adding GBIF information, we would reduce the loss of range (or
information) for the predator by 13\% since its distribution is
conditional on the occurrence of its preys.

\begin{figure}
\hypertarget{fig:serval}{%
\centering
\includegraphics{figures/serval_mismatch_combined.png}
\caption{Mismatch between serval's range loss and GBIF occurrence of its
prey. The left panel shows the reduction of serval's range when we
consider the IUCN data on its prey. On the right panel, we added GBIF
data on both serval and its prey, with a buffer for the prey to account
on species mobility.}\label{fig:serval}
}
\end{figure}

Finally, the extreme case of \emph{Canis aureus} illustrates a lack of
both geographical and ecological information: none of its GBIF
occurrences and none of its preys occur inside its IUCN range. We
believe, therefore, that the validation of species distribution based on
ecological interaction is a relevant method that can further fill in
information gaps. Nevertheless, it is imperative that more
geographically explicit data about ecological networks and interactions
become available. This would help clarify when cooccurrences can be
translated into interactions and help the development of more advanced
validation methods for occurrence data.

\hypertarget{next-steps}{%
\subsection{Next steps}\label{next-steps}}

Here we demonstrated how we can detect uncertainty in species
distribution data using ecological interactions. Knowing where
questionable occurrence data are can be crucial in ecological modelling
(Hortal 2008; Ladle and Hortal 2013), and accounting for these errors
can improve model outputs by diminishing the error propagation (Draper
1995). For instance, we believe this is a way to account for ecological
interactions in habitat suitability models without making the models
more complex, but making sure (not assuming) that the input data - the
species occurrence - actually accounts for ecological interactions. It
is important to notice, however, that the quality and usefulness of this
method is highly correlated with the amount and quality of data
available about species' occurrences \textbf{and} interactions. With
this paper we hope to add to the collective effort to decode the
encrypted message that is the occurrence of a species in space and time.
A promising avenue that adds to our method is the prediction of networks
and interactions in large scales (Strydom et al. 2021), for they can add
valuable information about ecological interactions where they are
missing. Additionally, in order to achieve a robust modelling framework
towards actual species distribution models we should invest in efforts
to collect and combine open data on species occurrence and interactions,
especially because we may be losing ecological interactions at least as
fast as we are losing species (Valiente-Banuet et al. 2015).

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

We acknowledge that this study was conducted on land within the
traditional unceded territory of the Saint Lawrence Iroquoian,
Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak nations. GH,
FB, GD, and NF are funded by the NSERC BIOS\(^2\) CREATE program; FB,
NF, and TP are funded by IVADO; NF and TP are funded by a donation from
the Courtois Foundation; GD is funded by the FRQNT doctoral scholarship;
TP is funded by the Canadian Institute of Ecology \& Evolution; FW is
funded by the Royal Society (Grant number:
CHL\textbackslash R1\textbackslash180156).

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-AbregoAccSpe}{}%
Abrego, Nerea, Tomas Roslin, Tea Huotari, Yinqiu Ji, Niels Martin
Schmidt, Jiaxin Wang, Douglas W. Yu, and Otso Ovaskainen. n.d.
{``Accounting for Species Interactions Is Necessary for Predicting How
Arctic Arthropod Communities Respond to Climate Change.''}
\emph{Ecography} n/a (n/a). \url{https://doi.org/10.1111/ecog.05547}.

\leavevmode\hypertarget{ref-Afkhami2014MutEff}{}%
Afkhami, Michelle E., Patrick J. McIntyre, and Sharon Y. Strauss. 2014.
{``Mutualist-Mediated Effects on Species' Range Limits Across Large
Geographic Scales.''} \emph{Ecology Letters} 17 (10): 1265--73.
\url{https://doi.org/10.1111/ele.12332}.

\leavevmode\hypertarget{ref-Albrecht2018PlaAni}{}%
Albrecht, Jörg. 2018. {``Plant and Animal Functional Diversity Drive
Mutualistic Network Assembly Across an Elevational Gradient.''}
\emph{NATURE COMMUNICATIONS}, 10.

\leavevmode\hypertarget{ref-Alhajeri2019HigCor}{}%
Alhajeri, Bader H, and Yoan Fourcade. 2019. {``High Correlation Between
Species-Level Environmental Data Estimates Extracted from IUCN Expert
Range Maps and from GBIF Occurrence Data.''} \emph{Journal of
Biogeography}, 13. \url{https://doi.org/10.1111/jbi.13619}.

\leavevmode\hypertarget{ref-Anderson2016SpaDis}{}%
Anderson, T. Michael, Staci White, Bryant Davis, Rob Erhardt, Meredith
Palmer, Alexandra Swanson, Margaret Kosmala, and Craig Packer. 2016.
{``The Spatial Distribution of African Savannah Herbivores: Species
Associations and Habitat Occupancy in a Landscape Context.''}
\emph{Philosophical Transactions of the Royal Society B: Biological
Sciences} 371 (1703): 20150314.
\url{https://doi.org/10.1098/rstb.2015.0314}.

\leavevmode\hypertarget{ref-Araujo2014ImpBio}{}%
Araújo, Carlos B. de, Luiz Octavio Marcondes-Machado, and Gabriel C.
Costa. 2014. {``The Importance of Biotic Interactions in Species
Distribution Models: A Test of the Eltonian Noise Hypothesis Using
Parrots.''} \emph{Journal of Biogeography} 41 (3): 513--23.
\url{https://doi.org/10.1111/jbi.12234}.

\leavevmode\hypertarget{ref-Baskerville2011SpaGui}{}%
Baskerville, Edward B., Andy P. Dobson, Trevor Bedford, Stefano
Allesina, T. Michael Anderson, and Mercedes Pascual. 2011. {``Spatial
Guilds in the Serengeti Food Web Revealed by a Bayesian Group Model.''}
\emph{PLOS Computational Biology} 7 (12): e1002321.
\url{https://doi.org/10.1371/journal.pcbi.1002321}.

\leavevmode\hypertarget{ref-Blanchet2020CooNot}{}%
Blanchet, F. Guillaume, Kevin Cazelles, and Dominique Gravel. 2020.
{``Co-Occurrence Is Not Evidence of Ecological Interactions.''}
\emph{Ecology Letters} 23 (7): 1050--63.
\url{https://doi.org/10.1111/ele.13525}.

\leavevmode\hypertarget{ref-Boakes2010DisVie}{}%
Boakes, Elizabeth H., Philip J. K. McGowan, Richard A. Fuller, Ding
Chang-qing, Natalie E. Clark, Kim O'Connor, and Georgina M. Mace. 2010.
{``Distorted Views of Biodiversity: Spatial and Temporal Bias in Species
Occurrence Data.''} \emph{PLOS Biology} 8 (6): e1000385.
\url{https://doi.org/10.1371/journal.pbio.1000385}.

\leavevmode\hypertarget{ref-Bullock2000GeoSep}{}%
Bullock, James M., Rebecca J. Edwards, Peter D. Carey, and Rob J. Rose.
2000. {``Geographical Separation of Two Ulex Species at Three Spatial
Scales: Does Competition Limit Species' Ranges?''} \emph{Ecography} 23
(2): 257--71. \url{https://doi.org/10.1111/j.1600-0587.2000.tb00281.x}.

\leavevmode\hypertarget{ref-Cabral2017MecSim}{}%
Cabral, Juliano Sarmento, Luis Valente, and Florian Hartig. 2017.
{``Mechanistic Simulation Models in Macroecology and Biogeography:
State-of-Art and Prospects.''} \emph{Ecography} 40 (2): 267--80.
\url{https://doi.org/10.1111/ecog.02480}.

\leavevmode\hypertarget{ref-Callaghan2019ImpBig}{}%
Callaghan, Corey T., Jodi J. L. Rowley, William K. Cornwell, Alistair G.
B. Poore, and Richard E. Major. 2019. {``Improving Big Citizen Science
Data: Moving Beyond Haphazard Sampling.''} \emph{PLOS Biology} 17 (6):
e3000357. \url{https://doi.org/10.1371/journal.pbio.3000357}.

\leavevmode\hypertarget{ref-Cazelles2016IntBio}{}%
Cazelles, Kévin, Nicolas Mouquet, David Mouillot, and Dominique Gravel.
2016. {``On the Integration of Biotic Interaction and Environmental
Constraints at the Biogeographical Scale.''} \emph{Ecography} 39 (10):
921--31. \url{https://doi.org/10.1111/ecog.01714}.

\leavevmode\hypertarget{ref-Dallas2020AbuNot}{}%
Dallas, Tad, Samuel Pironon, and Luca Santini. 2020. {``The
Abundant-Centre Is Not All That Abundant: A Comment to Osorio-Olvera Et
Al. 2020,''} 2020.02.27.968586.
\url{https://doi.org/10.1101/2020.02.27.968586}.

\leavevmode\hypertarget{ref-Daru2020GreToo}{}%
Daru, Barnabas H. 2020. {``GreenMaps: A Tool for Addressing the
Wallacean Shortfall in the Global Distribution of Plants.''}
\emph{bioRxiv}, 2020.02.21.960161.
\url{https://doi.org/10.1101/2020.02.21.960161}.

\leavevmode\hypertarget{ref-Dattilo2020SpeDri}{}%
Dáttilo, Wesley, Nathalia Barrozo-Chávez, Andrés Lira-Noriega, Roger
Guevara, Fabricio Villalobos, Diego Santiago-Alarcon, Frederico Siqueira
Neves, Thiago Izzo, and Sérvio Pontes Ribeiro. 2020. {``Species-Level
Drivers of Mammalian Ectoparasite Faunas.''} \emph{Journal of Animal
Ecology} 89 (8): 1754--65.
\url{https://doi.org/10.1111/1365-2656.13216}.

\leavevmode\hypertarget{ref-Dattilo2018EcoNet}{}%
Dáttilo, Wesley, and Victor Rico-Gray, eds. 2018. \emph{Ecological
Networks in the Tropics: An Integrative Overview of Species Interactions
from Some of the Most Species-Rich Habitats on Earth}. 1st ed. 2018.
Cham: Springer International Publishing : Imprint: Springer.
\url{https://doi.org/10.1007/978-3-319-68228-0}.

\leavevmode\hypertarget{ref-Dobson2009FooStr}{}%
Dobson, Andy. 2009. {``Food-Web Structure and Ecosystem Services:
Insights from the Serengeti.''} \emph{Philosophical Transactions of the
Royal Society B: Biological Sciences} 364 (1524): 1665--82.
\url{https://doi.org/10.1098/rstb.2008.0287}.

\leavevmode\hypertarget{ref-Draper1995AssPro}{}%
Draper, D. 1995. {``Assessment and Propagation of Model Uncertainty.''}
\emph{Journal of the Royal Statistical Society Series B-Statistical
Methodology} 57 (1): 45--97.
\url{https://doi.org/10.1111/j.2517-6161.1995.tb02015.x}.

\leavevmode\hypertarget{ref-Fourcade2016ComSpe}{}%
Fourcade, Yoan. 2016. {``Comparing Species Distributions Modelled from
Occurrence Data and from Expert-Based Range Maps. Implication for
Predicting Range Shifts with Climate Change.''} \emph{Ecological
Informatics} 36: 8--14.
\url{https://doi.org/10.1016/j.ecoinf.2016.09.002}.

\leavevmode\hypertarget{ref-Fricke2022EffDef}{}%
Fricke, Evan C., Alejandro Ordonez, Haldre S. Rogers, and Jens-Christian
Svenning. 2022. {``The Effects of Defaunation on Plants' Capacity to
Track Climate Change.''} \emph{Science}.
\url{https://doi.org/10.1126/science.abk3510}.

\leavevmode\hypertarget{ref-Godsoe2012HowSpe}{}%
Godsoe, William, and Luke J. Harmon. 2012. {``How Do Species
Interactions Affect Species Distribution Models?''} \emph{Ecography} 35
(9): 811--20. \url{https://doi.org/10.1111/j.1600-0587.2011.07103.x}.

\leavevmode\hypertarget{ref-Godsoe2017IntBio}{}%
Godsoe, William, Jill Jankowski, Robert D. Holt, and Dominique Gravel.
2017. {``Integrating Biogeography with Contemporary Niche Theory.''}
\emph{Trends in Ecology and Evolution} 32 (7): 488--99.
\url{https://doi.org/10.1016/j.tree.2017.03.008}.

\leavevmode\hypertarget{ref-Herkt2017MacCon}{}%
Herkt, K. Matthias B., Andrew K. Skidmore, and Jakob Fahr. 2017.
{``Macroecological Conclusions Based on IUCN Expert Maps: A Call for
Caution.''} \emph{Global Ecology and Biogeography} 26 (8): 930--41.
\url{https://doi.org/10.1111/geb.12601}.

\leavevmode\hypertarget{ref-Hortal2008UncMea}{}%
Hortal, Joaquín. 2008. {``Uncertainty and the Measurement of Terrestrial
Biodiversity Gradients.''} \emph{Journal of Biogeography} 35 (8):
1335--36. \url{https://doi.org/10.1111/j.1365-2699.2008.01955.x}.

\leavevmode\hypertarget{ref-Hortal2015SevSho}{}%
Hortal, Joaquín, Francesco de Bello, José Alexandre F. Diniz-Filho,
Thomas M. Lewinsohn, Jorge M. Lobo, and Richard J. Ladle. 2015. {``Seven
Shortfalls That Beset Large-Scale Knowledge of Biodiversity.''}
\emph{Annual Review of Ecology, Evolution, and Systematics} 46 (1):
523--49. \url{https://doi.org/10.1146/annurev-ecolsys-112414-054400}.

\leavevmode\hypertarget{ref-Hortal2008HisBia}{}%
Hortal, Joaquín, Alberto Jiménez-Valverde, José F. Gómez, Jorge M. Lobo,
and Andrés Baselga. 2008. {``Historical Bias in Biodiversity Inventories
Affects the Observed Environmental Niche of the Species.''} \emph{Oikos}
117 (6): 847--58.
\url{https://doi.org/10.1111/j.0030-1299.2008.16434.x}.

\leavevmode\hypertarget{ref-IUCNSSCRedListTechnicalWorkingGroup2021MapSta}{}%
IUCN SSC Red List Technical Working Group. 2021. \emph{Mapping Standards
and Data Quality for IUCN Red List Spatial Data}.

\leavevmode\hypertarget{ref-Krofel2021ResTax}{}%
Krofel, M., J. Hatlauf, W. Bogdanowicz, L. a. D. Campbell, R. Godinho,
Y. V. Jhala, A. C. Kitchener, et al. 2021. {``Towards Resolving
Taxonomic Uncertainties in Wolf, Dog and Jackal Lineages of Africa,
Eurasia and Australasia.''} \emph{Journal of Zoology} n/a (n/a): 1--14.
\url{https://doi.org/10.1111/jzo.12946}.

\leavevmode\hypertarget{ref-Ladle2013MapSpe}{}%
Ladle, Richard, and Joaquín Hortal. 2013. {``Mapping Species
Distributions: Living with Uncertainty.''} \emph{Frontiers of
Biogeography} 5 (1): 4--6.

\leavevmode\hypertarget{ref-McNaughton1992ProDis}{}%
McNaughton, S. J. 1992. {``The Propagation of Disturbance in Savannas
Through Food Webs.''} \emph{Journal of Vegetation Science} 3 (3):
301--14. \url{https://doi.org/10.2307/3235755}.

\leavevmode\hypertarget{ref-Meyer2016MulBia}{}%
Meyer, Carsten, Patrick Weigelt, and Holger Kreft. 2016.
{``Multidimensional Biases, Gaps and Uncertainties in Global Plant
Occurrence Information.''} \emph{Ecology Letters} 19 (8): 992--1006.
\url{https://doi.org/10.1111/ele.12624}.

\leavevmode\hypertarget{ref-Pocock2015BioRec}{}%
Pocock, Michael J. O., Helen E. Roy, Chris D. Preston, and David B. Roy.
2015. {``The Biological Records Centre: A Pioneer of Citizen Science.''}
\emph{Biological Journal of the Linnean Society} 115 (3): 475--93.
\url{https://doi.org/10.1111/bij.12548}.

\leavevmode\hypertarget{ref-Poisot2016ManMak}{}%
Poisot, Timothée, Benjamin Baiser, Jennifer A Dunne, Sonia Kéfi,
François Massol, Nicolas Mouquet, Tamara N Romanuk, Daniel B Stouffer,
Spencer A Wood, and Dominique Gravel. 2016. {``Mangal - Making
Ecological Network Analysis Simple.''} \emph{Ecography} 39 (4): 384--90.

\leavevmode\hypertarget{ref-Poisot2021GloKno}{}%
Poisot, Timothée, Gabriel Bergeron, Kevin Cazelles, Tad Dallas,
Dominique Gravel, Andrew MacDonald, Benjamin Mercier, Clément Violet,
and Steve Vissault. 2021. {``Global Knowledge Gaps in Species
Interaction Networks Data.''} \emph{Journal of Biogeography} 48 (7):
1552--63. \url{https://doi.org/10.1111/jbi.14127}.

\leavevmode\hypertarget{ref-Poisot2020EnvBia}{}%
Poisot, Timothée, Gabriel Bergeron, Kevin Cazelles, Tad Dallas,
Dominique Gravel, Andrew Macdonald, Benjamin Mercier, Clément Violet,
and Steve Vissault. 2020. {``Environmental Biases in the Study of
Ecological Networks at the Planetary Scale.''} \emph{bioRxiv},
2020.01.27.921429. \url{https://doi.org/10.1101/2020.01.27.921429}.

\leavevmode\hypertarget{ref-Power1992TopBot}{}%
Power, Mary E. 1992. {``Top-Down and Bottom-Up Forces in Food Webs: Do
Plants Have Primacy.''} \emph{Ecology} 73 (3): 733--46.
\url{https://doi.org/10.2307/1940153}.

\leavevmode\hypertarget{ref-Pringle2016LarHer}{}%
Pringle, Robert M., Kirsten M. Prior, Todd M. Palmer, Truman P. Young,
and Jacob R. Goheen. 2016. {``Large Herbivores Promote Habitat
Specialization and Beta Diversity of African Savanna Trees.''}
\emph{Ecology} 97 (10): 2640--57.
\url{https://doi.org/10.1002/ecy.1522}.

\leavevmode\hypertarget{ref-Ronquillo2020AssSpa}{}%
Ronquillo, Cristina, Fernanda Alves-Martins, Vicente Mazimpaka, Thadeu
Sobral-Souza, Bruno Vilela-Silva, Nagore G. Medina, and Joaquín Hortal.
2020. {``Assessing Spatial and Temporal Biases and Gaps in the Publicly
Available Distributional Information of Iberian Mosses.''}
\emph{Biodiversity Data Journal} 8: e53474.
\url{https://doi.org/10.3897/BDJ.8.e53474}.

\leavevmode\hypertarget{ref-Roy2016FocPla}{}%
Roy, Helen E., Elizabeth Baxter, Aoine Saunders, and Michael J. O.
Pocock. 2016. {``Focal Plant Observations as a Standardised Method for
Pollinator Monitoring: Opportunities and Limitations for Mass
Participation Citizen Science.''} \emph{PLOS ONE} 11 (3): e0150794.
\url{https://doi.org/10.1371/journal.pone.0150794}.

\leavevmode\hypertarget{ref-Ryan2018RolCit}{}%
Ryan, S. F., N. L. Adamson, A. Aktipis, L. K. Andersen, R. Austin, L.
Barnes, M. R. Beasley, et al. 2018. {``The Role of Citizen Science in
Addressing Grand Challenges in Food and Agriculture Research.''}
\emph{Proceedings of the Royal Society B: Biological Sciences} 285
(1891). \url{https://doi.org/10.1098/rspb.2018.1977}.

\leavevmode\hypertarget{ref-Scott2018RolHer}{}%
Scott, Abigail L., Paul H. York, Clare Duncan, Peter I. Macreadie, Rod
M. Connolly, Megan T. Ellis, Jessie C. Jarvis, Kristin I. Jinks, Helene
Marsh, and Michael A. Rasheed. 2018. {``The Role of Herbivory in
Structuring Tropical Seagrass Ecosystem Service Delivery.''}
\emph{Frontiers in Plant Science} 9: 127.
\url{https://doi.org/10.3389/fpls.2018.00127}.

\leavevmode\hypertarget{ref-Stoyanov2020CraVar}{}%
Stoyanov, S. 2020. {``Cranial Variability and Differentiation Among
Golden Jackals (Canis Aureus) in Europe, Asia Minor and Africa.''}
\emph{ZooKeys}. \url{https://doi.org/10.3897/zookeys.917.39449}.

\leavevmode\hypertarget{ref-Strydom2021RoaPre}{}%
Strydom, Tanya, Michael D. Catchen, Francis Banville, Dominique Caron,
Gabriel Dansereau, Philippe Desjardins-Proulx, Norma R. Forero-Muñoz, et
al. 2021. {``A Roadmap Towards Predicting Species Interaction Networks
(across Space and Time).''} \emph{Philosophical Transactions of the
Royal Society B: Biological Sciences} 376 (1837): 20210063.
\url{https://doi.org/10.1098/rstb.2021.0063}.

\leavevmode\hypertarget{ref-Svenning2014InfInt}{}%
Svenning, Jens Christian, Dominique Gravel, Robert D. Holt, Frank M.
Schurr, Wilfried Thuiller, Tamara Münkemüller, Katja H. Schiffers, et
al. 2014. {``The Influence of Interspecific Interactions on Species
Range Expansion Rates.''} \emph{Ecography} 37 (12): 1198--1209.
\url{https://doi.org/10.1111/j.1600-0587.2013.00574.x}.

\leavevmode\hypertarget{ref-Tsunoda2020VarTro}{}%
Tsunoda, Hiroshi, and Masayuki U. Saito. 2020. {``Variations in the
Trophic Niches of the Golden Jackal Canis Aureus Across the Eurasian
Continent Associated with Biogeographic and Anthropogenic Factors.''}
\emph{Journal of Vertebrate Biology} 69 (4): 20056.1.
\url{https://doi.org/10.25225/jvb.20056}.

\leavevmode\hypertarget{ref-Valiente-Banuet2015SpeLos}{}%
Valiente-Banuet, Alfonso, Marcelo A. Aizen, Julio M. Alcántara, Juan
Arroyo, Andrea Cocucci, Mauro Galetti, María B. García, et al. 2015.
{``Beyond Species Loss: The Extinction of Ecological Interactions in a
Changing World.''} Edited by Marc Johnson. \emph{Functional Ecology} 29
(3): 299--307. \url{https://doi.org/10.1111/1365-2435.12356}.

\leavevmode\hypertarget{ref-Young2013EffMam}{}%
Young, Hillary S., Douglas J. McCauley, Kristofer M. Helgen, Jacob R.
Goheen, Erik Otárola-Castillo, Todd M. Palmer, Robert M. Pringle, Truman
P. Young, and Rodolfo Dirzo. 2013. {``Effects of Mammalian Herbivore
Declines on Plant Communities: Observations and Experiments in an
\textsc{A} Frican Savanna.''} Edited by Luis Santamaria. \emph{Journal
of Ecology} 101 (4): 1030--41.
\url{https://doi.org/10.1111/1365-2745.12096}.

\end{CSLReferences}

\end{document}

### 2022-04-04 preprint.tex
Deploy to GitHub Pages

--- 2022-04-04 draft.tex
@@
 %!TEX TS-program = xelatex
-\documentclass[11pt]{article}
+\documentclass[10pt,oneside]{article}
 
@@
 \newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=4.5cm}
-
-\usepackage{lineno}
-\usepackage[nolists,noheads]{endfloat}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\usepackage[table,dvipsnames]{xcolor}
+
+\geometry{includemp,
+            letterpaper,
+            top=1.2in,
+            bottom=2.510cm,
+            inner=0.5in,
+            outer=0.4in,
+            marginparwidth=1.95in,
+            marginparsep=0.4in}
+
+\usepackage[singlelinecheck=off]{caption}
+\captionsetup{
+  font={small},
+  labelfont={bf},
+  format=plain,
+  labelsep=quad
+}
+\usepackage{floatrow}
+\floatsetup[figure]{margins=hangright,
+              facing=no,
+              capposition=beside,
+              capbesideposition={center,outside},
+              floatwidth=\textwidth}
+\floatsetup[table]{margins=hangoutside,
+             facing=yes,
+             capposition=beside,
+             capbesideposition={center,outside},
+             floatwidth=\textwidth}
 
@@
 
-\doublespacing
+\setcounter{secnumdepth}{5}
+
+\usepackage{titlesec}
+
+\titleformat{\section}[block]
+{\normalfont\large\sffamily}
+{\thesection}{.5em}{\titlerule\\[.8ex]\bfseries}
+
+\titleformat{\subsection}[runin]
+{\normalfont\fontseries{b}\selectfont\filright\sffamily}
+{\thesubsection.}{.5em}{}
+
+\titleformat{\subsubsection}[runin]
+{\normalfont\itshape\rmfamily\bfseries}{\thesubsubsection}{1em}{}
+
+\fancypagestyle{firstpage}
+{
+   \fancyhf{}
+   \renewcommand{\headrulewidth}{0pt}
+   \fancyfoot[R]{\footnotesize\ccby}
+   \fancyfoot[L]{\footnotesize\sffamily\today}
+}
 
@@
 }
+
+\usepackage{tikz}
 \begin{document}
-\thispagestyle{empty}
-{\Large\bfseries\sffamily Mismatch between IUCN range maps and species
-interactions data illustrated using the Serengeti food web}
-\vskip 5em
-
+\tikz [remember picture, overlay] %
+\node [shift={(-0.6in,1.1cm)},scale=0.2,opacity=0.4] at (current page.south east)[anchor=south east]{\includegraphics{logo}};%
+\pagestyle{normal}
+\thispagestyle{firstpage}
+
+\newcommand{\colorRule}[3][black]{\textcolor[HTML]{#1}{\rule{#2}{#3}}}
+
+\noindent {\LARGE \textbf{\textsf{Mismatch between IUCN range maps and
+species interactions data illustrated using the Serengeti food web}}}
+
+\medskip
+\begin{flushleft}
+{\small
 %
@@
 %
-\,\textsuperscript{1,2,‡}\quad %
+\,\textsuperscript{1,2,‡}, %
 \href{https://orcid.org/0000-0001-5030-3470}{Fredric\,M. Windsor}%
 %
-\,\textsuperscript{3,‡}\quad %
+\,\textsuperscript{3,‡}, %
 \href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
 %
-\,\textsuperscript{4,5,6,‡}\quad %
+\,\textsuperscript{4,5,6,‡}, %
 \href{https://orcid.org/0000-0002-2212-3584}{Gabriel\,Dansereau}%
 %
-\,\textsuperscript{4,6,‡}\quad %
+\,\textsuperscript{4,6,‡}, %
 \href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
 %
-\,\textsuperscript{4,6,‡}\quad %
+\,\textsuperscript{4,6,‡}, %
 \href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
@@
 \,\textsuperscript{4,6,‡}
-
+\vskip 1em
 \textsuperscript{1}\,The University of British
-Columbia\quad \textsuperscript{2}\,Computational Biodiversity Science
-and Services\quad \textsuperscript{3}\,School of Natural and
-Environmental Sciences, Newcastle
-University\quad \textsuperscript{4}\,Université de
-Montréal\quad \textsuperscript{5}\,Université de
-Sherbrooke\quad \textsuperscript{6}\,Quebec Centre for Biodiversity
-Science
-
+Columbia; \textsuperscript{2}\,Computational Biodiversity Science and
+Services; \textsuperscript{3}\,School of Natural and Environmental
+Sciences, Newcastle University; \textsuperscript{4}\,Université de
+Montréal; \textsuperscript{5}\,Université de
+Sherbrooke; \textsuperscript{6}\,Quebec Centre for Biodiversity
+Science\\
 \textsuperscript{‡}\,These authors contributed equally to the work\\
-
+\vskip 1em
 \textbf{Correspondance to:}\\
@@
 Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
-
-\vfill
-This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
-Last revision: \emph{\today}
-
-\clearpage
-\thispagestyle{empty}
-
-\vfill
-\textbf{\sffamily Abstract: }Range maps are a useful tool to describe
-the spatial distribution of species. However, they often need to be used
-with caution, as they essentially represent a rough approximation of a
+}
+\end{flushleft}
+
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
+\noindent
+
+\marginpar{\vskip 1em\flushright
+{\small{\bfseries Keywords}:\par
+range maps\\species interactions\\food web\\Serengeti\\}
+}
+
+\textbf{Abstract}:\,Range maps are a useful tool to describe the spatial
+distribution of species. However, they often need to be used with
+caution, as they essentially represent a rough approximation of a
 species' suitable habitats. When stacked together, the resulting
@@
 incomplete, is ecologically accurate.
-\vfill
-
-\clearpage
-\linenumbers
-\pagestyle{normal}
+
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
 

### 2022-06-27 response-letter.md
1st draft

Dear editor,

Thank you for the valuable feedback on our manuscript. We are pleased that you
and the reviewer found interest and worth in our manuscript. We addressed each comment and found that the manuscript is indeed clearer now, and we hope to have it approved after your consideration.

We have added more context in the introduction section, but we've found it hard
to expand the first paragraph. We believe that this particular paragraph needs
to be more succinct, at the same time that it provides a complete picture of the
paper, framed in a storytelling structure. Then, on the second paragraph, we
start providing literature background and many examples, to help the reader
understand where our paper stands in the scientific context. We have included
discussions about the quality and accuracy of range maps (lines XX-XX), examples
of data biases (lines XX-XX), and we addressed the uniqueness of our study
compared to previous research (lines XX-XX). We hope that this structure is
clarifying and appealing to the readers.

Regarding the GBIF data cleaning, retrieval and the validation steps, we added a
more detailed description of our process (lines XX-XX, XX-XX and XX-XX). Data
retrieving is detailed in the source code provided on our GitHub repository
(code/06-GBIF_data.jl). We used the list of species from the network dataset and
retrieved any occurrence within our bounding box (between longitudes -20.0 and
55.0 degrees; and latitudes -35.0 and 40.0 degrees). Some taxonomic
investigation needed to be done due to inconsistencies between GBIF and IUCN
nomenclatures (in the case of _Taurotragus oryx_). We didn't perform any further
data cleaning procedures because this could hinder the goals of the paper, which
was to investigate the characteristics of the data available for research. As we
needed to compare two sets of raw data, and data cleaning protocols are
dependent on the use objectives, we chose to avoid data manipulation both for
GBIF and IUCN datasets.

For the validation step, we understand our phrasing was confusing, and we have
rewritten this section to clarify our method. Rather than using
absence data, what we did was to transform the point data into raster files, and
then restrict our range maps to the locations where we had GBIF occurrences.
Therefore, the pixels where there are no GBIF occurrences are not considered
true absence of a species, but absence of **data** about the occurrence of that
species.

Finally, we have addressed all the other minor comments throughout the text as
described below:
- We've added citations on the Methods section to support our argument that a
  mismatch between ranges can be originated from different sources (L. 68-70)
- We have suppressed lines 214-217.
- The abstract is now restructured according to PeerJ guidelines.
- References to tables and figures in the Discussion section were suppressed,
  with the exception of Figure 05 (line XX), which is an example of our results
  to clarify an important point of the discussion.
- Lines 22-23 (now lines XX-XX): the cited literature are not examples of models
  that do not take ecological interactions into account, but studies that have
  demonstrated how ecological interactions might be responsible for shaping a
  species' distribution. We've rewritten the sentence to clarify that.
-  Lines 68-70: we have rewritten the sentence to include the consideration
   misestimation of both species in a trophic interaction. We have also added
   citations and examples.
- We have addressed the grammatical suggestions throughout the text, except for
  the legend of figure 5. We thought that the suggested phrasing adds a little
  bit of confusion to the comprehension of the figure.

We hope our revised manuscript is now more appropriate for publishing at PeerJ.
Reiterating our appreciation for yours and the reviewer's thoughtful comments,
we are available to answer any further questions.

Best regards,
The Authors

### 2022-07-08 draft.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@7dfa55f42d368132ed2c1af3d1475ee71992276e 🚀

@@
 \vfill
-\textbf{\sffamily Abstract: }Range maps are a useful tool to describe
-the spatial distribution of species. However, they often need to be used
-with caution, as they essentially represent a rough approximation of a
-species' suitable habitats. When stacked together, the resulting
-communities in each grid cell may not always be realistic, especially
-when species interactions are taken into account. Here we show the
-extent of the mismatch between range maps, provided by the International
-Union for Conservation of Nature, and species interactions data. More
-precisely, we show that local networks built from those stacked range
-maps often yield unrealistic communities, where species of higher
-trophic levels are completely disconnected from primary producers. We
-use the well-described Serengeti food web of mammals and plants as our
-case study, and provide updated range maps that take into account
-food-web structure. In our analysis, most predator ranges were
-restricted by the absence of herbivores. This restriction was sometimes
-contradicted by GBIF occurrences, suggesting the mismatch can be due
-either to the lack of information about ecological interactions or about
-the geographical occurrence of preys. We finally discuss general
-guidelines to help identify defective data among distributions and
-interactions data, and we recommend this method as a valuable way to
-assess weather the occurrence data that are being used, even if
-incomplete, is ecologically accurate.
+\textbf{\sffamily Abstract: }\textbf{Background.} Range maps are a
+useful tool to describe the spatial distribution of species. However,
+they need to be used with caution, as they essentially represent a rough
+approximation of a species' suitable habitats. When stacked together,
+the resulting communities in each grid cell may not always be realistic,
+especially when species interactions are taken into account. Here we
+show the extent of the mismatch between range maps, provided by the
+International Union for Conservation of Nature (IUCN), and species
+interactions data. More precisely, we show that local networks built
+from those stacked range maps often yield unrealistic communities, where
+species of higher trophic levels are completely disconnected from
+primary producers. \textbf{Methodology.} We used the well-described
+Serengeti food web of mammals and plants as our case study, and provide
+updated range maps for all predators by taking into account food-web
+structure. We then used occurrence data from the Global Biodiversity
+Information Facility (GBIF) to investigate where data is most lacking.
+\textbf{Results.} We found that most predator ranges comprised large
+areas without any overlapping distribution of their preys. However, many
+of these areas contained GBIF occurrences of the predator.
+\textbf{Conclusions.} Our results suggest that the mismatch between both
+data sources could be due either to the lack of information about
+ecological interactions or the geographical occurrence of preys. We
+finally discuss general guidelines to help identify defective data among
+distributions and interactions data, and we recommend this method as a
+valuable way to assess whether the occurrence data that are being used,
+even if incomplete, are ecologically accurate.
 \vfill
@@
 Finding a species in a certain location is like finding an encrypted
-message that travelled through time. It carries the species'
-evolutionary history, migration patterns, as well as any direct and
-indirect effects generated by other species (some of which we may not
-even know exist). Ecologists have been trying to decode this message
-with progressively more powerful tools, from their own field notes to
-highly complex computational algorithms. However, to succeed in this
-challenge it is important to have the right clues in hand. There are
-many ways we can be misled by data - or the lack of it: taxonomic
-errors, geographic inaccuracy, or sampling biases (Ladle and Hortal
-2013; Hortal et al. 2015; Poisot et al. 2021). One way to identify - and
-potentially fix - these errors is to combine many different pieces of
-information about the occurrence of a species, so agreements and
-mismatches can emerge. Here we suggest jointly analysing species
-occurrence (range maps and point occurrences) and ecological
-interactions to identify mismatches between datasets.
+message that traveled through time. It carries the species' evolutionary
+history, migration patterns, as well as any direct and indirect effects
+generated by other species (some of which we may not even know exist).
+Ecologists have been trying to decode this message with progressively
+more powerful tools, from their field notes to highly complex
+computational algorithms. However, to succeed in this challenge it is
+important to have the right clues in hand. There are many ways we can be
+misled by data - or the lack of it: taxonomic errors, geographic
+inaccuracy, or sampling biases (Ladle and Hortal 2013; Hortal et al.
+2015; Poisot et al. 2021). One way to identify - and potentially fix -
+these errors is to combine many different pieces of information about
+the occurrence of a species, so agreements and mismatches can emerge.
+Here we suggest jointly analyzing species occurrence (range maps and
+point occurrences) and ecological interactions to identify mismatches
+between datasets.
 
@@
 long-term monitoring schemes. A great source of bias in these datasets
-is the irregular sampling effort, with more occurrences originated from
+is the irregular sampling effort, with more occurrences originating from
 attractive and accessible areas and observation of charismatic species
@@
 interactions in Africa (fig.~\ref{fig:richness}). These ecosystems host
-a range of different species, including the well characterized
-predator-prey dynamics between iconic predators (e.g., lions, hyenas and
-leopards) and large herbivores (e.g., antelopes, wildebeests and
+a range of different species, including the well-characterized
+predator-prey dynamics between iconic predators (e.g., lions, hyenas,
+and leopards) and large herbivores (e.g., antelopes, wildebeests, and
 zebras), as well as a range of herbivorous and carnivorous small
@@
 sampled interaction data for herbivores and carnivores. This subnetwork
-contained 32 taxa (23 herbivores and 9 carnivores) and 84 interactions,
+contained 32 taxa (23 herbivores and 9 carnivores) and 84 interactions
 and had a connectance of 0.08. Although self-loops are informative, we
@@
 interactions: the former is derived information from the metaweb, and
-the later is contingent to the presence of herbivores.
+the latter is contingent on the presence of herbivores.
 
@@
 We calculated the geographical overlap, i.e.~the extent to which
-interacting predator and prey species cooccurred across their ranges, as
-\(a/(a + c)\), where \(a\) is the number of pixels where predator and
+interacting predator and prey species co-occurred across their ranges,
+as \(a/(a + c)\), where \(a\) is the number of pixels where predator and
 prey cooccur and \(c\) is the number of pixels where only the focal
@@
 ranges of the two species and values closer to 0 indicating low
-cooccurrence across their ranges. For each predator species we
+cooccurrence across their ranges. For each predator species, we
 calculated its generality to understand whether the level of trophic
@@
 presence or absence of the focal taxon. These data were used to validate
-the range adjustments made based on species interactions (see previous
-section). To do so, we calculated the proportion of GBIF presence pixels
-occurring within both the original and adjusted species ranges. We then
-compared these proportions for the predators to verify if the range
-adjustments removed locations with GBIF observations, hence likely true
-habitats.
+the range adjustments made based on species interactions (see the
+previous section). To do so, we calculated the proportion of GBIF
+presence pixels occurring within both the original and adjusted species
+ranges. We then compared these proportions for the predators to verify
+if the range adjustments removed locations with GBIF observations, hence
+likely true habitats.
 
@@
 
-Predators with less preys lose more range with our method
+Predators with fewer prey lose more range with our method
 (fig.~\ref{fig:degree}). For instance, both \emph{Leptailurus serval}
@@
 There was high variation in the overlap of predator and prey ranges
-(fig.~\ref{fig:geo_diss}). The high density of points on left-hand side
-of fig.~\ref{fig:geo_diss} indicates that most preys have small ranges
-in comparison to those of the set of carnivores in the networks,
+(fig.~\ref{fig:geo_diss}). The high density of points on the left-hand
+side of fig.~\ref{fig:geo_diss} indicates that most preys have small
+ranges in comparison to those of the set of carnivores in the networks,
 resulting in either low overlap between both ranges (bottom) or high
@@
 \caption{\label{tbl:everyone}List of species analyzed, their out and in
-degrees, total original range size (in pixels) and proportion of their
+degrees, total original range size (in pixels), and proportion of their
 ranges occupied by their preys and predators (values between 0 and 1).
@@
 al. (2011). Notice how some species are isolated in the network
-(\emph{Loxodonta africana}) and how \emph{Canis aureus}'s range do not
+(\emph{Loxodonta africana}) and how \emph{Canis aureus}'s range does not
 overlap with any of its preys.}\tabularnewline
@@
 original IUCN ranges for most predator species (fig.~\ref{fig:gbif}).
-Four species showed no difference of proportion while three species
+Four species showed no difference in proportion while three species
 showed only small differences (proportions of 0.01 to 0.05). On the
-other hand, two species, \emph{Canis mesomelas} and \emph{Leptailurus
-serval}, showed very high differences, with overlaps lower by 0.548 and
+other hand, two species, \emph{Canis mesomelas}, and \emph{Leptailurus
+serval} showed very high differences, with overlaps lower by 0.548 and
 0.871 respectively. For \emph{Leptailurus serval}, none of the GBIF
@@
 
-The jackal is a widespread taxon in northern Africa, Europe and
+The jackal is a widespread taxon in northern Africa, Europe, and
 Australasia, generally well adapted to local conditions due to its
@@
 there are significant reductions in the IUCN range size of predatory
-organisms. Despite showing the potential importance in accounting for
+organisms. Despite showing the potential importance of accounting for
 species interactions when estimating the range of a species, it remains
 unclear the extent to which the patterns observed represent ecological
-processes or a lack of data. In the following sections we discuss the
+processes or a lack of data. In the following sections, we discuss the
 implications of our findings, in terms of species range maps,
-interaction data and the next steps required to enhance understanding of
-species distributions using information on ecological networks.
+interaction data, and the next steps required to enhance understanding
+of species distributions using information on ecological networks.
 
@@
 older metacommunities are probably affected in different ways in the
-centre of the distribution, at the edge of ranges and in sink and source
-communities (Svenning et al. 2014; Godsoe et al. 2017; Cazelles et al.
-2016; Bullock et al. 2000). Additionally, it is likely that species with
-larger ranges of distribution and those that are more generalists would
-co-occur with a greater number of other species (Dáttilo et al. 2020),
-while dispersal capacity of competitive species modulate their
-aggregation in space and the effect of interactions on their range
-limits (Godsoe et al. 2017).
+center of the distribution, at the edge of ranges, and in sink and
+source communities (Svenning et al. 2014; Godsoe et al. 2017; Cazelles
+et al. 2016; Bullock et al. 2000). Additionally, it is likely that
+species with larger ranges of distribution and those that are more
+generalists would co-occur with a greater number of other species
+(Dáttilo et al. 2020), while dispersal capacity of competitive species
+modulate their aggregation in space and the effect of interactions on
+their range limits (Godsoe et al. 2017).
 
@@
 
-The geographical mismatch between predators and preys have ecological
+The geographical mismatch between predators and preys has ecological
 consequences such as loss of ecosystem functioning and extinction of
@@
 et al. 2016; Young et al. 2013). Climate change is one of the causes of
-this, leading, for instance, to the decrease of plants populations due
-to the lack of pollination (Bullock et al. 2000; Afkhami, McIntyre, and
+this, leading, for instance, to the decrease of plant populations due to
+the lack of pollination (Bullock et al. 2000; Afkhami, McIntyre, and
 Strauss 2014; Godsoe et al. 2017). However, this mismatch can also be
-purely informational. When the distribution of predators and preys do
+purely informational. When the distribution of predators and preys does
 not superpose, it can mean we lack information about the distribution of
@@
 suggests that we certainly do miss geographical information about the
-distribution of a certain species, but it is not an indicative about the
+distribution of a certain species, but it is not an indicator of the
 completeness of the information about ecological interactions. However,
@@
 species fell outside the IUCN range (fig.~\ref{fig:gbif}). In this
-particular case, the IUCN maps seem to agree with species interactions
+particular case, the IUCN maps seem to agree with species interaction
 data. However, the disagreement between the IUCN and the GBIF databases
@@
 data on both serval and its prey, with a buffer for the prey to account
-on species mobility.}\label{fig:serval}
+for species mobility.}\label{fig:serval}
 }
@@
 is important to notice, however, that the quality and usefulness of this
-method is highly correlated with the amount and quality of data
+method are highly correlated with the amount and quality of data
 available about species' occurrences \textbf{and} interactions. With
@@
 Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak nations. GH,
-FB, GD, and NF are funded by the NSERC BIOS\(^2\) CREATE program; FB,
-NF, and TP are funded by IVADO; NF and TP are funded by a donation from
-the Courtois Foundation; GD is funded by the FRQNT doctoral scholarship;
-TP is funded by the Canadian Institute of Ecology \& Evolution; FW is
-funded by the Royal Society (Grant number:
+FB, GD, and NF are funded by the NSERC Computational Biodiversity
+Science and Services (BIOS\(^2\)) CREATE program; FB, NF, and TP are
+funded by the Institute for Data Valorization (IVADO); NF and TP are
+funded by a donation from the Courtois Foundation; GD is funded by the
+FRQNT doctoral scholarship; TP is funded by the Canadian Institute of
+Ecology \& Evolution; FW is funded by the Royal Society (Grant number:
 CHL\textbackslash R1\textbackslash180156).

### 2022-07-08 preprint.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@7dfa55f42d368132ed2c1af3d1475ee71992276e 🚀

@@
 
-\textbf{Abstract}:\,Range maps are a useful tool to describe the spatial
-distribution of species. However, they often need to be used with
-caution, as they essentially represent a rough approximation of a
-species' suitable habitats. When stacked together, the resulting
+\textbf{Abstract}:\,\textbf{Background.} Range maps are a useful tool to
+describe the spatial distribution of species. However, they need to be
+used with caution, as they essentially represent a rough approximation
+of a species' suitable habitats. When stacked together, the resulting
 communities in each grid cell may not always be realistic, especially
@@
 extent of the mismatch between range maps, provided by the International
-Union for Conservation of Nature, and species interactions data. More
-precisely, we show that local networks built from those stacked range
-maps often yield unrealistic communities, where species of higher
-trophic levels are completely disconnected from primary producers. We
-use the well-described Serengeti food web of mammals and plants as our
-case study, and provide updated range maps that take into account
-food-web structure. In our analysis, most predator ranges were
-restricted by the absence of herbivores. This restriction was sometimes
-contradicted by GBIF occurrences, suggesting the mismatch can be due
-either to the lack of information about ecological interactions or about
-the geographical occurrence of preys. We finally discuss general
-guidelines to help identify defective data among distributions and
-interactions data, and we recommend this method as a valuable way to
-assess weather the occurrence data that are being used, even if
-incomplete, is ecologically accurate.
+Union for Conservation of Nature (IUCN), and species interactions data.
+More precisely, we show that local networks built from those stacked
+range maps often yield unrealistic communities, where species of higher
+trophic levels are completely disconnected from primary producers.
+\textbf{Methodology.} We used the well-described Serengeti food web of
+mammals and plants as our case study, and provide updated range maps for
+all predators by taking into account food-web structure. We then used
+occurrence data from the Global Biodiversity Information Facility (GBIF)
+to investigate where data is most lacking. \textbf{Results.} We found
+that most predator ranges comprised large areas without any overlapping
+distribution of their preys. However, many of these areas contained GBIF
+occurrences of the predator. \textbf{Conclusions.} Our results suggest
+that the mismatch between both data sources could be due either to the
+lack of information about ecological interactions or the geographical
+occurrence of preys. We finally discuss general guidelines to help
+identify defective data among distributions and interactions data, and
+we recommend this method as a valuable way to assess whether the
+occurrence data that are being used, even if incomplete, are
+ecologically accurate.
 

### 2022-07-14 code/06-GBIF_data.jl
🔧 run GBIF query without Africa as continent
updated data

@@ -1,8 +1,10 @@
 # Load required scripts and packages
-include("01-load_rasters.jl") # range maps of Serengeti mammals 
+include("01-load_rasters.jl") # range maps of Serengeti mammals
 include("shapefile.jl") # mapping functions
 
+using CSV
 using GBIF
+using DataFramesMeta
 
 # Getting taxa codes
 sp_codes = taxon.(mammals, rank = :SPECIES)
@@ -17,7 +19,6 @@ occ = occurrences.(
     "hasCoordinate" => "true",
     "decimalLatitude" => lat,
     "decimalLongitude" => lon,
-    "continent" => "AFRICA"
 )
 ## Loop to get all occurrences
 Threads.@threads for o in occ
@@ -40,6 +41,9 @@ occ_df = DataFrame.(occ)
 occ_df = reduce(vcat, occ_df)
 select!(occ_df, :species, :longitude, :latitude)
 occ_df.species = replace.(occ_df.species, " " => "_")
+
+# Remove observations with coordinates around (0.0, 0.0) which are outside mainland
+filter!(x -> !(x.latitude > -2.0 && x.latitude < 2.0 && x.longitude > -2.0 && x.longitude < 2.0), occ_df)
 
 # Make sure the species names match
 isequal(unique(occ_df.species), mammals) # not the same

### 2022-07-14 code/06-GBIF_data.jl
🔍 investigate difference with previous GBIF query

@@ -59,6 +59,21 @@ isequal(unique(occ_df.species), mammals) # true
 # Save as CSV
 CSV.write(joinpath("data", "clean", "gbif_occurrences.csv"), occ_df)
 
+## Investigate difference with original query with Africa as continent
+# Load datasets
+old = CSV.read(joinpath("data", "clean", "gbif_occurrences_old.csv"), DataFrame) # get from previous commit
+new = CSV.read(joinpath("data", "clean", "gbif_occurrences.csv"), DataFrame)
+
+# Compare number of observations per species
+_nold = combine(groupby(old, :species), nrow => :nrow_old)
+_nnew = combine(groupby(new, :species), nrow => :nrow_new)
+diff = @chain begin
+    leftjoin(_nold, _nnew, on = :species)
+    @transform(diff = :nrow_new .- :nrow_old)
+    sort(:diff, rev=true)
+end
+diff
+
 ## Create layers
 
 # Make sure GBIF records order is the same as in mammals CSV file

### 2022-07-14 code/05-degrees.jl
🐛 repair broken scripts

@@ -1,4 +1,4 @@
-include("02-get_networks.jl")
+include("04-ranges_diff.jl")
 
 ## Calculate the out degree of the organisms in the metaweb
 mammal_degree = degree(MM, dims = 1)
@@ -15,7 +15,7 @@ sp_outdegree_df = DataFrame(species = collect(keys(sp_outdegree)), n_preys = col
 sp_indegree = degree(M, dims=2);
 sp_indegree_df = DataFrame(species = collect(keys(sp_indegree)), n_predators = collect(values(sp_indegree)))
 
-# Total preys and predators 
+# Total preys and predators
 sp_degrees = leftjoin(sp_outdegree_df, sp_indegree_df, on=:species)
 
 ranges_degrees_df = copy(cooccurrence_beta)

### 2022-07-14 draft.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@5a150cb024075c3f4a0c0f293c3d3ba61fcf4ed8 🚀

@@
 In the Serengeti food web there is a positive relationship between the
-out degrees of predators and the size of their ranges
-(tbl.~\ref{tbl:everyone}). In addition, our results show that there is a
-negative relationship between the relative loss of predators' ranges and
-their number of preys (fig.~\ref{fig:degree}), reinforcing the idea that
-generalist species can preserve their distributions longer while losing
-interactions. The factors limiting the geographical range of a species
-in a community can vary with connectivity and richness (Svenning et al.
-2014). Younger communities may be more affected by environmental
-limitations because they are dominated by generalist species, while
-older metacommunities are probably affected in different ways in the
-center of the distribution, at the edge of ranges, and in sink and
-source communities (Svenning et al. 2014; Godsoe et al. 2017; Cazelles
-et al. 2016; Bullock et al. 2000). Additionally, it is likely that
-species with larger ranges of distribution and those that are more
+out degrees of predators and the size of their ranges. In addition, our
+results show that there is a negative relationship between the relative
+loss of predators' ranges and their number of preys, reinforcing the
+idea that generalist species can preserve their distributions longer
+while losing interactions. The factors limiting the geographical range
+of a species in a community can vary with connectivity and richness
+(Svenning et al. 2014). Younger communities may be more affected by
+environmental limitations because they are dominated by generalist
+species, while older metacommunities are probably affected in different
+ways in the center of the distribution, at the edge of ranges, and in
+sink and source communities (Svenning et al. 2014; Godsoe et al. 2017;
+Cazelles et al. 2016; Bullock et al. 2000). Additionally, it is likely
+that species with larger ranges of distribution and those that are more
 generalists would co-occur with a greater number of other species
@@
 the lion (\emph{Panthera leo}) was one of the species with the smallest
-difference between the original and the updated ranges
-(fig.~\ref{fig:degree}), but 59.5\% of the GBIF occurrences for this
-species fell outside the IUCN range (fig.~\ref{fig:gbif}). In this
-particular case, the IUCN maps seem to agree with species interaction
-data. However, the disagreement between the IUCN and the GBIF databases
-is concerning and suggests that the IUCN maps might underestimate the
-lion's distribution. On the other hand, \emph{Leptailurus serval} and
-\emph{Canis mesomelas} are two of the three species that lose the higher
-proportion of range due to the lack of paths to a herbivore
-(fig.~\ref{fig:degree}), but are also some of the species with the
+difference between the original and the updated ranges, but 59.5\% of
+the GBIF occurrences for this species fell outside the IUCN range
+(fig.~\ref{fig:gbif}). In this particular case, the IUCN maps seem to
+agree with species interaction data. However, the disagreement between
+the IUCN and the GBIF databases is concerning and suggests that the IUCN
+maps might underestimate the lion's distribution. On the other hand,
+\emph{Leptailurus serval} and \emph{Canis mesomelas} are two of the
+three species that lose the higher proportion of range due to the lack
+of paths to a herbivore, but are also some of the species with the
 higher proportion of GBIF occurrences inside IUCN range maps

### 2022-07-14 draft.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@8668df84be3ce4d66689ced6284ae5641ea452e4 🚀

@@
 important to have the right clues in hand. There are many ways we can be
-misled by data - or the lack of it: taxonomic errors, geographic
-inaccuracy, or sampling biases (Ladle and Hortal 2013; Hortal et al.
-2015; Poisot et al. 2021). One way to identify - and potentially fix -
-these errors is to combine many different pieces of information about
-the occurrence of a species, so agreements and mismatches can emerge.
-Here we suggest jointly analyzing species occurrence (range maps and
-point occurrences) and ecological interactions to identify mismatches
-between datasets.
+misled by data - or the lack of it: taxonomic errors (e.g., due to
+updates in the taxonomy of a species), geographic inaccuracy (e.g.,
+approximate coordinates or lack of documentation about their accuracy),
+or sampling biases (e.g.~data clustered near roads or research centers)
+(Ladle and Hortal 2013; Hortal et al. 2015; Poisot et al. 2021). One way
+to identify - and potentially fix - these errors is to combine many
+different pieces of information about the occurrence of a species, so
+agreements and mismatches can emerge. Although previous studies have
+combined different types of occurrence data to measure the accuracy of
+datasets (Hurlbert and Jetz 2007; Hurlbert and White 2005; Ficetola et
+al. 2014), none have used different types of information so far (i.e.,
+ecological characteristics other than geographical distribution). Here
+we suggest jointly analysing species occurrence (range maps and point
+occurrences) and ecological interactions to identify mismatches between
+datasets.
 
@@
 occurrence and interaction data is a frequent debate in ecology
-(Blanchet, Cazelles, and Gravel 2020). For instance, macroecological
-models are often used with point or range occurrence data in order to
-investigate the dynamics of a species with its environment. However,
-these models do not account for ecological interactions, which might
-largely affect species distribution (Abrego et al., n.d.; Afkhami,
-McIntyre, and Strauss 2014; Araújo, Marcondes-Machado, and Costa 2014;
-Godsoe et al. 2017; Godsoe and Harmon 2012). Some researchers argue that
-occurrence data can also capture real-time interactions (Roy et al.
-2016; Ryan et al. 2018), and, because of that, it would not be necessary
-to include ecological interaction dynamics in macroecological models. On
-the other hand, many mechanistic simulation models in ecology have
-considered the effect of competition and facilitation in range shifts,
-whilst the use of trophic interactions in this context remains
-insufficient (Cabral, Valente, and Hartig 2017).
+{[}Blanchet, Cazelles, and Gravel (2020); Wisz2013RolBio{]}. For
+instance, macroecological models are often used with point or range
+occurrence data in order to investigate the dynamics of a species with
+its environment. However, these models do not account for ecological
+interactions, although it has been demonstrated that they might largely
+affect species distribution {[}Abrego et al. (2021); Afkhami, McIntyre,
+and Strauss (2014); Araújo, Marcondes-Machado, and Costa (2014); Godsoe
+et al. (2017); Godsoe and Harmon (2012); Gotelli, Graves, and Rahbek
+(2010); Wisz2013RolBio{]}. Some researchers argue that occurrence data
+can also capture real-time interactions (see Roy et al. 2016; Ryan et
+al. 2018), and, because of that, it would not be necessary to include
+ecological interaction dynamics in macroecological models. On the other
+hand, many mechanistic simulation models in ecology have considered the
+effect of competition and facilitation in range shifts. For example,
+Gotelli \emph{et al.} -(Gotelli, Graves, and Rahbek 2010) demonstrate
+how conspecific attraction might be the main factor driving the
+distribution of migratory birds; Afkhami \emph{et al.} -(Afkhami,
+McIntyre, and Strauss 2014) explores how mutualistic fungal endophytes
+are responsible or expanding the range of native grass; many other
+examples are discussed in Wisz \emph{et al.} -(Wisz et al. 2013).
+Although interactions across trophic levels are demonstrated to
+determine species range (Wisz et al. 2013), the use of these
+interactions in mechanistic simulation models in macroecology remains
+insufficient (as discussed in Cabral, Valente, and Hartig 2017).
 
@@
 around known species locations, refined by expert knowledge about the
-species (2021). These maps can be used in macroecological inferences in
-the lack of more precise information (Fourcade 2016; Alhajeri and
-Fourcade 2019), but it has been recommended that they are used with
-caution since they tend to underestimate the distribution of species
-that are not well-known (Herkt, Skidmore, and Fahr 2017), do not
-represent spatial variation in species occurrence and abundance (Dallas,
-Pironon, and Santini 2020), and can include inadequate areas within the
-estimated range. Another source of species distribution information is
-the Global Biodiversity Information Facility (GBIF), which is an online
-repository of georeferenced observational records that come from various
-sources, including community science programs, museum collections, and
-long-term monitoring schemes. A great source of bias in these datasets
-is the irregular sampling effort, with more occurrences originating from
+species (IUCN Red List Technical Working Group 2019). These maps can be
+used in macroecological inferences in the lack of more precise
+information (Fourcade 2016; Alhajeri and Fourcade 2019), but it has been
+recommended that they are used with caution since they tend to
+underestimate the distribution of species that are not well-known
+(Herkt, Skidmore, and Fahr 2017) (especially at fine scale resolutions;
+(Hurlbert and Jetz 2007; Hurlbert and White 2005)), do not represent
+spatial variation in species occurrence and abundance (Dallas, Pironon,
+and Santini 2020), and can include inadequate areas within the estimated
+range. Another source of species distribution information is the Global
+Biodiversity Information Facility (GBIF), which is an online repository
+of georeferenced observational records that come from various sources,
+including community science programs, museum collections, and long-term
+monitoring schemes. A great source of bias in these datasets is the
+irregular sampling effort, with more occurrences originating from
 attractive and accessible areas and observation of charismatic species
@@
 
-In this context, we elaborate a method that allows us to refine
-distribution data (more precisely range maps) based on interaction data,
-considering the basic assumption that predators can only be present in
-regions where they are connected to at least one herbivore - and thus
-indirectly connected to primary producers. We used a Serengeti food web
-dataset (Baskerville et al. 2011) (which comprises carnivores,
-herbivores, and plants from Tanzania) to demonstrate how a mismatch
-between occurrence and interaction data can highlight significant
-uncertainty areas in IUCN range maps. Finally, we add the GBIF
-occurrence points for the Serengeti species to the investigation,
+It has been demonstrated that the agreement between range maps and point
+data varies geographically (Hurlbert and Jetz 2007; Hurlbert and White
+2005; Ficetola et al. 2014). Adding ecological interaction data to this
+comparison might help to elucidate where these (dis)agreements are more
+likely to be true and which dataset better represent the actual
+distribution of species. In this context, we elaborate a method that
+allows us to refine distribution data (more precisely range maps) based
+on interaction data, considering the basic assumption that predators can
+only be present in regions where they are connected to at least one
+herbivore - and thus indirectly connected to primary producers. We used
+a Serengeti food web dataset (Baskerville et al. 2011) (which comprises
+carnivores, herbivores, and plants from Tanzania) to demonstrate how a
+mismatch between occurrence and interaction data can highlight
+significant uncertainty areas in IUCN range maps. Finally, we add the
+GBIF occurrence points for the Serengeti species to the investigation,
 discuss the mechanisms that can lead to the lack of agreement between
@@
 expect the predator to occur in this area. This mismatch can be the
-result of different mechanisms, like the overestimation of the
-predator's range, taxonomic errors, or the lack of information about
-trophic links. Thus, given that herbivores are the main connection
-between plant resources (directly limited by environmental conditions)
-and predators (Dobson 2009; Scott et al. 2018), here we adjusted the
-ranges of predators based on a simple rule: we removed any part of a
-predator's range that did not intersect with the range of at least one
-prey herbivore species. So, unless the range of the predator overlapped
-with at least one prey item, which in turn is directly connected to a
-primary producer (plants), we removed that section of the predator's
-range. Finally, we calculated the difference in range size between the
-original IUCN ranges and those adjusted based on species interaction
-data.
+result of different mechanisms, like the misestimation of both the
+predator's and the preys' ranges {[}Ladle and Hortal (2013);
+Rondinini2006TraDif{]}, taxonomic errors (Isaac, Mallet, and Mace 2004;
+Ladle and Hortal 2013), or the lack of information about trophic links
+(i.e., the lack of connection between the ranges of a predator and a
+primary producer may be due a third species we don't know is connected
+to both). Thus, given that herbivores are the main connection between
+plant resources (directly limited by environmental conditions) and
+predators (Dobson 2009; Scott et al. 2018), here we adjusted the ranges
+of predators based on a simple rule: we removed any part of a predator's
+range that did not intersect with the range of at least one prey
+herbivore species. So, unless the range of the predator overlapped with
+at least one prey item, which in turn is directly connected to a primary
+producer (plants), we removed that section of the predator's range.
+Finally, we calculated the difference in range size between the original
+IUCN ranges and those adjusted based on species interaction data.
 
@@
 
-There was high variation in the overlap of predator and prey ranges
+There was a high variation in the overlap of predator and prey ranges
 (fig.~\ref{fig:geo_diss}). The high density of points on the left-hand
@@
 \begin{longtable}[]{@{}lrrrrr@{}}
-\caption{\label{tbl:everyone}List of species analyzed, their out and in
+\caption{\label{tbl:everyone}List of species analysed, their out and in
 degrees, total original range size (in pixels), and proportion of their
@@
 unclear the extent to which the patterns observed represent ecological
-processes or a lack of data. In the following sections, we discuss the
-implications of our findings, in terms of species range maps,
-interaction data, and the next steps required to enhance understanding
-of species distributions using information on ecological networks.
+processes or a lack of data.
 
@@
 interactions in habitat suitability models without making the models
-more complex, but making sure (not assuming) that the input data - the
-species occurrence - actually accounts for ecological interactions. It
-is important to notice, however, that the quality and usefulness of this
-method are highly correlated with the amount and quality of data
+more complex, but by making sure (not assuming) that the input data -
+the species occurrence - actually accounts for ecological interactions.
+It is important to notice, however, that the quality and usefulness of
+this method are highly correlated with the amount and quality of data
 available about species' occurrences \textbf{and} interactions. With
-this paper we hope to add to the collective effort to decode the
+this paper, we hope to add to the collective effort to decode the
 encrypted message that is the occurrence of a species in space and time.
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-AbregoAccSpe}{}%
+\leavevmode\hypertarget{ref-Abrego2021AccSpe}{}%
 Abrego, Nerea, Tomas Roslin, Tea Huotari, Yinqiu Ji, Niels Martin
-Schmidt, Jiaxin Wang, Douglas W. Yu, and Otso Ovaskainen. n.d.
+Schmidt, Jiaxin Wang, Douglas W. Yu, and Otso Ovaskainen. 2021.
 {``Accounting for Species Interactions Is Necessary for Predicting How
 Arctic Arthropod Communities Respond to Climate Change.''}
-\emph{Ecography} n/a (n/a). \url{https://doi.org/10.1111/ecog.05547}.
+\emph{Ecography} 44 (6): 885--96.
+\url{https://doi.org/10.1111/ecog.05547}.
 
@@
 
+\leavevmode\hypertarget{ref-Ficetola2014EvaRob}{}%
+Ficetola, Gentile Francesco, Carlo Rondinini, Anna Bonardi, Vineet
+Katariya, Emilio Padoa-Schioppa, and Ariadne Angulo. 2014. {``An
+Evaluation of the Robustness of Global Amphibian Range Maps.''}
+\emph{Journal of Biogeography} 41 (2): 211--21.
+\url{https://doi.org/10.1111/jbi.12206}.
+
 \leavevmode\hypertarget{ref-Fourcade2016ComSpe}{}%
@@
 
+\leavevmode\hypertarget{ref-Gotelli2010MacSig}{}%
+Gotelli, Nicholas J., Gary R. Graves, and Carsten Rahbek. 2010.
+{``Macroecological Signals of Species Interactions in the Danish
+Avifauna.''} \emph{Proceedings of the National Academy of Sciences} 107
+(11): 5030--35. \url{https://doi.org/10.1073/pnas.0914089107}.
+
 \leavevmode\hypertarget{ref-Herkt2017MacCon}{}%
@@
 
-\leavevmode\hypertarget{ref-IUCNSSCRedListTechnicalWorkingGroup2021MapSta}{}%
-IUCN SSC Red List Technical Working Group. 2021. \emph{Mapping Standards
-and Data Quality for IUCN Red List Spatial Data}.
+\leavevmode\hypertarget{ref-Hurlbert2007SpeRic}{}%
+Hurlbert, Allen H., and Walter Jetz. 2007. {``Species Richness,
+Hotspots, and the Scale Dependence of Range Maps in Ecology and
+Conservation.''} \emph{Proceedings of the National Academy of Sciences}
+104 (33): 13384--89. \url{https://doi.org/10.1073/pnas.0704469104}.
+
+\leavevmode\hypertarget{ref-Hurlbert2005DisRan}{}%
+Hurlbert, Allen H., and Ethan P. White. 2005. {``Disparity Between Range
+Map- and Survey-Based Analyses of Species Richness: Patterns, Processes
+and Implications.''} \emph{Ecology Letters} 8 (3): 319--27.
+\url{https://doi.org/10.1111/j.1461-0248.2005.00726.x}.
+
+\leavevmode\hypertarget{ref-Isaac2004TaxInf}{}%
+Isaac, Nick J. B., James Mallet, and Georgina M. Mace. 2004.
+{``Taxonomic Inflation: Its Influence on Macroecology and
+Conservation.''} \emph{Trends in Ecology \& Evolution} 19 (9): 464--69.
+\url{https://doi.org/10.1016/j.tree.2004.06.004}.
+
+\leavevmode\hypertarget{ref-IUCN2019MapSta}{}%
+IUCN Red List Technical Working Group. 2019. {``Mapping Standards and
+Data Quality for IUCN Red List Spatial Data.''} Prepared by the
+Standards and Petitions Working Group of the IUCN SSC Red \ldots.
 
@@
 (3): 299--307. \url{https://doi.org/10.1111/1365-2435.12356}.
+
+\leavevmode\hypertarget{ref-Wisz2013RolBio}{}%
+Wisz, Mary Susanne, Julien Pottier, W Daniel Kissling, Loïc Pellissier,
+Jonathan Lenoir, Christian F Damgaard, Carsten F Dormann, et al. 2013.
+{``The Role of Biotic Interactions in Shaping Distributions and Realised
+Assemblages of Species: Implications for Species Distribution
+Modelling.''} \emph{Biological Reviews of the Cambridge Philosophical
+Society} 88 (1): 15--30.
+\url{https://doi.org/10.1111/j.1469-185X.2012.00235.x}.
 

### 2022-07-15 code/01-load_rasters.jl
🚚 renumber all scripts in correct order

@@ -23,8 +23,8 @@ geotiff(joinpath("data", "clean", "richness.tif"), richness)
 richness = geotiff(SimpleSDMPredictor, joinpath("data", "clean", "richness.tif"))
 
 # Map the richness
-include("shapefile.jl")
-plot(; 
+include("A1_shapefile.jl")
+plot(;
     frame=:box,
     xlim=extrema(longitudes(richness)),
     ylim=extrema(latitudes(richness)),

### 2022-07-15 code/02-get_networks.jl

@@ -1,6 +1,6 @@
 # Load required scripts and packages
 include("01-load_rasters.jl") # range maps of Serengeti mammals
-include("shapefile.jl") # mapping functions
+include("A1_shapefile.jl") # mapping functions
 
 import CSV
 using DataFrames
@@ -58,7 +58,7 @@ M_plants_herb = M[vcat(plants, herbivores)]
 kout_plants_herb = collect(values(degree(M_plants_herb, dims = 1))) # out-degree of herbivores and plants
 kout_herb = kout_plants_herb[kout_plants_herb .!= 0] # out-degree of herbivores
 kout_herb_avg = mean(kout_herb) # mean out-degree of herbivores
-kout_herb_sd = std(kout_herb) 
+kout_herb_sd = std(kout_herb)
 kout_herb_ext = extrema(kout_herb)
 
 #### Build spatially-explicit networks of mammals and remove carnivores with no paths to an herbivore
@@ -208,7 +208,7 @@ plot!(worldshape(50), c=:lightgrey, lc=:lightgrey, alpha=0.6)
 plot!(delta_Sxy_layer, c=cgrad(:turku, rev=true))
 savefig(joinpath("figures", "species_removal.png"))
 
-## Map of species richness before correction 
+## Map of species richness before correction
 map_richness = plot(;
     frame=:box,
     xlim=extrema(longitudes(Sxy_layer)),
@@ -220,7 +220,7 @@ map_richness = plot(;
 plot!(worldshape(50), c=:lightgrey, lc=:lightgrey, alpha=0.6)
 plot!(Sxy_layer, c=cgrad(:turku, rev=true))
 
-## Map of proportion of species remaining after correction 
+## Map of proportion of species remaining after correction
 map_prop = plot(;
     frame=:box,
     xlim=extrema(longitudes(prop_Sxy_layer)),
@@ -232,7 +232,7 @@ map_prop = plot(;
 plot!(worldshape(50), c=:lightgrey, lc=:lightgrey, alpha=0.6)
 plot!(prop_Sxy_layer, c=cgrad(:viridis, rev=true))
 
-## Proportion of remaining species as a function of species richeness 
+## Proportion of remaining species as a function of species richeness
 index = Sxy_df.Sxy .!= nothing
 
 prop_richness = scatter(Sxy_df.Sxy[index],

### 2022-07-15 code/06-scatterplots.jl

@@ -2,7 +2,6 @@ using Base: get_preferences
 using Plots.PlotMeasures
 
 include("05-degrees.jl")
-include("07-GBIF_comparison.jl")
 
 # Remove underscores
 ranges_degrees_df.species = replace.(ranges_degrees_df.species, "_" => " ")
@@ -235,49 +234,3 @@ scatter(
     annotate = (128,10,text("Original range size (km²)", 12,  rotation = 270))
 )
 savefig(joinpath("figures", "rel_lost-in_degree-species-and-range.png"))
-
-# Exploring occurrences
-i_ex = indexin(["Canis_aureus"], mammals)[1]
-plot(;
-    frame=:box,
-    xlim=extrema(longitudes(delta_Sxy_layer)),
-    ylim=extrema(latitudes(delta_Sxy_layer)),
-    dpi=500,
-    xaxis="Longitude",
-    yaxis="Latitude",
-)
-plot!(worldshape(50); c=:lightgrey, lc=:lightgrey, alpha=0.6)
-plot!(ranges[i_ex]; c=:turku, colorbar=:none)
-scatter!(
-    occ_df[occ_df.species .== mammals[i_ex], :longitude],
-    occ_df[occ_df.species .== mammals[i_ex], :latitude];
-    markerstrokewidth=0,
-    markeralpha=0.5,
-    markersize=2,
-    title=replace(mammals[i_ex], "_" => " "),
-    legend=:none,
-)
-savefig(joinpath("figures", "ranges", "iucn_gbif_ex.png"))
-
-for i in eachindex(mammals)
-    plot(;
-        frame=:box,
-        xlim=extrema(longitudes(delta_Sxy_layer)),
-        ylim=extrema(latitudes(delta_Sxy_layer)),
-        dpi=500,
-        xaxis="Longitude",
-        yaxis="Latitude",
-    )
-    plot!(worldshape(50); c=:lightgrey, lc=:lightgrey, alpha=0.6)
-    plot!(ranges[i]; c=:turku, colorbar=:none)
-    scatter!(
-        occ_df[occ_df.species .== mammals[i], :longitude],
-        occ_df[occ_df.species .== mammals[i], :latitude];
-        markerstrokewidth=0,
-        markeralpha=0.5,
-        markersize=2,
-        title=replace(mammals[i], "_" => " "),
-        legend=:none,
-    )
-    savefig(joinpath("figures", "ranges", "iucn_gbif" * mammals[i] * ".png"))
-end

### 2022-07-15 code/09-GBIF_data.jl

@@ -1,6 +1,6 @@
 # Load required scripts and packages
 include("01-load_rasters.jl") # range maps of Serengeti mammals
-include("shapefile.jl") # mapping functions
+include("A1_shapefile.jl") # mapping functions
 
 using CSV
 using GBIF

### 2022-07-15 code/10-GBIF_comparison.jl

@@ -13,7 +13,7 @@ using Statistics
 using StatsPlots
 using SimpleSDMLayers
 
-include("shapefile.jl") # mapping functions
+include("A1_shapefile.jl") # mapping functions
 
 ## Load required data
 
@@ -231,3 +231,27 @@ plot(
     bottommargin=50px
 )
 savefig(joinpath("figures", "gbif_panels.png"))
+
+## Plot all species distributions with GBIF observations on top
+for i in eachindex(mammals)
+    plot(;
+        frame=:box,
+        xlim=extrema(longitudes(ranges[i])),
+        ylim=extrema(latitudes(ranges[i])),
+        dpi=500,
+        xaxis="Longitude",
+        yaxis="Latitude",
+    )
+    plot!(worldshape(50); c=:lightgrey, lc=:lightgrey, alpha=0.6)
+    plot!(ranges[i]; c=:turku, colorbar=:none)
+    scatter!(
+        occ_df[occ_df.species .== mammals[i], :longitude],
+        occ_df[occ_df.species .== mammals[i], :latitude];
+        markerstrokewidth=0,
+        markeralpha=0.5,
+        markersize=2,
+        title=replace(mammals[i], "_" => " "),
+        legend=:none,
+    )
+    savefig(joinpath("figures", "ranges", "iucn_gbif" * mammals[i] * ".png"))
+end

### 2022-07-15 code/11-GBIF_doublecheck.jl

@@ -63,7 +63,7 @@ prey_mismatch = similar(serval_loss)
 prey_mismatch[_prey_sites] = fill(1.0, length(_prey_sites))
 
 # Map the mismatch
-include("shapefile.jl")
+include("A1_shapefile.jl")
 begin
     plot(;
         frame=:box,

### 2022-07-15 code/00_get_rasters.jl
🔧 combine all package loading in one script

@@ -1,9 +1,3 @@
-import Pkg; Pkg.activate(".")
-
-using SimpleSDMLayers
-using CSV
-using DataFrames
-
 # I store my IUCN data in the same location, so adapt this to where your files are
 const IUCNPATH = expanduser(joinpath("~", ".data", "iucn"))
 const IUCNDB = "MAMMALS"

### 2022-07-15 code/01-load_rasters.jl

@@ -1,10 +1,3 @@
-import Pkg; Pkg.activate("."); Pkg.instantiate()
-
-using SimpleSDMLayers
-using Plots
-using Shapefile
-using DataFrames
-
 # This is the bounding box we care about
 bounding_box = (left=-20.0, right=55.0, bottom=-35.0, top=40.0)
 
@@ -23,7 +16,7 @@ geotiff(joinpath("data", "clean", "richness.tif"), richness)
 richness = geotiff(SimpleSDMPredictor, joinpath("data", "clean", "richness.tif"))
 
 # Map the richness
-include("A1_shapefile.jl")
+include("A2_shapefile.jl")
 plot(;
     frame=:box,
     xlim=extrema(longitudes(richness)),

### 2022-07-15 code/02-get_networks.jl

@@ -1,12 +1,5 @@
 # Load required scripts and packages
 include("01-load_rasters.jl") # range maps of Serengeti mammals
-include("A1_shapefile.jl") # mapping functions
-
-import CSV
-using DataFrames
-using EcologicalNetworks
-using SparseArrays
-using Statistics
 
 #### Build metawebs
 

### 2022-07-15 code/03-analyse_cooccurrence.jl

@@ -1,7 +1,5 @@
 include("02-get_networks.jl")
 
-using Combinatorics
-
 # Mammals in the Serengeti ecosystem
 mammals = readlines(joinpath("data", "clean", "mammals.csv"))
 

### 2022-07-15 code/06-scatterplots.jl

@@ -1,6 +1,3 @@
-using Base: get_preferences
-using Plots.PlotMeasures
-
 include("05-degrees.jl")
 
 # Remove underscores

### 2022-07-15 code/08-export_table.jl

@@ -1,9 +1,5 @@
 ## Export as markdown table
 
-using CSV
-using DataFrames
-using Latexify
-
 # Load ranges results & species groups
 results = CSV.read(joinpath("data", "clean", "range_proportions.csv"), DataFrame)
 sp_groups = CSV.read(joinpath("data", "species_groups.csv"), DataFrame)

### 2022-07-15 code/09-GBIF_data.jl

@@ -1,10 +1,5 @@
 # Load required scripts and packages
 include("01-load_rasters.jl") # range maps of Serengeti mammals
-include("A1_shapefile.jl") # mapping functions
-
-using CSV
-using GBIF
-using DataFramesMeta
 
 # Getting taxa codes
 sp_codes = taxon.(mammals, rank = :SPECIES)

### 2022-07-15 code/10-GBIF_comparison.jl

@@ -1,20 +1,3 @@
-## Load required scripts and packages
-import Pkg; Pkg.activate("."); Pkg.instantiate()
-
-using CSV
-using DataFrames
-using DataFramesMeta
-using GBIF
-using Latexify
-using Plots
-using Plots.PlotMeasures
-using Shapefile
-using Statistics
-using StatsPlots
-using SimpleSDMLayers
-
-include("A1_shapefile.jl") # mapping functions
-
 ## Load required data
 
 # This is the bounding box we care about

### 2022-07-15 code/11-GBIF_doublecheck.jl

@@ -1,12 +1,4 @@
-using SimpleSDMLayers
-using Plots
-using Plots.PlotMeasures
-using Shapefile
-using DataFramesMeta
-using GBIF
-using CSV
-using Statistics
-using StatsPlots
+include("A1_required.jl")
 
 # Load IUCN ranges
 mammals = readlines(joinpath("data", "clean", "mammals.csv"))
@@ -63,7 +55,7 @@ prey_mismatch = similar(serval_loss)
 prey_mismatch[_prey_sites] = fill(1.0, length(_prey_sites))
 
 # Map the mismatch
-include("A1_shapefile.jl")
+include("A2_shapefile.jl")
 begin
     plot(;
         frame=:box,

### 2022-07-15 code/A1_required.jl

@@ -1,0 +1,20 @@
+## Load required scripts and packages
+import Pkg; Pkg.activate("."); Pkg.instantiate()
+
+using Combinatorics
+using CSV
+using DataFramesMeta
+using EcologicalNetworks
+using GBIF
+using GLM
+using JLD2
+using Latexify
+using Plots
+using Plots.PlotMeasures
+using Shapefile
+using SimpleSDMLayers
+using SparseArrays
+using Statistics
+using StatsPlots
+
+include("A2_shapefile.jl") # mapping functions

### 2022-07-15 code/00_get_rasters.jl
🔧 all scripts need the package loading script

@@ -1,3 +1,5 @@
+include("A1_required.jl")
+
 # I store my IUCN data in the same location, so adapt this to where your files are
 const IUCNPATH = expanduser(joinpath("~", ".data", "iucn"))
 const IUCNDB = "MAMMALS"

### 2022-07-15 code/01-load_rasters.jl

@@ -1,3 +1,5 @@
+include("A1_required.jl")
+
 # This is the bounding box we care about
 bounding_box = (left=-20.0, right=55.0, bottom=-35.0, top=40.0)
 
@@ -16,7 +18,6 @@ geotiff(joinpath("data", "clean", "richness.tif"), richness)
 richness = geotiff(SimpleSDMPredictor, joinpath("data", "clean", "richness.tif"))
 
 # Map the richness
-include("A2_shapefile.jl")
 plot(;
     frame=:box,
     xlim=extrema(longitudes(richness)),

### 2022-07-15 code/03-analyse_cooccurrence.jl

@@ -1,3 +1,5 @@
+include("A1_required.jl")
+
 include("02-get_networks.jl")
 
 # Mammals in the Serengeti ecosystem

### 2022-07-15 code/04-ranges_diff.jl

@@ -1,3 +1,5 @@
+include("A1_required.jl")
+
 include("03-analyse_cooccurrence.jl")
 
 short_list = filter(!isnothing, species_lists_corr)

### 2022-07-15 code/06-scatterplots.jl

@@ -1,3 +1,5 @@
+include("A1_required.jl")
+
 include("05-degrees.jl")
 
 # Remove underscores

### 2022-07-15 code/07-updated_ranges.jl

@@ -1,3 +1,5 @@
+include("A1_required.jl")
+
 include("02-get_networks.jl")
 
 ## Load required data

### 2022-07-15 code/08-export_table.jl

@@ -1,3 +1,5 @@
+include("A1_required.jl")
+
 ## Export as markdown table
 
 # Load ranges results & species groups

### 2022-07-15 code/09-GBIF_data.jl

@@ -1,3 +1,5 @@
+include("A1_required.jl")
+
 # Load required scripts and packages
 include("01-load_rasters.jl") # range maps of Serengeti mammals
 

### 2022-07-15 code/10-GBIF_comparison.jl

@@ -1,3 +1,5 @@
+include("A1_required.jl")
+
 ## Load required data
 
 # This is the bounding box we care about

### 2022-07-15 code/11-GBIF_doublecheck.jl

@@ -55,7 +55,6 @@ prey_mismatch = similar(serval_loss)
 prey_mismatch[_prey_sites] = fill(1.0, length(_prey_sites))
 
 # Map the mismatch
-include("A2_shapefile.jl")
 begin
     plot(;
         frame=:box,

### 2022-07-15 response-letter.md
Update response-letter.md
:memo: add points about data retrieval

@@
 retrieving is detailed in the source code provided on our GitHub repository
-(code/06-GBIF_data.jl). We used the list of species from the network dataset and
+(code/09-GBIF_data.jl). We used the list of species from the network dataset and
 retrieved any occurrence within our bounding box (between longitudes -20.0 and
-55.0 degrees; and latitudes -35.0 and 40.0 degrees). Some taxonomic
-investigation needed to be done due to inconsistencies between GBIF and IUCN
-nomenclatures (in the case of _Taurotragus oryx_). We didn't perform any further
-data cleaning procedures because this could hinder the goals of the paper, which
-was to investigate the characteristics of the data available for research. As we
-needed to compare two sets of raw data, and data cleaning protocols are
-dependent on the use objectives, we chose to avoid data manipulation both for
-GBIF and IUCN datasets.
+55.0 degrees; and latitudes -35.0 and 40.0 degrees). We changed a two things
+regarding geographical information during data retrieval:
+1. We had originally added an argument to capture only the data that had
+   information about the continent location equals to "AFRICA". However, this
+   constrained our search by thousands of occurrences, and added a filtering
+   layer that could be interpreted as "data cleaning". We removed that because
+   we don't perform any kind of data cleaning with the IUCN dataset.
+
+2. We added, however, a constraint to exclude occurrences falling within a 4°x4°
+   degrees square around the "Null Island" (see code/09-GBIF_data.jl#L42 on our
+   repository). Rather than a data cleaning step, we see this as a geographic
+   filter complementing the bounding box we used to retrieve data from GBIF and
+   to limit IUCN range maps. This is important because the existence of
+   coordinates is a fundamental part of our analysis, and a (00,00) coordinate
+   can be interpreted as a null coordinate.
+
+Some taxonomic investigation needed to be done due to inconsistencies between
+GBIF and IUCN nomenclatures which would block our analysis completely (in the case of _Taurotragus oryx_).
+However, in the case of *Canis aureus*, as discussed in the paper, we could not track wich occurrences or which maps corresponded to which species, which we think is a great illustration of our point.
+We didn't
+perform any further data cleaning procedures because this could hinder the goals
+of the paper, which was to investigate the characteristics of the data available
+for research. As we needed to compare two sets of raw data, and data cleaning
+protocols are dependent on the use objectives, we chose to avoid data
+manipulation both for GBIF and IUCN datasets.
 
@@
 described below:
-- We've added citations on the Methods section to support our argument that a
+- We've added citations in the Methods section to support our argument that a
   mismatch between ranges can be originated from different sources (L. 68-70)
@@
 - We have addressed the grammatical suggestions throughout the text, except for
-  the legend of figure 5. We thought that the suggested phrasing adds a little
+  the legend of figure 1. We thought that the suggested phrasing adds a little
   bit of confusion to the comprehension of the figure.

### 2022-07-15 code/02-get_networks.jl
🔧 reduce need to rerun scripts over and over

@@ -33,6 +33,10 @@ vals = ones(Bool, L)
 M = sparse(rows, cols, vals, S, S)
 M = UnipartiteNetwork(Matrix(M), sp.species)
 
+# Export trophic levels for later use
+trophic_df = DataFrame(species = collect(keys(trophic_level(M))), level = collect(values(trophic_level(M))))
+CSV.write(joinpath("data", "clean", "trophic_levels.csv"), trophic_df)
+
 # Get list of plants and mammals (carnivores and herbivores)
 plants = sp.species[sp.type .== "plant"]
 mammals = sp.species[sp.type .!== "plant"]
@@ -46,6 +50,11 @@ end
 
 # Build metaweb of mammals (subnetwork of metaweb of mammals and plants)
 MM = M[mammals]
+
+# Export metaweb as DataFrame
+interactions_df = DataFrame(interactions(MM))
+rename!(interactions_df, :from => :pred, :to => :prey)
+CSV.write(joinpath("data", "clean", "metaweb.csv"), interactions_df)
 
 # Count the number of plants that are eaten by each herbivores
 M_plants_herb = M[vcat(plants, herbivores)]
@@ -189,6 +198,8 @@ Sxy_layer = SimpleSDMPredictor(Sxy_df, :Sxy, ranges[1])
 delta_Sxy_layer = SimpleSDMPredictor(Sxy_df, :delta_Sxy, ranges[1])
 prop_Sxy_layer = SimpleSDMPredictor(Sxy_df, :prop_Sxy, ranges[1])
 
+# Export as tif
+geotiff(joinpath("data", "clean", "richness_diff.tif"), delta_Sxy_layer)
 
 # Map differences in species richness
 plot(;

### 2022-07-15 code/03-analyse_cooccurrence.jl

@@ -2,9 +2,6 @@ include("A1_required.jl")
 
 include("02-get_networks.jl")
 
-# Mammals in the Serengeti ecosystem
-mammals = readlines(joinpath("data", "clean", "mammals.csv"))
-
 # Subset subnetwork using this list of mammals
 MM = MM[mammals]
 

### 2022-07-15 code/07-updated_ranges.jl

@@ -1,15 +1,13 @@
 include("A1_required.jl")
 
-include("02-get_networks.jl")
-
 ## Load required data
 
 # Get ranges
 ranges = [geotiff(SimpleSDMPredictor, joinpath("data", "clean", "stack.tif"), i) for i in eachindex(mammals)]
+ranges_updated = [geotiff(SimpleSDMPredictor, joinpath("data", "clean", "ranges_updated.tif"), i) for i in eachindex(mammals)]
 
-# List interactions in DataFrame
-interactions_df = DataFrame(interactions(MM))
-rename!(interactions_df, :from => :pred, :to => :prey)
+# Get list interactions in DataFrame
+interactions_df = CSV.read(joinpath("data", "clean", "metaweb.csv"), DataFrame)
 
 # Separate predators & preys
 predators = unique(interactions_df.pred)
@@ -112,9 +110,10 @@ missing_species_df = DataFrame(
 append!(results, missing_species_df; cols=:union)
 
 # Sort by trophic level
-results = leftjoin(results, DataFrame(species = species(M), trophic_levels = floor.(values(trophic_level(M)))), on = :species)
-sort!(results, :trophic_levels, rev=true)
-results = results[!, Not(:trophic_levels)]
+trophic_df = CSV.read(joinpath("data", "clean", "trophic_levels.csv"), DataFrame)
+results = leftjoin(results, trophic_df, on = :species)
+sort!(results, :level, rev=true)
+results = results[!, Not(:level)]
 
 # Export to CSV
 CSV.write(joinpath("data", "clean", "range_proportions.csv"), results)
@@ -133,8 +132,6 @@ plot(richness_updated, c=:turku)
 richness_diff = richness_original - replace(richness_updated, nothing => 0.0)
 
 plot(replace(richness_diff, 0.0 => nothing), c=:turku)
-plot(delta_Sxy_layer, c=:turku)
-replace(richness_diff, 0.0 => nothing) == delta_Sxy_layer # true if intermediate predators filtered earlier
 
 # Export nicer plot
 plot(;

### 2022-07-15 code/09-GBIF_data.jl

@@ -1,8 +1,5 @@
 include("A1_required.jl")
 
-# Load required scripts and packages
-include("01-load_rasters.jl") # range maps of Serengeti mammals
-
 # Getting taxa codes
 sp_codes = taxon.(mammals, rank = :SPECIES)
 
@@ -26,7 +23,6 @@ Threads.@threads for o in occ
 end
 # Export to JLD2 for faster reload
 #=
-using JLD2
 @save joinpath("data", "clean", "gbif-occurrences.jld2") occ
 @load joinpath("data", "clean", "gbif-occurrences.jld2") occ
 =#
@@ -78,8 +74,6 @@ diff
 
 # Create background layer
 bglayer = SimpleSDMPredictor(WorldClim, BioClim, 1; bounding_box...)
-boundingbox(bglayer) == boundingbox(ranges[1]) || @error "background layer bounding box is different from range layer bounding box"
-size(bglayer) == size(ranges[1]) || @error "background layer size is different from range layer size"
 
 # Create an abundance layer (number of GBIF occurrences per pixel)
 gbif_occ_layers = [mask(bglayer, o, Float64) for o in occ]

### 2022-07-15 code/A1_required.jl

@@ -18,3 +18,11 @@ using Statistics
 using StatsPlots
 
 include("A2_shapefile.jl") # mapping functions
+
+## Objects needed in most scripts
+
+# This is the bounding box we care about
+bounding_box = (left=-20.0, right=55.0, bottom=-35.0, top=40.0);
+
+# Get the list of mammals
+mammals = readlines(joinpath("data", "clean", "mammals.csv"));

### 2022-07-15 draft.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@f0df5760733f9e4661a0419c313416a90f10cd3f 🚀

@@
 occurrence and interaction data is a frequent debate in ecology
-{[}Blanchet, Cazelles, and Gravel (2020); Wisz2013RolBio{]}. For
-instance, macroecological models are often used with point or range
-occurrence data in order to investigate the dynamics of a species with
-its environment. However, these models do not account for ecological
+(Blanchet, Cazelles, and Gravel 2020; Wisz et al. 2013). For instance,
+macroecological models are often used with point or range occurrence
+data in order to investigate the dynamics of a species with its
+environment. However, these models do not account for ecological
 interactions, although it has been demonstrated that they might largely
-affect species distribution {[}Abrego et al. (2021); Afkhami, McIntyre,
-and Strauss (2014); Araújo, Marcondes-Machado, and Costa (2014); Godsoe
-et al. (2017); Godsoe and Harmon (2012); Gotelli, Graves, and Rahbek
-(2010); Wisz2013RolBio{]}. Some researchers argue that occurrence data
-can also capture real-time interactions (see Roy et al. 2016; Ryan et
-al. 2018), and, because of that, it would not be necessary to include
-ecological interaction dynamics in macroecological models. On the other
-hand, many mechanistic simulation models in ecology have considered the
-effect of competition and facilitation in range shifts. For example,
-Gotelli \emph{et al.} -(Gotelli, Graves, and Rahbek 2010) demonstrate
-how conspecific attraction might be the main factor driving the
-distribution of migratory birds; Afkhami \emph{et al.} -(Afkhami,
-McIntyre, and Strauss 2014) explores how mutualistic fungal endophytes
-are responsible or expanding the range of native grass; many other
-examples are discussed in Wisz \emph{et al.} -(Wisz et al. 2013).
-Although interactions across trophic levels are demonstrated to
-determine species range (Wisz et al. 2013), the use of these
-interactions in mechanistic simulation models in macroecology remains
-insufficient (as discussed in Cabral, Valente, and Hartig 2017).
+affect species distribution (Abrego et al. 2021; Afkhami, McIntyre, and
+Strauss 2014; Araújo, Marcondes-Machado, and Costa 2014; Godsoe et al.
+2017; Godsoe and Harmon 2012; Gotelli, Graves, and Rahbek 2010; Wisz et
+al. 2013). Some researchers argue that occurrence data can also capture
+real-time interactions (see Roy et al. 2016; Ryan et al. 2018), and,
+because of that, it would not be necessary to include ecological
+interaction dynamics in macroecological models. On the other hand, many
+mechanistic simulation models in ecology have considered the effect of
+competition and facilitation in range shifts. For example, Gotelli
+\emph{et al.} (2010) demonstrate how conspecific attraction might be the
+main factor driving the distribution of migratory birds; Afkhami
+\emph{et al.} (2014) explores how mutualistic fungal endophytes are
+responsible or expanding the range of native grass; many other examples
+are discussed in Wisz \emph{et al.} (2013). Although interactions across
+trophic levels are demonstrated to determine species range (Wisz et al.
+2013), the use of these interactions in mechanistic simulation models in
+macroecology remains insufficient (as discussed in Cabral, Valente, and
+Hartig 2017).
 
@@
 (Herkt, Skidmore, and Fahr 2017) (especially at fine scale resolutions;
-(Hurlbert and Jetz 2007; Hurlbert and White 2005)), do not represent
+Hurlbert and Jetz (2007); Hurlbert and White (2005)), do not represent
 spatial variation in species occurrence and abundance (Dallas, Pironon,
@@
 result of different mechanisms, like the misestimation of both the
-predator's and the preys' ranges {[}Ladle and Hortal (2013);
-Rondinini2006TraDif{]}, taxonomic errors (Isaac, Mallet, and Mace 2004;
-Ladle and Hortal 2013), or the lack of information about trophic links
-(i.e., the lack of connection between the ranges of a predator and a
-primary producer may be due a third species we don't know is connected
-to both). Thus, given that herbivores are the main connection between
-plant resources (directly limited by environmental conditions) and
-predators (Dobson 2009; Scott et al. 2018), here we adjusted the ranges
-of predators based on a simple rule: we removed any part of a predator's
+predator's and the preys' ranges (Ladle and Hortal 2013; Rondinini et
+al. 2006), taxonomic errors (Isaac, Mallet, and Mace 2004; Ladle and
+Hortal 2013), or the lack of information about trophic links (i.e., the
+lack of connection between the ranges of a predator and a primary
+producer may be due a third species we don't know is connected to both).
+Thus, given that herbivores are the main connection between plant
+resources (directly limited by environmental conditions) and predators
+(Dobson 2009; Scott et al. 2018), here we adjusted the ranges of
+predators based on a simple rule: we removed any part of a predator's
 range that did not intersect with the range of at least one prey
@@
 The proportion of GBIF pixels (pixels with at least one GBIF occurrence)
-falling in the IUCN ranges varied from low to high depending on the
+falling within the IUCN ranges varied from low to high depending on the
 species (fig.~\ref{fig:gbif}, left). The lowest proportions occurred for
-species with small ranges (such as \emph{Lycaon pictus}), although some
-species with small ranges showed high overlap. Species with median and
-large ranges had high proportions of occurrences falling into their IUCN
-range. Predators and preys displayed similar overlap variations. While
-no species had all of its GBIF occurrences within its IUCN range, one
-species had this proportion equal to zero, \emph{Canis aureus}, which is
-also the only species whose range is not covered by any of its preys.
-This result reinforces the concern raised in the literature on the use
-of IUCN range maps for species that are not well known (Herkt, Skidmore,
-and Fahr 2017), demonstrating how small range species are likely to have
-their distribution underestimated in the IUCN database. Additionally,
-the fact that \emph{Canis aureus} had none of its GBIF pixels
-overlapping with IUCN maps suggests a taxonomic mismatch between both
-databases, which we explore in the Discussion section.
+species with small ranges. Amongst herbivores, \emph{Rhabdomys pumilio}
+has a proportion of 22.6\% of its presence pixels within its IUCN range,
+while predators have this proportion above 55\% (such as \emph{Lycaon
+pictus}, with 55.1\%, and \emph{Canis aureus}, with 56.2\%).
+Nevertheless, some species with smaller ranges showed high data overlap
+(such as \emph{Canis mesomelas}, with 94.9\%, and many herbivores).
+Overall, predators and preys displayed similar overlap variations, and
+species with median and large ranges had higher proportions of
+occurrences falling into their IUCN range.
 
@@
 original IUCN ranges for most predator species (fig.~\ref{fig:gbif}).
-Four species showed no difference in proportion while three species
-showed only small differences (proportions of 0.01 to 0.05). On the
-other hand, two species, \emph{Canis mesomelas}, and \emph{Leptailurus
-serval} showed very high differences, with overlaps lower by 0.548 and
-0.871 respectively. For \emph{Leptailurus serval}, none of the GBIF
-observations occurred in the updated range. These two species are also
-the only predators with a single prey in our metaweb. Our results
-delineate how a mismatch between GBIF and IUCN databases differ greatly
-with small changes in herbivore species ranges, and it is somewhat
-positively related to range size for predator species. Moreover, we show
-that accounting for interactions does not necessarily aggravates this
-dissimilarity, but it is relevant for species with little ecological
-information or specialists.
+Two species showed no difference in proportion while four species showed
+only small differences (\emph{Crocuta crocuta} lost 1.3\% of the
+original data overlap; \emph{Acinonyx jubatus} lost 1.9\%;
+\emph{Panthera pardus} lost 8.8\%; and \emph{Caracal caracal} lost
+12.3\%). \textless!---\textgreater Note to self: here I calculated how
+much the difference represents as a proportion of the total proportion,
+which means the decreased rate. E.g., when the range\_prop\_diff is
+equal to the original proportion (range\_prop), this means that this
+species lost 100\% of the original proportion. Therefore I can't use
+range\_prop\_diff numbers if I'm talking about \%
+lost.\textless---\textgreater{} On the other hand, three species,
+\emph{Canis aureus}, \emph{Canis mesomelas}, and \emph{Leptailurus
+serval} showed very high differences, with overlaps lowered by 100\%,
+57.4\%, and 100\% respectively. These last two species are also the only
+predators with a single prey in our metaweb. \emph{Canis aureus} has
+four preys, but it has one of the smallest ranges in IUCN, which is not
+covered by any of its preys. This result reinforces the concern raised
+in the literature on the use of IUCN range maps for species that are not
+well known (Herkt, Skidmore, and Fahr 2017), demonstrating how small
+range species are likely to have their distribution underestimated in
+the IUCN database. Additionally, the fact that \emph{Canis aureus} had
+such a conspicuous mismatch between both the original and updated IUCN
+range maps, and between GBIF and IUCN data, may indicate a taxonomic
+incongruency between the three databases used here, which we explore in
+the Discussion section. Our results delineate how a mismatch between
+GBIF and IUCN databases differ greatly with small changes in herbivore
+species ranges, and it is somewhat positively related to range size for
+predator species. Moreover, we show that accounting for interactions
+does not necessarily aggravates this dissimilarity, but it is relevant
+for species with little ecological information or specialists.
 
@@
 clustering of species and subspecies (Krofel et al. 2021; Stoyanov
-2020). This debate is indeed reflected in our analysis: the GBIF
-identification of the golden jackal is incompatible with the one used by
-IUCN, each of them mapping its distribution in completely different
-places. This led to a complete exclusion of \emph{Canis aureus} from its
-original range in our analysis, despite the fact that this species has
-four documented preys in our metaweb. This example illustrates how the
-taxonomic, geographical and ecological data can be used to validate one
-another.
+2020). This debate probably influenced our results: with originally only
+56.2\% of the GBIF pixels of the golden jackal (\emph{Canis aureus})
+overlapping with the IUCN data, we suspect that many of the GBIF
+occurrences refer to other \emph{Canis} species, and that its taxonomic
+identification in the network database is probably outdated. This led to
+a complete exclusion of \emph{Canis aureus} from its original range in
+our analysis, despite the fact that this species has four documented
+preys in our metaweb. This example illustrates how the taxonomic,
+geographical and ecological data can be used to validate one another.
 
@@
 In the Serengeti food web there is a positive relationship between the
-out degrees of predators and the size of their ranges. In addition, our
-results show that there is a negative relationship between the relative
-loss of predators' ranges and their number of preys, reinforcing the
-idea that generalist species can preserve their distributions longer
-while losing interactions. The factors limiting the geographical range
-of a species in a community can vary with connectivity and richness
-(Svenning et al. 2014). Younger communities may be more affected by
-environmental limitations because they are dominated by generalist
-species, while older metacommunities are probably affected in different
-ways in the center of the distribution, at the edge of ranges, and in
-sink and source communities (Svenning et al. 2014; Godsoe et al. 2017;
-Cazelles et al. 2016; Bullock et al. 2000). Additionally, it is likely
-that species with larger ranges of distribution and those that are more
+out degrees of predators and the size of their ranges. Here, we showed
+that there is a negative relationship between the relative loss of
+predators' ranges and their number of preys, reinforcing the idea that
+generalist species can preserve their distributions longer while losing
+interactions. The factors limiting the geographical range of a species
+in a community can vary with connectivity and richness (Svenning et al.
+2014). Younger communities may be more affected by environmental
+limitations because they are dominated by generalist species, while
+older metacommunities are probably affected in different ways in the
+center of the distribution, at the edge of ranges, and in sink and
+source communities (Svenning et al. 2014; Godsoe et al. 2017; Cazelles
+et al. 2016; Bullock et al. 2000). Additionally, it is likely that
+species with larger ranges of distribution and those that are more
 generalists would co-occur with a greater number of other species
@@
 suggests that we certainly do miss geographical information about the
-distribution of a certain species, but it is not an indicator of the
+distribution of a certain species, but this is not an indicator of the
 completeness of the information about ecological interactions. However,
@@
 to have a clearer idea of which information we are missing. For example,
-the lion (\emph{Panthera leo}) was one of the species with the smallest
-difference between the original and the updated ranges, but 59.5\% of
-the GBIF occurrences for this species fell outside the IUCN range
+the lion (\emph{Panthera leo}) was one of the species with no difference
+between the original and the updated ranges, but 40.7\% of the GBIF
+occurrences for this species fell outside its IUCN range
 (fig.~\ref{fig:gbif}). In this particular case, the IUCN maps seem to
@@
 a mobility buffer around each point (fig.~\ref{fig:serval}). When
-considering GBIF data, approximately 53\% of the prey's occurrences are
+considering GBIF data, approximately 42\% of the prey's occurrences are
 within the portion of the serval's range that was lost. With the buffer
-area, this corresponds to 13\% of the lost range. This means that by
+area, this corresponds to 15\% of the lost range. This means that by
 adding GBIF information, we would reduce the loss of range (or
-information) for the predator by 13\% since its distribution is
+information) for the predator by 15\% since its distribution is
 conditional on the occurrence of its preys.
@@
 Finally, the extreme case of \emph{Canis aureus} illustrates a lack of
-both geographical and ecological information: none of its GBIF
-occurrences and none of its preys occur inside its IUCN range. We
+both geographical and ecological information: only half of its GBIF
+presence pixels and none of its preys occur inside its IUCN range. We
 believe, therefore, that the validation of species distribution based on
@@
 become available. This would help clarify when cooccurrences can be
-translated into interactions and help the development of more advanced
-validation methods for occurrence data.
+translated into interactions (Windsor et al. 2022) and help the
+development of more advanced validation methods for occurrence data.
 
@@
 A promising avenue that adds to our method is the prediction of networks
-and interactions in large scales (Strydom et al. 2021), for they can add
-valuable information about ecological interactions where they are
-missing. Additionally, in order to achieve a robust modelling framework
-towards actual species distribution models we should invest in efforts
-to collect and combine open data on species occurrence and interactions,
-especially because we may be losing ecological interactions at least as
-fast as we are losing species (Valiente-Banuet et al. 2015).
+and interactions in large scales (Strydom et al. 2021; Windsor et al.
+2022), for they can add valuable information about ecological
+interactions where they are missing. Additionally, in order to achieve a
+robust modelling framework towards actual species distribution models we
+should invest in efforts to collect and combine open data on species
+occurrence and interactions (Windsor et al. 2022), especially because we
+may be losing ecological interactions at least as fast as we are losing
+species (Valiente-Banuet et al. 2015).
 
@@
 funded by a donation from the Courtois Foundation; GD is funded by the
-FRQNT doctoral scholarship; TP is funded by the Canadian Institute of
-Ecology \& Evolution; FW is funded by the Royal Society (Grant number:
-CHL\textbackslash R1\textbackslash180156).
+Natural Sciences and Engineering Research Council (NSERC) and the Fond
+de recherche du Québec - Nature et technologie (FRQNT) doctoral
+scholarships; TP is funded by the Canadian Institute of Ecology \&
+Evolution; FW is funded by the Royal Society (Grant number:
+CHL\textbackslash R1\textbackslash180156). We thank the editor and
+reviewer for their thoughtful comments, which considerably improved this
+manuscript.
 
@@
 
+\leavevmode\hypertarget{ref-Rondinini2006TraDif}{}%
+Rondinini, Carlo, Kerrie A. Wilson, Luigi Boitani, Hedley Grantham, and
+Hugh P. Possingham. 2006. {``Tradeoffs of Different Types of Species
+Occurrence Data for Use in Systematic Conservation Planning.''}
+\emph{Ecology Letters} 9 (10): 1136--45.
+\url{https://doi.org/10.1111/j.1461-0248.2006.00970.x}.
+
 \leavevmode\hypertarget{ref-Ronquillo2020AssSpa}{}%
@@
 (3): 299--307. \url{https://doi.org/10.1111/1365-2435.12356}.
+
+\leavevmode\hypertarget{ref-Windsor2022UsiEco}{}%
+Windsor, Fredric M., Johan van den Hoogen, Thomas W. Crowther, and
+Darren M. Evans. 2022. {``Using Ecological Networks to Answer Questions
+in Global Biogeography and Ecology.''} \emph{Journal of Biogeography}
+n/a (n/a). \url{https://doi.org/10.1111/jbi.14447}.
 

### 2022-07-15 draft.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@af47296c0554e5ff4be07181cc68d909ca2fb7f8 🚀

@@
 combined different types of occurrence data to measure the accuracy of
-datasets (Hurlbert and Jetz 2007; Hurlbert and White 2005; Ficetola et
-al. 2014), none have used different types of information so far (i.e.,
-ecological characteristics other than geographical distribution). Here
-we suggest jointly analysing species occurrence (range maps and point
-occurrences) and ecological interactions to identify mismatches between
-datasets.
+datasets (Hurlbert and Jetz 2007; Hurlbert and White 2005;
+\textbf{Ficetola2014EvaRob?}), none have used different types of
+information so far (i.e., ecological characteristics other than
+geographical distribution). Here we suggest jointly analysing species
+occurrence (range maps and point occurrences) and ecological
+interactions to identify mismatches between datasets.
 
@@
 data varies geographically (Hurlbert and Jetz 2007; Hurlbert and White
-2005; Ficetola et al. 2014). Adding ecological interaction data to this
-comparison might help to elucidate where these (dis)agreements are more
-likely to be true and which dataset better represent the actual
+2005; \textbf{Ficetola2014EvaRob?}). Adding ecological interaction data
+to this comparison might help to elucidate where these (dis)agreements
+are more likely to be true and which dataset better represent the actual
 distribution of species. In this context, we elaborate a method that
@@
 (www.iucnredlist.org/resources/spatial-data-download), which we
-rasterized at 10 arc-minute resolution (\textasciitilde19 km² at the
-equator). We then combined interaction data from the metaweb and
-cooccurrence data generated from species ranges to create networks for
-each raster pixel. This generated a total of 84,244 pixel-level
-networks. These networks describe potential predation, not actual
-interactions: the former is derived information from the metaweb, and
-the latter is contingent on the presence of herbivores.
+rasterized at 10 arc-minute resolution (\textasciitilde18 km at the
+equator). We restricted the rasters a spatial extent comprised between
+latitudes 35°S and 40°N and longitudes 20°W and 55°E. We then combined
+interaction data from the metaweb and cooccurrence data generated from
+species ranges to create networks for each raster pixel. This generated
+a total of 84,244 pixel-level networks. These networks describe
+potential predation, not actual interactions: the former is derived
+information from the metaweb, and the latter is contingent on the
+presence of herbivores.
 
@@
 For each species in the dataset we collated point observation data from
-GBIF (www.gbif.org), and condensed these data into pixels representing
-presence or absence of the focal taxon. These data were used to validate
-the range adjustments made based on species interactions (see the
-previous section). To do so, we calculated the proportion of GBIF
-presence pixels occurring within both the original and adjusted species
-ranges. We then compared these proportions for the predators to verify
-if the range adjustments removed locations with GBIF observations, hence
-likely true habitats.
+GBIF (www.gbif.org). We restricted our queries to the data with spatial
+coordinates and which were inside the spatial extent of our rasters. We
+did not use continental or date filters to retrieve as much data as
+possible. However, a few observations were localized in the ocean near
+latitude 0° and longitude 0°. We assumed these were errors and removed
+all observations falling in the extent between latitudes 2°S and 2°N and
+longitudes 2°W and 2°E to keep only mainland sites.
+
+We then converted the occurrence data into raster format by determining
+which pixels had a least one GBIF occurrence. This allowed us to remove
+the effect of repeated sampling in some locations. These data were used
+to validate the range adjustments made based on species interactions
+(see beginning of Methods section). To do so, we calculated the
+proportion of GBIF presence pixels occurring within both the original
+IUCN species range and the adjusted one. We then compared these
+proportions for the predators to verify if the range adjustments removed
+locations with GBIF observations, hence likely true habitats.
+
+\hypertarget{software}{%
+\subsection{Software}\label{software}}
+
+We performed all analyses using \emph{Julia} v1.7.2 (Bezanson et al.
+2017). We used the packages \texttt{SimpleSDMLayers.jl} (Dansereau and
+Poisot 2021) to manipulate the raster layers,
+\texttt{EcologicalNetworks.jl} (Poisot et al. 2019) to construct and
+manipulate the interaction networks, and \texttt{GBIF.jl} (Dansereau and
+Poisot 2021) to retrieve the species occurrences from GBIF. We also used
+\emph{GDAL} (GDAL/OGR contributors 2021) to rasterize the IUCN range
+maps (initially available as shapefiles from the Spatial Data Download
+portal). All the scripts required to reproduce the analyses are
+available at {[}\textbf{link to Zenodo archive}{]}.
 
@@
 may be losing ecological interactions at least as fast as we are losing
-species (Valiente-Banuet et al. 2015).
+species (\textbf{Valiente-Banuet2015SpeLos?}).
 
@@
 
+\leavevmode\hypertarget{ref-Bezanson2017JulFre}{}%
+Bezanson, Jeff, Alan Edelman, Stefan Karpinski, and Viral B. Shah. 2017.
+{``Julia: A Fresh Approach to Numerical Computing.''} \emph{SIAM Review}
+59 (1): 65--98. \url{https://doi.org/10.1137/141000671}.
+
 \leavevmode\hypertarget{ref-Blanchet2020CooNot}{}%
@@
 Abundant-Centre Is Not All That Abundant: A Comment to Osorio-Olvera Et
-Al. 2020,''} 2020.02.27.968586.
+Al. 2020,''} May, 2020.02.27.968586.
 \url{https://doi.org/10.1101/2020.02.27.968586}.
+
+\leavevmode\hypertarget{ref-Dansereau2021SimJl}{}%
+Dansereau, Gabriel, and Timothée Poisot. 2021. {``SimpleSDMLayers.jl and
+GBIF.jl: A Framework for Species Distribution Modeling in Julia.''}
+\emph{Journal of Open Source Software} 6 (57): 2872.
+\url{https://doi.org/10.21105/joss.02872}.
+
+\leavevmode\hypertarget{ref-Dansereau2021SimJl}{}%
+---------. 2021. {``SimpleSDMLayers.jl and GBIF.jl: A Framework for
+Species Distribution Modeling in Julia.''} \emph{Journal of Open Source
+Software} 6 (57): 2872. \url{https://doi.org/10.21105/joss.02872}.
 
@@
 Wallacean Shortfall in the Global Distribution of Plants.''}
-\emph{bioRxiv}, 2020.02.21.960161.
+\emph{bioRxiv}, February, 2020.02.21.960161.
 \url{https://doi.org/10.1101/2020.02.21.960161}.
@@
 
-\leavevmode\hypertarget{ref-Ficetola2014EvaRob}{}%
-Ficetola, Gentile Francesco, Carlo Rondinini, Anna Bonardi, Vineet
-Katariya, Emilio Padoa-Schioppa, and Ariadne Angulo. 2014. {``An
-Evaluation of the Robustness of Global Amphibian Range Maps.''}
-\emph{Journal of Biogeography} 41 (2): 211--21.
-\url{https://doi.org/10.1111/jbi.12206}.
-
 \leavevmode\hypertarget{ref-Fourcade2016ComSpe}{}%
@@
 Predicting Range Shifts with Climate Change.''} \emph{Ecological
-Informatics} 36: 8--14.
+Informatics} 36 (November): 8--14.
 \url{https://doi.org/10.1016/j.ecoinf.2016.09.002}.
@@
 Svenning. 2022. {``The Effects of Defaunation on Plants' Capacity to
-Track Climate Change.''} \emph{Science}.
+Track Climate Change.''} \emph{Science}, January.
 \url{https://doi.org/10.1126/science.abk3510}.
+
+\leavevmode\hypertarget{ref-GDALux2fOGRcontributors2021GdaOgr}{}%
+GDAL/OGR contributors. 2021. \emph{GDAL/OGR Geospatial Data Abstraction
+Software Library}. Manual. Open Source Geospatial Foundation.
 
@@
 and Steve Vissault. 2020. {``Environmental Biases in the Study of
-Ecological Networks at the Planetary Scale.''} \emph{bioRxiv},
+Ecological Networks at the Planetary Scale.''} \emph{bioRxiv}, January,
 2020.01.27.921429. \url{https://doi.org/10.1101/2020.01.27.921429}.
+
+\leavevmode\hypertarget{ref-Poisot2019EcoJl}{}%
+Poisot, Timothée, Zachary Bélisle, Laura Hoebeke, Michiel Stock, and
+Piotr Szefer. 2019. {``EcologicalNetworks.jl: Analysing Ecological
+Networks of Species Interactions.''} \emph{Ecography} 42 (11): 1850--61.
+\url{https://doi.org/10.1111/ecog.04310}.
 
@@
 Available Distributional Information of Iberian Mosses.''}
-\emph{Biodiversity Data Journal} 8: e53474.
+\emph{Biodiversity Data Journal} 8 (September): e53474.
 \url{https://doi.org/10.3897/BDJ.8.e53474}.
@@
 Structuring Tropical Seagrass Ecosystem Service Delivery.''}
-\emph{Frontiers in Plant Science} 9: 127.
+\emph{Frontiers in Plant Science} 9 (February): 127.
 \url{https://doi.org/10.3389/fpls.2018.00127}.
@@
 
-\leavevmode\hypertarget{ref-Valiente-Banuet2015SpeLos}{}%
-Valiente-Banuet, Alfonso, Marcelo A. Aizen, Julio M. Alcántara, Juan
-Arroyo, Andrea Cocucci, Mauro Galetti, María B. García, et al. 2015.
-{``Beyond Species Loss: The Extinction of Ecological Interactions in a
-Changing World.''} Edited by Marc Johnson. \emph{Functional Ecology} 29
-(3): 299--307. \url{https://doi.org/10.1111/1365-2435.12356}.
-
 \leavevmode\hypertarget{ref-Windsor2022UsiEco}{}%
@@
 n/a (n/a). \url{https://doi.org/10.1111/jbi.14447}.
+
+\leavevmode\hypertarget{ref-Windsor2022UsiEco}{}%
+---------. 2022. {``Using Ecological Networks to Answer Questions in
+Global Biogeography and Ecology.''} \emph{Journal of Biogeography} n/a
+(n/a). \url{https://doi.org/10.1111/jbi.14447}.
 

### 2022-07-15 draft.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@2fa2e76f994bf8a152eb7a024c46fe00746dd3e5 🚀

@@
 combined different types of occurrence data to measure the accuracy of
-datasets (Hurlbert and Jetz 2007; Hurlbert and White 2005;
-\textbf{Ficetola2014EvaRob?}), none have used different types of
-information so far (i.e., ecological characteristics other than
-geographical distribution). Here we suggest jointly analysing species
-occurrence (range maps and point occurrences) and ecological
-interactions to identify mismatches between datasets.
+datasets (Hurlbert and Jetz 2007; Hurlbert and White 2005; Ficetola et
+al. 2014), none have used different types of information so far (i.e.,
+ecological characteristics other than geographical distribution). Here
+we suggest jointly analysing species occurrence (range maps and point
+occurrences) and ecological interactions to identify mismatches between
+datasets.
 
@@
 data varies geographically (Hurlbert and Jetz 2007; Hurlbert and White
-2005; \textbf{Ficetola2014EvaRob?}). Adding ecological interaction data
-to this comparison might help to elucidate where these (dis)agreements
-are more likely to be true and which dataset better represent the actual
+2005; Ficetola et al. 2014). Adding ecological interaction data to this
+comparison might help to elucidate where these (dis)agreements are more
+likely to be true and which dataset better represent the actual
 distribution of species. In this context, we elaborate a method that
@@
 may be losing ecological interactions at least as fast as we are losing
-species (\textbf{Valiente-Banuet2015SpeLos?}).
+species (Valiente-Banuet et al. 2015).
 
@@
 
+\leavevmode\hypertarget{ref-Ficetola2014EvaRoba}{}%
+Ficetola, Gentile Francesco, Carlo Rondinini, Anna Bonardi, Vineet
+Katariya, Emilio Padoa-Schioppa, and Ariadne Angulo. 2014. {``An
+Evaluation of the Robustness of Global Amphibian Range Maps.''}
+\emph{Journal of Biogeography} 41 (2): 211--21.
+\url{https://doi.org/10.1111/jbi.12206}.
+
 \leavevmode\hypertarget{ref-Fourcade2016ComSpe}{}%
@@
 \url{https://doi.org/10.25225/jvb.20056}.
+
+\leavevmode\hypertarget{ref-Valiente-Banuet2015SpeLosa}{}%
+Valiente-Banuet, Alfonso, Marcelo A. Aizen, Julio M. Alcántara, Juan
+Arroyo, Andrea Cocucci, Mauro Galetti, María B. García, et al. 2015.
+{``Beyond Species Loss: The Extinction of Ecological Interactions in a
+Changing World.''} Edited by Marc Johnson. \emph{Functional Ecology} 29
+(3): 299--307. \url{https://doi.org/10.1111/1365-2435.12356}.
 

### 2022-07-16 response-letter.md
add line numbers and GBIF details

@@
 Thank you for the valuable feedback on our manuscript. We are pleased that you
-and the reviewer found interest and worth in our manuscript. We addressed each comment and found that the manuscript is indeed clearer now, and we hope to have it approved after your consideration.
+and the reviewer found interest and worth in our manuscript. We addressed each
+comment and found that the manuscript is indeed clearer now, and we hope to have
+it approved after your consideration. We have added more citations, context and
+examples, as well as revised the data retrieval code and added more details in
+the Methods section. We detail specific changes below (line numbers refer to the clean, revised PDF file).
+
+>*"The reviewer pointed out that some background is lacking in the introduction. Citing Gotelli, Graves & Rahbek 2010 PNAS in the intro could be useful."*
+
+>*"[...] relevant prior literature must be referenced in your introduction to provide the necessary scientific basis for understanding.
+So, please provide more literature references in the first paragraph of your introduction."*
+
+>*Lines 7-9: Please provide a short description for each example (taxonomic errors, geographic inaccuracy, or sampling biases).*
+
+>*Lines 9-11: Please cite studies that have done this before! If there are no previous studies, it is important to highlight the novelty of your study.*
 
@@
 start providing literature background and many examples, to help the reader
-understand where our paper stands in the scientific context. We have included
-discussions about the quality and accuracy of range maps (lines XX-XX), examples
-of data biases (lines XX-XX), and we addressed the uniqueness of our study
-compared to previous research (lines XX-XX). We hope that this structure is
-clarifying and appealing to the readers.
+understand where our paper stands in the scientific context. The references
+suggested were indeed helpful; we have included Gotelli *et al*. (2010) in the
+introduction (L. 28 & 33), Hurlbert and White (2005) (L. 14, 50 & 66), Hurlbert
+and Jetz (2007) (L. 14 & 50), Ficetola *et al*. (2014) (L. 15 & 66); we have
+also added Isaac, Mallet, and Mace (2004) (L.86), Rondinini *et al*. (2006) (L.
+86), and Windsor *et al*. (2022) (L. 311 & 325). Finally, we have fixed the IUCN
+reference, as pointed out by the reviewer in the annotated manuscript (L. 46),
+and added citation regarding all software infrastructure used and availability
+of our scripts (L. 158-165). Along with these references, we have included
+discussions about the quality and accuracy of range maps (L. 46-58), examples of
+data biases (L. 7-11), and we addressed the uniqueness of our study compared to
+previous research (L. 13-18). We hope that this structure is clarifying and
+appealing to the readers.
+
+>*[...] I would add the need to provide more details on how you cleaned GBIF data before actually using it. You also need to provide many more details on data retrieval, which date range?*
 
@@
    to limit IUCN range maps. This is important because the existence of
-   coordinates is a fundamental part of our analysis, and a (00,00) coordinate
+   coordinates is a fundamental part of our analysis, and a (00,00) value
    can be interpreted as a null coordinate.
+
+Our results changed with that (we provide updated numbers in lines 201-237, and Figure 04), but remained conceptually the same.
+Mainly, with the inclusion of occurrences of *Canis aureus* out of Africa, we now have 56.2% of its presence pixels within its original IUCN range map (in contrast with the previous number, 0%).
+However, this proportion after we consider its preys' ranges is still null.
+Therefore, we still suspect of a taxonomic confusion in this case, since many of the occurrences still appear to refer to other species of *Canis* based on location and due to the mismatch with the preys.
+The fact that the results remained conceptually the same regardless of the number of occurrences retrieved from GBIF can be interpreted as an evidence of the robustness of our method.
 
@@
 GBIF and IUCN nomenclatures which would block our analysis completely (in the case of _Taurotragus oryx_).
-However, in the case of *Canis aureus*, as discussed in the paper, we could not track wich occurrences or which maps corresponded to which species, which we think is a great illustration of our point.
+However, in the case of *Canis aureus*, as discussed in the paper, we could not track which occurrences or which maps corresponded to which species, which we think is a great illustration of our point.
 We didn't
@@
 
+>*Lines 124-131: I have a doubt about your data validation.
+First, you mentioned that you compiled point observation data from GBIF.
+Then you converted that data in the presence or absence of the focal taxon.
+How did you transform these data in the presence or absence once the GBIF provides just occurrence points (i.e.
+presence data)?
+This was not well explained.
+In general, absence data are not provided because the non-detection of a species in a location does not mean a true absence.
+This could just be a detection issue.
+Thus, it is needed to calculate the pseudo-absence data.
+Please explain this better in your manuscript.*
+
+>*[...] the section on geographical data validation needs improvement, by explaining how you produced absence data from presence-only data base.*
+
 For the validation step, we understand our phrasing was confusing, and we have
-rewritten this section to clarify our method. Rather than using
+rewritten this section to clarify our method (L. 151-153). Rather than using
 absence data, what we did was to transform the point data into raster files, and
@@
 Finally, we have addressed all the other minor comments throughout the text as
-described below:
-- We've added citations in the Methods section to support our argument that a
-  mismatch between ranges can be originated from different sources (L. 68-70)
-- We have suppressed lines 214-217.
-- The abstract is now restructured according to PeerJ guidelines.
-- References to tables and figures in the Discussion section were suppressed,
-  with the exception of Figure 05 (line XX), which is an example of our results
+detailed below:  
+- *Lines 68-70: This mismatch cannot just be a result of the overestimation of the predator’s range but it could be the result of misestimating both the predator's and prey's range.
+Please rephrase the sentence.*
+  We've added citations in the Methods section to support our argument that a
+  mismatch between ranges can be originated from different sources (L. 68-70).  
+- *L. 214-217 can be suppressed.*  
+  Agreed. We have suppressed lines 214-217.  
+- *PeerJ uses a structured abstract. I highly recommend authors to adhere to it when resubmitting the revised version.*
+  The abstract is now restructured according to PeerJ guidelines.  
+- *Avoid citing tables and figures in the Discussion.*
+  References to tables and figures in the Discussion section were suppressed,
+  with the exception of Figure 05 (L. 305), which is an example of our results
   to clarify an important point of the discussion.  
-- Lines 22-23 (now lines XX-XX): the cited literature are not examples of models
-  that do not take ecological interactions into account, but studies that have
-  demonstrated how ecological interactions might be responsible for shaping a
-  species' distribution. We've rewritten the sentence to clarify that.
--  Lines 68-70: we have rewritten the sentence to include the consideration
+- *Lines 21-23: Are the cited literature examples of models that do not take ecological interactions into account? Use e.g. before.*
+  The cited literature are not examples of models that do not take ecological
+  interactions into account, but studies that have demonstrated how ecological
+  interactions might be responsible for shaping a species' distribution. We've
+  rewritten the sentence to clarify that.  
+- *Lines 68-70: This mismatch cannot just be a result of the overestimation of the predator’s range but it could be the result of misestimating both the predator's and prey's range.
+Please rephrase the sentence.*
+  Lines 84-89: we have rewritten the sentence to include the consideration
   misestimation of both species in a trophic interaction. We have also added
@@
 - We have addressed the grammatical suggestions throughout the text, except for
-  the legend of figure 1. We thought that the suggested phrasing adds a little
+  the legend of Figure 1. We thought that the suggested phrasing adds a little
   bit of confusion to the comprehension of the figure.

### 2022-07-16 draft.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@644efd1d131060333072e667e7d137bb76660462 🚀

@@
 combined different types of occurrence data to measure the accuracy of
-datasets (Hurlbert and Jetz 2007; Hurlbert and White 2005; Ficetola et
-al. 2014), none have used different types of information so far (i.e.,
-ecological characteristics other than geographical distribution). Here
-we suggest jointly analysing species occurrence (range maps and point
-occurrences) and ecological interactions to identify mismatches between
-datasets.
+datasets (Hurlbert and Jetz 2007; Hurlbert and White 2005;
+\textbf{Ficetola2014EvaRoba?}), none have used different types of
+information so far (i.e., ecological characteristics other than
+geographical distribution). Here we suggest jointly analysing species
+occurrence (range maps and point occurrences) and ecological
+interactions to identify mismatches between datasets.
 
@@
 data varies geographically (Hurlbert and Jetz 2007; Hurlbert and White
-2005; Ficetola et al. 2014). Adding ecological interaction data to this
-comparison might help to elucidate where these (dis)agreements are more
-likely to be true and which dataset better represent the actual
+2005; \textbf{Ficetola2014EvaRoba?}). Adding ecological interaction data
+to this comparison might help to elucidate where these (dis)agreements
+are more likely to be true and which dataset better represent the actual
 distribution of species. In this context, we elaborate a method that
@@
 
+\leavevmode\hypertarget{ref-Dansereau2021SimJl}{}%
+---------. 2021. {``SimpleSDMLayers.jl and GBIF.jl: A Framework for
+Species Distribution Modeling in Julia.''} \emph{Journal of Open Source
+Software} 6 (57): 2872. \url{https://doi.org/10.21105/joss.02872}.
+
 \leavevmode\hypertarget{ref-Daru2020GreToo}{}%
@@
 
-\leavevmode\hypertarget{ref-Ficetola2014EvaRoba}{}%
-Ficetola, Gentile Francesco, Carlo Rondinini, Anna Bonardi, Vineet
-Katariya, Emilio Padoa-Schioppa, and Ariadne Angulo. 2014. {``An
-Evaluation of the Robustness of Global Amphibian Range Maps.''}
-\emph{Journal of Biogeography} 41 (2): 211--21.
-\url{https://doi.org/10.1111/jbi.12206}.
-
 \leavevmode\hypertarget{ref-Fourcade2016ComSpe}{}%
@@
 
+\leavevmode\hypertarget{ref-Gotelli2010MacSig}{}%
+---------. 2010. {``Macroecological Signals of Species Interactions in
+the Danish Avifauna.''} \emph{Proceedings of the National Academy of
+Sciences} 107 (11): 5030--35.
+\url{https://doi.org/10.1073/pnas.0914089107}.
+
 \leavevmode\hypertarget{ref-Herkt2017MacCon}{}%
@@
 \emph{Ecology Letters} 9 (10): 1136--45.
+\url{https://doi.org/10.1111/j.1461-0248.2006.00970.x}.
+
+\leavevmode\hypertarget{ref-Rondinini2006TraDif}{}%
+---------. 2006. {``Tradeoffs of Different Types of Species Occurrence
+Data for Use in Systematic Conservation Planning.''} \emph{Ecology
+Letters} 9 (10): 1136--45.
 \url{https://doi.org/10.1111/j.1461-0248.2006.00970.x}.

### 2022-07-16 preprint.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@644efd1d131060333072e667e7d137bb76660462 🚀

@@
 datasets (Hurlbert and Jetz 2007; Hurlbert and White 2005;
-\textbf{Ficetola2014EvaRob?}), none have used different types of
+\textbf{Ficetola2014EvaRoba?}), none have used different types of
 information so far (i.e., ecological characteristics other than
@@
 data varies geographically (Hurlbert and Jetz 2007; Hurlbert and White
-2005; \textbf{Ficetola2014EvaRob?}). Adding ecological interaction data
+2005; \textbf{Ficetola2014EvaRoba?}). Adding ecological interaction data
 to this comparison might help to elucidate where these (dis)agreements
@@
 
+\leavevmode\hypertarget{ref-Valiente-Banuet2015SpeLosa}{}%
+Valiente-Banuet, Alfonso, Marcelo A. Aizen, Julio M. Alcántara, Juan
+Arroyo, Andrea Cocucci, Mauro Galetti, María B. García, et al. 2015.
+{``Beyond Species Loss: The Extinction of Ecological Interactions in a
+Changing World.''} Edited by Marc Johnson. \emph{Functional Ecology} 29
+(3): 299--307. \url{https://doi.org/10.1111/1365-2435.12356}.
+
 \leavevmode\hypertarget{ref-Windsor2022UsiEco}{}%

### 2022-07-16 preprint.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@79ba5448203e48bdc1cbd11a18cc1125b62a7850 🚀

@@
 combined different types of occurrence data to measure the accuracy of
-datasets (Hurlbert and Jetz 2007; Hurlbert and White 2005;
-\textbf{Ficetola2014EvaRoba?}), none have used different types of
-information so far (i.e., ecological characteristics other than
-geographical distribution). Here we suggest jointly analysing species
-occurrence (range maps and point occurrences) and ecological
-interactions to identify mismatches between datasets.
+datasets (Hurlbert and Jetz 2007; Hurlbert and White 2005; Ficetola et
+al. 2014), none have used different types of information so far (i.e.,
+ecological characteristics other than geographical distribution). Here
+we suggest jointly analysing species occurrence (range maps and point
+occurrences) and ecological interactions to identify mismatches between
+datasets.
 
@@
 data varies geographically (Hurlbert and Jetz 2007; Hurlbert and White
-2005; \textbf{Ficetola2014EvaRoba?}). Adding ecological interaction data
-to this comparison might help to elucidate where these (dis)agreements
-are more likely to be true and which dataset better represent the actual
+2005; Ficetola et al. 2014). Adding ecological interaction data to this
+comparison might help to elucidate where these (dis)agreements are more
+likely to be true and which dataset better represent the actual
 distribution of species. In this context, we elaborate a method that
@@
 
-\leavevmode\hypertarget{ref-Dansereau2021SimJl}{}%
----------. 2021. {``SimpleSDMLayers.jl and GBIF.jl: A Framework for
-Species Distribution Modeling in Julia.''} \emph{Journal of Open Source
-Software} 6 (57): 2872. \url{https://doi.org/10.21105/joss.02872}.
-
 \leavevmode\hypertarget{ref-Daru2020GreToo}{}%
@@
 
-\leavevmode\hypertarget{ref-Gotelli2010MacSig}{}%
----------. 2010. {``Macroecological Signals of Species Interactions in
-the Danish Avifauna.''} \emph{Proceedings of the National Academy of
-Sciences} 107 (11): 5030--35.
-\url{https://doi.org/10.1073/pnas.0914089107}.
-
 \leavevmode\hypertarget{ref-Herkt2017MacCon}{}%
@@
 \emph{Ecology Letters} 9 (10): 1136--45.
-\url{https://doi.org/10.1111/j.1461-0248.2006.00970.x}.
-
-\leavevmode\hypertarget{ref-Rondinini2006TraDif}{}%
----------. 2006. {``Tradeoffs of Different Types of Species Occurrence
-Data for Use in Systematic Conservation Planning.''} \emph{Ecology
-Letters} 9 (10): 1136--45.
 \url{https://doi.org/10.1111/j.1461-0248.2006.00970.x}.
@@
 n/a (n/a). \url{https://doi.org/10.1111/jbi.14447}.
-
-\leavevmode\hypertarget{ref-Windsor2022UsiEco}{}%
----------. 2022. {``Using Ecological Networks to Answer Questions in
-Global Biogeography and Ecology.''} \emph{Journal of Biogeography} n/a
-(n/a). \url{https://doi.org/10.1111/jbi.14447}.
 

### 2022-07-16 draft.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@afdc65f85795a7aa4e4a02aef00617b266eb78be 🚀

--- 2022-07-15 draft.tex
@@
 traditional unceded territory of the Saint Lawrence Iroquoian,
-Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak nations. GH,
-FB, GD, and NF are funded by the NSERC Computational Biodiversity
-Science and Services (BIOS\(^2\)) CREATE program; FB, NF, and TP are
-funded by the Institute for Data Valorization (IVADO); NF and TP are
-funded by a donation from the Courtois Foundation; GD is funded by the
-Natural Sciences and Engineering Research Council (NSERC) and the Fond
-de recherche du Québec - Nature et technologie (FRQNT) doctoral
-scholarships; TP is funded by the Canadian Institute of Ecology \&
-Evolution; FW is funded by the Royal Society (Grant number:
-CHL\textbackslash R1\textbackslash180156). We thank the editor and
-reviewer for their thoughtful comments, which considerably improved this
-manuscript.
+Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak nations. We
+thank the editor and reviewer for their thoughtful comments, which
+considerably improved this manuscript.
 
@@
 Abundant-Centre Is Not All That Abundant: A Comment to Osorio-Olvera Et
-Al. 2020,''} May, 2020.02.27.968586.
+Al. 2020,''} 2020.02.27.968586.
 \url{https://doi.org/10.1101/2020.02.27.968586}.
@@
 Wallacean Shortfall in the Global Distribution of Plants.''}
-\emph{bioRxiv}, February, 2020.02.21.960161.
+\emph{bioRxiv}, 2020.02.21.960161.
 \url{https://doi.org/10.1101/2020.02.21.960161}.
@@
 
-\leavevmode\hypertarget{ref-Ficetola2014EvaRoba}{}%
+\leavevmode\hypertarget{ref-Ficetola2014EvaRob}{}%
 Ficetola, Gentile Francesco, Carlo Rondinini, Anna Bonardi, Vineet
@@
 Predicting Range Shifts with Climate Change.''} \emph{Ecological
-Informatics} 36 (November): 8--14.
+Informatics} 36: 8--14.
 \url{https://doi.org/10.1016/j.ecoinf.2016.09.002}.
@@
 Svenning. 2022. {``The Effects of Defaunation on Plants' Capacity to
-Track Climate Change.''} \emph{Science}, January.
+Track Climate Change.''} \emph{Science}.
 \url{https://doi.org/10.1126/science.abk3510}.
@@
 and Steve Vissault. 2020. {``Environmental Biases in the Study of
-Ecological Networks at the Planetary Scale.''} \emph{bioRxiv}, January,
+Ecological Networks at the Planetary Scale.''} \emph{bioRxiv},
 2020.01.27.921429. \url{https://doi.org/10.1101/2020.01.27.921429}.
@@
 Available Distributional Information of Iberian Mosses.''}
-\emph{Biodiversity Data Journal} 8 (September): e53474.
+\emph{Biodiversity Data Journal} 8: e53474.
 \url{https://doi.org/10.3897/BDJ.8.e53474}.
@@
 Structuring Tropical Seagrass Ecosystem Service Delivery.''}
-\emph{Frontiers in Plant Science} 9 (February): 127.
+\emph{Frontiers in Plant Science} 9: 127.
 \url{https://doi.org/10.3389/fpls.2018.00127}.
@@
 
-\leavevmode\hypertarget{ref-Valiente-Banuet2015SpeLosa}{}%
+\leavevmode\hypertarget{ref-Valiente-Banuet2015SpeLos}{}%
 Valiente-Banuet, Alfonso, Marcelo A. Aizen, Julio M. Alcántara, Juan

### 2022-07-16 response-letter.md
fix line number for methods

@@
 Regarding the GBIF data cleaning, retrieval and the validation steps, we added a
-more detailed description of our process (lines XX-XX, XX-XX and XX-XX). Data
-retrieving is detailed in the source code provided on our GitHub repository
+more detailed description of our process (L. 144-165). Data
+retrieving is detailed in the source code provided on our repository
 (code/09-GBIF_data.jl). We used the list of species from the network dataset and
 retrieved any occurrence within our bounding box (between longitudes -20.0 and
-55.0 degrees; and latitudes -35.0 and 40.0 degrees). We changed a two things
+55.0 degrees; and latitudes -35.0 and 40.0 degrees). We changed two things
 regarding geographical information during data retrieval:
+
 1. We had originally added an argument to capture only the data that had
@@
 detailed below:
+
 - *Lines 68-70: This mismatch cannot just be a result of the overestimation of the predator’s range but it could be the result of misestimating both the predator's and prey's range.
 Please rephrase the sentence.*
+
   We've added citations in the Methods section to support our argument that a
   mismatch between ranges can be originated from different sources (L. 68-70).
+
 - *L. 214-217 can be suppressed.*
+
   Agreed. We have suppressed lines 214-217.
+
 - *PeerJ uses a structured abstract. I highly recommend authors to adhere to it when resubmitting the revised version.*
+
   The abstract is now restructured according to PeerJ guidelines.
+
 - *Avoid citing tables and figures in the Discussion.*
+
   References to tables and figures in the Discussion section were suppressed,
@@
   to clarify an important point of the discussion.
+
 - *Lines 21-23: Are the cited literature examples of models that do not take ecological interactions into account? Use e.g. before.*
+
   The cited literature are not examples of models that do not take ecological
@@
   rewritten the sentence to clarify that.
+
 - *Lines 68-70: This mismatch cannot just be a result of the overestimation of the predator’s range but it could be the result of misestimating both the predator's and prey's range.
 Please rephrase the sentence.*
+
   Lines 84-89: we have rewritten the sentence to include the consideration
@@
   citations and examples.
+
 - We have addressed the grammatical suggestions throughout the text, except for

### 2022-07-16 draft.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@40c766e52a0a7380952f78d649000b13025db880 🚀
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@6589da1782c0d676cd233e22335a24261ec0d2c3 🚀

@@
 portal). All the scripts required to reproduce the analyses are
-available at {[}\textbf{link to Zenodo archive}{]}.
+available at https://doi.org/10.5281/zenodo.6842861.
 
@@
 \emph{Panthera pardus} lost 8.8\%; and \emph{Caracal caracal} lost
-12.3\%). \textless!---\textgreater Note to self: here I calculated how
-much the difference represents as a proportion of the total proportion,
-which means the decreased rate. E.g., when the range\_prop\_diff is
-equal to the original proportion (range\_prop), this means that this
-species lost 100\% of the original proportion. Therefore I can't use
-range\_prop\_diff numbers if I'm talking about \%
-lost.\textless---\textgreater{} On the other hand, three species,
-\emph{Canis aureus}, \emph{Canis mesomelas}, and \emph{Leptailurus
-serval} showed very high differences, with overlaps lowered by 100\%,
-57.4\%, and 100\% respectively. These last two species are also the only
-predators with a single prey in our metaweb. \emph{Canis aureus} has
-four preys, but it has one of the smallest ranges in IUCN, which is not
-covered by any of its preys. This result reinforces the concern raised
-in the literature on the use of IUCN range maps for species that are not
-well known (Herkt, Skidmore, and Fahr 2017), demonstrating how small
-range species are likely to have their distribution underestimated in
-the IUCN database. Additionally, the fact that \emph{Canis aureus} had
-such a conspicuous mismatch between both the original and updated IUCN
-range maps, and between GBIF and IUCN data, may indicate a taxonomic
+12.3\%). On the other hand, three species, \emph{Canis aureus},
+\emph{Canis mesomelas}, and \emph{Leptailurus serval} showed very high
+differences, with overlaps lowered by 100\%, 57.4\%, and 100\%
+respectively. These last two species are also the only predators with a
+single prey in our metaweb. \emph{Canis aureus} has four preys, but it
+has one of the smallest ranges in IUCN, which is not covered by any of
+its preys. This result reinforces the concern raised in the literature
+on the use of IUCN range maps for species that are not well known
+(Herkt, Skidmore, and Fahr 2017), demonstrating how small range species
+are likely to have their distribution underestimated in the IUCN
+database. Additionally, the fact that \emph{Canis aureus} had such a
+conspicuous mismatch between both the original and updated IUCN range
+maps, and between GBIF and IUCN data, may indicate a taxonomic
 incongruency between the three databases used here, which we explore in

### 2022-07-26 draft.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@01b0bf77e27b1d7dd71250d44c5b322979bd64c1 🚀

@@
 %
-\,\textsuperscript{1,2,‡}\quad %
+\,\textsuperscript{1}\quad %
+\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
+%
+\,\textsuperscript{2,3,4}\quad %
+\href{https://orcid.org/0000-0002-2212-3584}{Gabriel\,Dansereau}%
+%
+\,\textsuperscript{2,4}\quad %
+\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
+%
+\,\textsuperscript{2,4}\quad %
 \href{https://orcid.org/0000-0001-5030-3470}{Fredric\,M. Windsor}%
 %
-\,\textsuperscript{3,‡}\quad %
-\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
-%
-\,\textsuperscript{4,5,6,‡}\quad %
-\href{https://orcid.org/0000-0002-2212-3584}{Gabriel\,Dansereau}%
-%
-\,\textsuperscript{4,6,‡}\quad %
-\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
-%
-\,\textsuperscript{4,6,‡}\quad %
+\,\textsuperscript{5}\quad %
 \href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
 %
-\,\textsuperscript{4,6,‡}
-
-\textsuperscript{1}\,The University of British
-Columbia\quad \textsuperscript{2}\,Computational Biodiversity Science
-and Services\quad \textsuperscript{3}\,School of Natural and
-Environmental Sciences, Newcastle
-University\quad \textsuperscript{4}\,Université de
-Montréal\quad \textsuperscript{5}\,Université de
-Sherbrooke\quad \textsuperscript{6}\,Quebec Centre for Biodiversity
-Science
-
-\textsuperscript{‡}\,These authors contributed equally to the work\\
+\,\textsuperscript{2,4}
+
+\textsuperscript{1}\,Biodiversity Research Centre, University of British
+Columbia\quad \textsuperscript{2}\,Université de
+Montréal\quad \textsuperscript{3}\,Université de
+Sherbrooke\quad \textsuperscript{4}\,Quebec Centre for Biodiversity
+Science\quad \textsuperscript{5}\,School of Natural and Environmental
+Sciences, Newcastle University
 

### 2022-07-26 preprint.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@01b0bf77e27b1d7dd71250d44c5b322979bd64c1 🚀

@@
 %
-\,\textsuperscript{1,2,‡}, %
+\,\textsuperscript{1}, %
+\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
+%
+\,\textsuperscript{2,3,4}, %
+\href{https://orcid.org/0000-0002-2212-3584}{Gabriel\,Dansereau}%
+%
+\,\textsuperscript{2,4}, %
+\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
+%
+\,\textsuperscript{2,4}, %
 \href{https://orcid.org/0000-0001-5030-3470}{Fredric\,M. Windsor}%
 %
-\,\textsuperscript{3,‡}, %
-\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
-%
-\,\textsuperscript{4,5,6,‡}, %
-\href{https://orcid.org/0000-0002-2212-3584}{Gabriel\,Dansereau}%
-%
-\,\textsuperscript{4,6,‡}, %
-\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
-%
-\,\textsuperscript{4,6,‡}, %
+\,\textsuperscript{5}, %
 \href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
 %
-\,\textsuperscript{4,6,‡}
+\,\textsuperscript{2,4}
 \vskip 1em
-\textsuperscript{1}\,The University of British
-Columbia; \textsuperscript{2}\,Computational Biodiversity Science and
-Services; \textsuperscript{3}\,School of Natural and Environmental
-Sciences, Newcastle University; \textsuperscript{4}\,Université de
-Montréal; \textsuperscript{5}\,Université de
-Sherbrooke; \textsuperscript{6}\,Quebec Centre for Biodiversity
-Science\\
-\textsuperscript{‡}\,These authors contributed equally to the work\\
+\textsuperscript{1}\,Biodiversity Research Centre, University of British
+Columbia; \textsuperscript{2}\,Université de
+Montréal; \textsuperscript{3}\,Université de
+Sherbrooke; \textsuperscript{4}\,Quebec Centre for Biodiversity
+Science; \textsuperscript{5}\,School of Natural and Environmental
+Sciences, Newcastle University\\
 \vskip 1em

### 2022-11-22 draft.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@6a03212150abe2f94369e350bd8509868cfa9ea2 🚀
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@1c8da06906e50354f2b96c92b09fa8cbaee445a9 🚀

@@
 distribution of species. In this context, we elaborate a method that
-allows us to refine distribution data (more precisely range maps) based
-on interaction data, considering the basic assumption that predators can
-only be present in regions where they are connected to at least one
-herbivore - and thus indirectly connected to primary producers. We used
-a Serengeti food web dataset (Baskerville et al. 2011) (which comprises
-carnivores, herbivores, and plants from Tanzania) to demonstrate how a
-mismatch between occurrence and interaction data can highlight
-significant uncertainty areas in IUCN range maps. Finally, we add the
-GBIF occurrence points for the Serengeti species to the investigation,
+allows us to detect areas of potential misestimation of species'
+distribution data (more precisely range maps) based on interaction data,
+considering the basic assumption that predators can only be present in
+regions where they are connected to at least one herbivore - and thus
+indirectly connected to primary producers. We used a Serengeti food web
+dataset (Baskerville et al. 2011) (which comprises carnivores,
+herbivores, and plants from Tanzania) to demonstrate how a mismatch
+between occurrence and interaction data can highlight significant
+uncertainty areas in IUCN range maps. Finally, we add the GBIF
+occurrence points for the Serengeti species to the investigation,
 discuss the mechanisms that can lead to the lack of agreement between
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-15540\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-0.560\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-0.670\strut
+9250\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+0.437\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+0.618\strut
 \end{minipage}\tabularnewline
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-43307\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-0.848\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-0.252\strut
+4822\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+0.844\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+0.253\strut
 \end{minipage}\tabularnewline
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-3873\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-0.916\strut
+427\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+0.918\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-11384\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-0.934\strut
+1274\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+0.935\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-68137\strut
+7563\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-7358\strut
+816\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-0.780\strut
+0.782\strut
 \end{minipage}\tabularnewline
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-19872\strut
+2201\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-0.995\strut
+0.994\strut
 \end{minipage}\tabularnewline
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-47243\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-0.832\strut
+5239\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+0.833\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-38856\strut
+4319\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-0.979\strut
+0.978\strut
 \end{minipage}\tabularnewline
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-5567\strut
+626\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-3695\strut
+419\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-26705\strut
+2961\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-22380\strut
+2484\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-11901\strut
+1318\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-29963\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
--\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-0.999\strut
+3331\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+-\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+1\strut
 \end{minipage}\tabularnewline
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-17465\strut
+1935\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-465\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
--\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-0.998\strut
+53\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+-\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+1\strut
 \end{minipage}\tabularnewline
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-20852\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
--\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-0.991\strut
+2316\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+-\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+0.990\strut
 \end{minipage}\tabularnewline
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-36011\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
--\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-0.984\strut
+3999\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+-\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+0.985\strut
 \end{minipage}\tabularnewline
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-10579\strut
+1167\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-20761\strut
+2307\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-9650\strut
+1074\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-7070\strut
+786\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-463\strut
+51\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-2303\strut
+261\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-17728\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
--\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-0.972\strut
+1961\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+-\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+0.973\strut
 \end{minipage}\tabularnewline
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-47697\strut
+5312\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-5418\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
--\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-0.470\strut
+607\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+-\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+0.473\strut
 \end{minipage}\tabularnewline
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-9654\strut
+1078\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-4002\strut
+443\strut
 \end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-23171\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
--\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-0.938\strut
+2571\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+-\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+0.937\strut
 \end{minipage}\tabularnewline
@@
 \end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedleft
-25223\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
--\strut
-\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
-0.250\strut
+2808\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+-\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft
+0.251\strut
 \end{minipage}\tabularnewline
@@
 
-The jackal is a widespread taxon in northern Africa, Europe, and
-Australasia, generally well adapted to local conditions due to its
-largely varied diet (Tsunoda and Saito 2020; Krofel et al. 2021).
-Because of that, we expected that the \emph{Canis} species in our
-dataset would be the ones losing the least amount of range, with a
-higher value of the proportion of GBIF pixels within their IUCN range
-maps. However, the taxonomy of this group is a matter of intense
-discussion, as molecular and morphological data seem to disagree in the
-clustering of species and subspecies (Krofel et al. 2021; Stoyanov
-2020). This debate probably influenced our results: with originally only
-56.2\% of the GBIF pixels of the golden jackal (\emph{Canis aureus})
-overlapping with the IUCN data, we suspect that many of the GBIF
-occurrences refer to other \emph{Canis} species, and that its taxonomic
+Here we identify areas of data mismatch between species range maps by
+using ecological interaction data (predator-prey interactions within
+food webs). Our results did show a significant mismatch in the IUCN
+range areas of specialized and generalist predatory organisms and their
+prey, which highlights the importance of accounting for species
+interactions when estimating the range of a species. Although this type
+of data mismatch can result of actual ecological processes, outdated
+occurrence data, taxonomic errors and more, we argue that, here, they
+rather indicate a lack of interaction sampling data.
+
+The case of the golden jackal (\emph{Canis aureus}) is a good
+illustration of how the taxonomic, geographical and ecological data can
+be used to validate one another. The jackal is a widespread taxon in
+northern Africa, Europe, and Australasia, generally well adapted to
+local conditions due to its largely varied diet (Tsunoda and Saito 2020;
+Krofel et al. 2021). Because of that, we expected that
+the~\emph{Canis}~species in our dataset would be the ones losing the
+least amount of range, with a higher value of the proportion of GBIF
+pixels within their IUCN range maps. However, the taxonomy of this group
+is a matter of intense discussion, as molecular and morphological data
+seem to disagree in the clustering of species and subspecies (Krofel et
+al. 2021; Stoyanov 2020). This debate probably influenced our results:
+with originally only 56.2\% of the GBIF pixels of the golden jackal
+overlapping with its IUCN data, we suspect that many of the GBIF
+occurrences refer to other~\emph{Canis}~species, and that its taxonomic
 identification in the network database is probably outdated. This led to
-a complete exclusion of \emph{Canis aureus} from its original range in
+a complete exclusion of~\emph{Canis aureus}~from its original range in
 our analysis, despite the fact that this species has four documented
-preys in our metaweb. This example illustrates how the taxonomic,
-geographical and ecological data can be used to validate one another.
-
-Here we show that when ecological interaction data (predator-prey
-interactions within food webs) are used to refine species range maps,
-there are significant reductions in the IUCN range size of predatory
-organisms. Despite showing the potential importance of accounting for
-species interactions when estimating the range of a species, it remains
-unclear the extent to which the patterns observed represent ecological
-processes or a lack of data.
-
-\hypertarget{connectivity-diversity-and-range-preservation}{%
-\subsection{Connectivity, diversity and range
-preservation}\label{connectivity-diversity-and-range-preservation}}
-
-In the Serengeti food web there is a positive relationship between the
-out degrees of predators and the size of their ranges. Here, we showed
-that there is a negative relationship between the relative loss of
-predators' ranges and their number of preys, reinforcing the idea that
-generalist species can preserve their distributions longer while losing
-interactions. The factors limiting the geographical range of a species
-in a community can vary with connectivity and richness (Svenning et al.
-2014). Younger communities may be more affected by environmental
-limitations because they are dominated by generalist species, while
-older metacommunities are probably affected in different ways in the
-center of the distribution, at the edge of ranges, and in sink and
-source communities (Svenning et al. 2014; Godsoe et al. 2017; Cazelles
-et al. 2016; Bullock et al. 2000). Additionally, it is likely that
-species with larger ranges of distribution and those that are more
-generalists would co-occur with a greater number of other species
-(Dáttilo et al. 2020), while dispersal capacity of competitive species
-modulate their aggregation in space and the effect of interactions on
-their range limits (Godsoe et al. 2017).
+preys in our metaweb.
 
@@
 
-The geographical mismatch between predators and preys has ecological
-consequences such as loss of ecosystem functioning and extinction of
-populations (Anderson et al. 2016; Dáttilo and Rico-Gray 2018; Pringle
-et al. 2016; Young et al. 2013). Climate change is one of the causes of
-this, leading, for instance, to the decrease of plant populations due to
-the lack of pollination (Bullock et al. 2000; Afkhami, McIntyre, and
-Strauss 2014; Godsoe et al. 2017). However, this mismatch can also be
-purely informational. When the distribution of predators and preys does
-not superpose, it can mean we lack information about the distribution of
-either species or about their interactions (e.g., predators may be
-feeding on different species than the ones in our dataset outside the
-Serengeti ecosystem). Here we addressed part of this problem by
-comparing the IUCN range maps with GBIF occurrences, which helped us
-clarify what is the shortfall for each species.
-
 The lack of superposition between IUCN range maps and GBIF occurrences
-suggests that we certainly do miss geographical information about the
-distribution of a certain species, but this is not an indicator of the
-completeness of the information about ecological interactions. However,
-if both GBIF and IUCN occurrences tend to superpose and still the
-species is locally removed, this indicates we don't have information
-about all its interactions. The combination of this rationale with our
-method of updating range maps based on ecological interactions allows us
-to have a clearer idea of which information we are missing. For example,
-the lion (\emph{Panthera leo}) was one of the species with no difference
-between the original and the updated ranges, but 40.7\% of the GBIF
+in our results suggests that we certainly miss geographical information
+about the distribution of either the prey or the predator. On the other
+hand, if both GBIF and IUCN occurrences tended to superpose and the
+species was still locally removed, this indicates that we don't have
+information about all its interactions (e.g., predators may be feeding
+on different species than the ones in our dataset outside the Serengeti
+ecosystem). This rationale can be illustrated with three types of
+mismatches identified in our results.
+
+First, \emph{Panthera leo} was one of the species with no difference
+between ranges before and after our analysis, but 40.7\% of the GBIF
 occurrences for this species fell outside its IUCN range
@@
 the IUCN and the GBIF databases is concerning and suggests that the IUCN
-maps might underestimate the lion's distribution. On the other hand,
-\emph{Leptailurus serval} and \emph{Canis mesomelas} are two of the
-three species that lose the higher proportion of range due to the lack
-of paths to a herbivore, but are also some of the species with the
-higher proportion of GBIF occurrences inside IUCN range maps
-(fig.~\ref{fig:gbif}). This indicates that the information we are
-missing for these two species is related to either the occurrence of an
-interaction or the presence of interacting species. To illustrate that,
-we mapped the GBIF data for the prey of \emph{Leptailurus serval}, with
-a mobility buffer around each point (fig.~\ref{fig:serval}). When
-considering GBIF data, approximately 42\% of the prey's occurrences are
-within the portion of the serval's range that was lost. With the buffer
-area, this corresponds to 15\% of the lost range. This means that by
-adding GBIF information, we would reduce the loss of range (or
-information) for the predator by 15\% since its distribution is
-conditional on the occurrence of its preys.
+maps might underestimate the lion's distribution.
+
+On the other hand,~\emph{Leptailurus serval}~and~\emph{Canis
+mesomelas}~are two of the three species that have the higher proportion
+of mismatched range due to the lack of paths to a herbivore, but are
+also some of the species with the higher proportion of GBIF occurrences
+inside IUCN range maps (fig.~\ref{fig:gbif}). This indicates that the
+information we are missing for these two species is related to either an
+additional interaction or to the presence of interacting species. To
+illustrate that, we mapped the GBIF data for the prey
+of~\emph{Leptailurus serval}, with a mobility buffer around each point
+(fig.~\ref{fig:serval}). When considering GBIF data, approximately 42\%
+of the prey's occurrences are within the portion of the predator's range
+that was divergent from its original IUCN data. With the buffer area,
+this corresponds to 15\% of the mismatched area. By adding GBIF
+information for the prey, we could therefore reduce the discrepancy of
+the range (or information) for the predator by 15\% since its
+distribution is conditional on the occurrence of its preys. In other
+words, the range mismatch was exagerated because we were missing
+information on the presence of an interacting species (i.e., this also
+indicates that there is a mismatch - or complementarity - between the
+IUCN and GBIF data for their prey).
 
@@
 
-Finally, the extreme case of \emph{Canis aureus} illustrates a lack of
+Finally, the extreme case of~\emph{Canis aureus}~illustrates a lack of
 both geographical and ecological information: only half of its GBIF
@@
 
-\leavevmode\hypertarget{ref-Anderson2016SpaDis}{}%
-Anderson, T. Michael, Staci White, Bryant Davis, Rob Erhardt, Meredith
-Palmer, Alexandra Swanson, Margaret Kosmala, and Craig Packer. 2016.
-{``The Spatial Distribution of African Savannah Herbivores: Species
-Associations and Habitat Occupancy in a Landscape Context.''}
-\emph{Philosophical Transactions of the Royal Society B: Biological
-Sciences} 371 (1703): 20150314.
-\url{https://doi.org/10.1098/rstb.2015.0314}.
-
 \leavevmode\hypertarget{ref-Araujo2014ImpBio}{}%
@@
 
-\leavevmode\hypertarget{ref-Bullock2000GeoSep}{}%
-Bullock, James M., Rebecca J. Edwards, Peter D. Carey, and Rob J. Rose.
-2000. {``Geographical Separation of Two Ulex Species at Three Spatial
-Scales: Does Competition Limit Species' Ranges?''} \emph{Ecography} 23
-(2): 257--71. \url{https://doi.org/10.1111/j.1600-0587.2000.tb00281.x}.
-
 \leavevmode\hypertarget{ref-Cabral2017MecSim}{}%
@@
 
-\leavevmode\hypertarget{ref-Cazelles2016IntBio}{}%
-Cazelles, Kévin, Nicolas Mouquet, David Mouillot, and Dominique Gravel.
-2016. {``On the Integration of Biotic Interaction and Environmental
-Constraints at the Biogeographical Scale.''} \emph{Ecography} 39 (10):
-921--31. \url{https://doi.org/10.1111/ecog.01714}.
-
 \leavevmode\hypertarget{ref-Dallas2020AbuNot}{}%
@@
 \url{https://doi.org/10.1101/2020.02.21.960161}.
-
-\leavevmode\hypertarget{ref-Dattilo2020SpeDri}{}%
-Dáttilo, Wesley, Nathalia Barrozo-Chávez, Andrés Lira-Noriega, Roger
-Guevara, Fabricio Villalobos, Diego Santiago-Alarcon, Frederico Siqueira
-Neves, Thiago Izzo, and Sérvio Pontes Ribeiro. 2020. {``Species-Level
-Drivers of Mammalian Ectoparasite Faunas.''} \emph{Journal of Animal
-Ecology} 89 (8): 1754--65.
-\url{https://doi.org/10.1111/1365-2656.13216}.
-
-\leavevmode\hypertarget{ref-Dattilo2018EcoNet}{}%
-Dáttilo, Wesley, and Victor Rico-Gray, eds. 2018. \emph{Ecological
-Networks in the Tropics: An Integrative Overview of Species Interactions
-from Some of the Most Species-Rich Habitats on Earth}. 1st ed. 2018.
-Cham: Springer International Publishing : Imprint: Springer.
-\url{https://doi.org/10.1007/978-3-319-68228-0}.
 
@@
 \url{https://doi.org/10.2307/1940153}.
-
-\leavevmode\hypertarget{ref-Pringle2016LarHer}{}%
-Pringle, Robert M., Kirsten M. Prior, Todd M. Palmer, Truman P. Young,
-and Jacob R. Goheen. 2016. {``Large Herbivores Promote Habitat
-Specialization and Beta Diversity of African Savanna Trees.''}
-\emph{Ecology} 97 (10): 2640--57.
-\url{https://doi.org/10.1002/ecy.1522}.
 
@@
 \url{https://doi.org/10.1098/rstb.2021.0063}.
-
-\leavevmode\hypertarget{ref-Svenning2014InfInt}{}%
-Svenning, Jens Christian, Dominique Gravel, Robert D. Holt, Frank M.
-Schurr, Wilfried Thuiller, Tamara Münkemüller, Katja H. Schiffers, et
-al. 2014. {``The Influence of Interspecific Interactions on Species
-Range Expansion Rates.''} \emph{Ecography} 37 (12): 1198--1209.
-\url{https://doi.org/10.1111/j.1600-0587.2013.00574.x}.
 
@@
 
-\leavevmode\hypertarget{ref-Young2013EffMam}{}%
-Young, Hillary S., Douglas J. McCauley, Kristofer M. Helgen, Jacob R.
-Goheen, Erik Otárola-Castillo, Todd M. Palmer, Robert M. Pringle, Truman
-P. Young, and Rodolfo Dirzo. 2013. {``Effects of Mammalian Herbivore
-Declines on Plant Communities: Observations and Experiments in an
-\textsc{A} Frican Savanna.''} Edited by Luis Santamaria. \emph{Journal
-of Ecology} 101 (4): 1030--41.
-\url{https://doi.org/10.1111/1365-2745.12096}.
-
 \end{CSLReferences}

### 2022-11-22 code/A3_gbif_query.jl
✨ generate GBIF query from Julia

@@ -1,0 +1,58 @@
+#### Preparing the query for the GBIF download API ###
+
+include("A1_required.jl")
+
+# Bounding box
+lat, lon = (bounding_box.bottom, bounding_box.top), (bounding_box.left, bounding_box.right)
+left, right, bottom, top = bounding_box
+
+# Getting taxa codes
+sp_taxon = taxon.(mammals, rank = :SPECIES)
+sp_codes = [t.species.second for t in sp_taxon]
+unique!(sp_codes)
+
+# Add taxa codes and bounding box to the JSON query
+query = """
+{
+    "creator": "username",
+    "notification_address": [
+        "useremail"
+    ],
+    "sendNotification": true,
+    "format": "SIMPLE_CSV",
+    "predicate": {
+        "type": "and",
+        "predicates": [
+        {
+            "type": "in",
+            "key": "TAXON_KEY",
+            "values": $(sp_codes)
+        },
+        {
+            "type":"equals",
+            "key":"HAS_COORDINATE",
+            "value":"true"
+        },
+        {
+            "type":"within",
+            "geometry":"POLYGON(($left $top,
+                      $left $bottom, $right $bottom,
+                      $right $top,$left $top))"
+        }
+    ]}
+}
+"""
+open(joinpath("code", "query.json"), "w") do io
+    println(io, query)
+end
+
+# Next edit the query file with your GBIF username and email
+# Then run add your username and password to the following curl command
+# and run it in a terminal
+
+# curl --include --user username:password --header "Content-Type: application/json" --data @code/query.json https://api.gbif.org/v1/occurrence/download/request
+
+# This will send the request to GBIF. You will then receive an email with a
+# download link (probably within minutes)
+
+# ⚠️ DO NOT COMMIT THE FILES WITH YOUR USERNAME, EMAIL, OR PASSWORD ⚠️

### 2022-11-22 code/09-GBIF_data.jl
✨ fix code and make fig on recent GBIF obs

@@ -31,10 +31,10 @@ end
 
 ## Create DataFrame
 
-# Make Data Frames
+# Make DataFrame
 occ_df = DataFrame.(occ)
 occ_df = reduce(vcat, occ_df)
-select!(occ_df, :species, :longitude, :latitude)
+select!(occ_df, :species, :longitude, :latitude, :date)
 occ_df.species = replace.(occ_df.species, " " => "_")
 
 # Remove observations with coordinates around (0.0, 0.0) which are outside mainland
@@ -54,6 +54,7 @@ isequal(unique(occ_df.species), mammals) # true
 # Save as CSV
 CSV.write(joinpath("data", "clean", "gbif_occurrences.csv"), occ_df)
 
+
 ## Investigate difference with original query with Africa as continent
 # Load datasets
 old = CSV.read(joinpath("data", "clean", "gbif_occurrences_old.csv"), DataFrame) # get from previous commit
@@ -68,6 +69,7 @@ diff = @chain begin
     sort(:diff, rev=true)
 end
 diff
+
 
 ## Create layers
 
@@ -92,59 +94,94 @@ geotiff(joinpath("data", "clean", "gbif_occurrences.tif"), gbif_occ_layers)
 geotiff(joinpath("data", "clean", "gbif_ranges.tif"), gbif_ranges)
 
 
-# Explore year distribution
+## Explore year distribution
 
-#Get years
-using Dates
-
-occ_with_dates = dropmissing(occ_df, :date)
-occ_with_dates.year = year.(occ_with_dates.date)
-
-#Calculate mode per species
-Pkg.add("StatsBase")
+# Calculate median date for each species
 using StatsBase
+
 group_species = groupby(occ_with_dates, :species)
-mode_species = combine(group_species, :year => StatsBase.mode)
-Pkg.rm("StatsBase")
+median_species = combine(group_species, :year => StatsBase.median)
 
 
-# Plot the distribution of the occurrences' year of record per species
+# Plot the distribution of the occurrences' year of record for each species
 p = plot(layout = 32, size = (1200, 800), dpi= 600)
 
 for i in 1:32
     plot!(group_species[i].year, subplot = i, title = replace(levels(occ_df.species)[i], "_" => " "), titlefontsize = 7,
-    seriestype=:histogram, legends = :none, fillcolor = "black", bins = :scott, xlims = extrema(occ_with_dates.year))
[…]

### 2022-11-22 code/10-GBIF_comparison.jl
✨ use only recent GBIF obs in validation

@@ -21,10 +21,19 @@ ranges_updated = [geotiff(SimpleSDMPredictor, joinpath("data", "clean", "ranges_
 occ_df = CSV.read(joinpath("data", "clean", "gbif_occurrences.csv"), DataFrame)
 gbif_ranges = [geotiff(SimpleSDMPredictor, joinpath("data", "clean", "gbif_ranges.tif"), i) for i in eachindex(mammals)]
 
+# Keep recent GBIF occurrences only 
+year_recent = 2000
+
+occ_with_dates = dropmissing(occ_df, :date)
+occ_with_dates.year = year.(occ_with_dates.date)
+
+occ_df_recent = subset(occ_with_dates, :year => ByRow(>(year_recent)))
+
+
 ## Get IUCN range values at GBIF occurrences
 
 # Separate occurrences per species
-spp_df = [filter(:species => ==(m), occ_df) for m in mammals];
+spp_df = [filter(:species => ==(m), occ_df_recent) for m in mammals];
 
 # Get values from IUCN layers at corresponding GBIF coordinates
 for (i, df) in enumerate(spp_df)
@@ -33,16 +42,16 @@ for (i, df) in enumerate(spp_df)
 end
 
 # Reassemble in single DataFrame
-occ_df = reduce(vcat, spp_df)
+occ_df_recent = reduce(vcat, spp_df)
 
 # Replace nothings by zeros before performing sum
-replace!(occ_df.IUCN, nothing => 0.0)
-replace!(occ_df.IUCN_updated, nothing => 0.0)
+replace!(occ_df_recent.IUCN, nothing => 0.0)
+replace!(occ_df_recent.IUCN_updated, nothing => 0.0)
 
 ## Compare GBIF occurrences with IUCN ranges
 
 # Get number of occurrences in IUCN ranges
-comparison_occ = @chain occ_df begin
+comparison_occ = @chain occ_df_recent begin
     groupby(:species)
     @combine(
         total_occ = length(:species),
@@ -230,8 +239,8 @@ for i in eachindex(mammals)
     plot!(worldshape(50); c=:lightgrey, lc=:lightgrey, alpha=0.6)
     plot!(ranges[i]; c=:turku, colorbar=:none)
     scatter!(
-        occ_df[occ_df.species .== mammals[i], :longitude],
-        occ_df[occ_df.species .== mammals[i], :latitude];
+        occ_df_recent[occ_df_recent.species .== mammals[i], :longitude],
[…]

### 2022-11-23 code/A3_gbif_query.jl
✨ download & export the occurrence data from the download API

@@ -2,6 +2,8 @@
 
 include("A1_required.jl")
 
+## 1. GBIF Query ###
+
 # Bounding box
 lat, lon = (bounding_box.bottom, bounding_box.top), (bounding_box.left, bounding_box.right)
 left, right, bottom, top = bounding_box
@@ -56,3 +58,61 @@ end
 # download link (probably within minutes)
 
 # ⚠️ DO NOT COMMIT THE FILES WITH YOUR USERNAME, EMAIL, OR PASSWORD ⚠️
+
+## 2. Download dataset ####
+
+# Download & extract dataset if absent
+csv_file = joinpath("data", "gbif_occurrences_query.csv")
+zip_file = joinpath("data", "gbif_occurrences_query.zip")
+if !isfile(csv_file)
+    if !isfile(zip_file)
+        download("https://api.gbif.org/v1/occurrence/download/request/0174925-220831081235567.zip", zip_file)
+    end
+    zf = ZipFile.Reader(zip_file)
+    write(csv_file, read(zf.files[1]))
+    close(zf)
+end
+
+## 3. Select the columns of interest ###
+
+# Load the dataset
+occ_df = CSV.read(joinpath(csv_file), DataFrame; delim="\t", quoted=false)
+
+# Note that quoted=false is absolutely necessary to avoid a bug while reading.
+# After manual verification, the data is not quoted.
+# However, some elements in the occurrenceID column start with a ", which is the
+# quote character. E.g. "AFEW-DSCN0025
+# The bug specifically happens on line 59,279 which you can reproduce with:
+# DataFrame(CSV.File(csv_file), delim="\t", ntasks=1, limit=59278)) # works
+# DataFrame(CSV.File(csv_file), delim="\t", ntasks=1, limit=59279)) # doesn't
+
+# Select the columns of interest
+select!(occ_df, [:species, :decimalLongitude, :decimalLatitude, :eventDate])
+
+# Quick note: following the Darwing Core (https://dwc.tdwg.org/terms/) and
+# GBIF.jl, we are interested in the eventDate column, not dateIdentified
+
+# Rename columns
+rename!(occ_df, [:species, :longitude, :latitude, :date])
+
+## 4. Additional data manipulations
+
+# Arrange species names as elsewhere
+occ_df.species = replace.(occ_df.species, " " => "_")
+
+# Remove observations with coordinates around (0.0, 0.0) which are outside mainland
[…]

### 2022-11-23 response-letter.md
Responses 1 & 5 [Review_02] response letter #89

--- 2022-07-15 response-letter.md
@@
 
-Thank you for the valuable feedback on our manuscript. We are pleased that you
-and the reviewer found interest and worth in our manuscript. We addressed each comment and found that the manuscript is indeed clearer now, and we hope to have it approved after your consideration.
+Thank you for the inviting a specialist on large scale biodiversity patterns of
+Africa to review our manuscript. We were happy to see that the first reveiwer
+was satisfied with our response, and that the second reviewer also saw value in
+our contribution. The new comments were very pertinent and we hope that this
+letter and the changes we've made to the paper are satisfactory.
 
-We have added more context in the introduction section, but we've found it hard
-to expand the first paragraph. We believe that this particular paragraph needs
-to be more succinct, at the same time that it provides a complete picture of the
-paper, framed in a storytelling structure. Then, on the second paragraph, we
-start providing literature background and many examples, to help the reader
-understand where our paper stands in the scientific context. We have included
-discussions about the quality and accuracy of range maps (lines XX-XX), examples
-of data biases (lines XX-XX), and we addressed the uniqueness of our study
-compared to previous research (lines XX-XX). We hope that this structure is
-clarifying and appealing to the readers.
+We have improved the text in order to avoid misleading phrasing. For example, we
+understand that using the words "updated ranges" can be read as distribution
+modelling, which is not the case: here, we simply use a method to identify areas
+where the predator range does not match with their prey's range, which might
+indicate distribution uncertainty areas.
 
-Regarding the GBIF data cleaning, retrieval and the validation steps, we added a
-more detailed description of our process (lines XX-XX, XX-XX and XX-XX). Data
-retrieving is detailed in the source code provided on our GitHub repository
-(code/09-GBIF_data.jl). We used the list of species from the network dataset and
-retrieved any occurrence within our bounding box (between longitudes -20.0 and
-55.0 degrees; and latitudes -35.0 and 40.0 degrees). We changed a two things
-regarding geographical information during data retrieval:
-1. We had originally added an argument to capture only the data that had
-   information about the continent location equals to "AFRICA". However, this
-   constrained our search by thousands of occurrences, and added a filtering
-   layer that could be interpreted as "data cleaning". We removed that because
-   we don't perform any kind of data cleaning with the IUCN dataset.
+We have also addressed reviewer's concerns about the GBIF data (see below): our investigations show that most of the data we were using are recent (from the last 20 years).
+We describe the time distribution of GBIF records to explicit that.
+Finally, we have improved the methods and the discussion sections to include more detailed descriptions of the data being used and to give more context to the results.
+We detail specific changes below (line numbers refer to the clean, revised PDF file).
 
-2. We added, however, a constraint to exclude occurrences falling within a 4°x4°
-   degrees square around the "Null Island" (see code/09-GBIF_data.jl#L42 on our
-   repository). Rather than a data cleaning step, we see this as a geographic
-   filter complementing the bounding box we used to retrieve data from GBIF and
-   to limit IUCN range maps. This is important because the existence of
-   coordinates is a fundamental part of our analysis, and a (00,00) coordinate
-   can be interpreted as a null coordinate.
+>*"1.
+In the extent of the study, the authors mention that they “restricted the rasters a spatial extent comprised between latitudes 35°S and 40°N and longitudes 20°W and 55°E.
+“ – which is the whole of Africa.
+Since the study uses a dataset from Tanzania (Serengeti food web dataset), roughly 3% of the continent, how did the authors deal with the presence of putative prey items in other parts of the continent that are absent from the Serengeti food web dataset?
+For example Papio ursinus, Sylvicapra caffra and S.
+grimmia don't occur in Tanzania but are prey items to many carnivores in Africa."*
 
-Some taxonomic investigation needed to be done due to inconsistencies between
-GBIF and IUCN nomenclatures which would block our analysis completely (in the case of _Taurotragus oryx_).
-However, in the case of *Canis aureus*, as discussed in the paper, we could not track wich occurrences or which maps corresponded to which species, which we think is a great illustration of our point.
-We didn't
-perform any further data cleaning procedures because this could hinder the goals
-of the paper, which was to investigate the characteristics of the data available
-for research. As we needed to compare two sets of raw data, and data cleaning
-protocols are dependent on the use objectives, we chose to avoid data
-manipulation both for GBIF and IUCN datasets.
+>*"5.
+Taxonomic groups: Carnivores feed on a diversity of items, beyond herbivores.
+Their diet might include birds, fish, reptiles, amphibians, and even invertebrates.
+How did the authors account for the fact that despite missing the herbivores from Serengeti, there were other sources of protein that could sustain the species in the continent?"*
 
-For the validation step, we understand our phrasing was confusing, and we have
-rewritten this section to clarify our method. Rather than using
-absence data, what we did was to transform the point data into raster files, and
-then restrict our range maps to the locations where we had GBIF occurrences.
-Therefore, the pixels where there are no GBIF occurrences are not considered
-true absence of a species, but absence of **data** about the occurrence of that
-species.
+We have found that these two comments address the same issue: the representativity of the Serengeti foodweb.
+First, we would like to emphasize that our analysis is meant to be a proof of concept, showing the consequences of data limitation.
+Therefore, rather than trying to gather an exhaustive foodweb dataset - with information for all possible interactions for all occurring mammals in the African continent -, we looked for a very complete, readily available, widely used and well known dataset which could represent the main interactions in that area.
+Interaction data is difficult to collect, especially at broad scales.
+Because of that, we expected that no foodweb would be complete, and we are aware of the biases of our interactions data.
+However, the goal of this paper is to investigate precisely what happens if we need to deal with incomplete and biased datasets, because we believe that this might lead us to describe unrealistic ecological communities at the local scale.
+More than that, we believe that data incompleteness is not a limitation of our study, but one of its strengths, because we present a simple method to identify and describe these limitations.
 
-Finally, we have addressed all the other minor comments throughout the text as
-described below:
-- We've added citations in the Methods section to support our argument that a
-  mismatch between ranges can be originated from different sources (L. 68-70)
-- We have suppressed lines 214-217.
-- The abstract is now restructured according to PeerJ guidelines.
-- References to tables and figures in the Discussion section were suppressed,
-  with the exception of Figure 05 (line XX), which is an example of our results
-  to clarify an important point of the discussion.
-- Lines 22-23 (now lines XX-XX): the cited literature are not examples of models
-  that do not take ecological interactions into account, but studies that have
-  demonstrated how ecological interactions might be responsible for shaping a
-  species' distribution. We've rewritten the sentence to clarify that.
--  Lines 68-70: we have rewritten the sentence to include the consideration
-   misestimation of both species in a trophic interaction. We have also added
-   citations and examples.
-- We have addressed the grammatical suggestions throughout the text, except for
-  the legend of figure 1. We thought that the suggested phrasing adds a little
-  bit of confusion to the comprehension of the figure.
+That being said, the foodweb database that we chose is known for being representative for these animals on the whole African continent (as we can see, for example, in de Visser, Freymann and Olff, 2011).
+Although our dataset miss a few links, again, it was not our goal to make a comprehensive analysis of all the area where a predator would miss a prey based on all the knowledge available or not, but rather demonstrate what can happen if we deal with incomplete datasets, highlight the importance of accounting for uncertainty when dealing with species distribution data, and call to attention the need to make more interaction data open.
+Moreover, many of the prey items on Baskerville's dataset were also found outside the Serengeti park area, and our method only needed one link connecting a predator to a herbivore to "keep" a pixel from a predator's range.
+Therefore, the impact of the missing links on the foodweb should be of great magnitude to invalidate our methods.
+
+Finally, some of the results we highlight would not change with the addition of new prey items.
+For example, the *Canis aureus* results are due mainly to an apparent taxonomic disagreement - which is indeed connected to its interaction data, but this would not change with a more complete list of preys for this species.
+
+To emphasize and clarify these points, we have changed lines XX, XX and XX on the manuscript.
 

### 2022-11-23 response-letter.md
Forgot to wrap, sorry!

@@
 
-We have also addressed reviewer's concerns about the GBIF data (see below): our investigations show that most of the data we were using are recent (from the last 20 years).
-We describe the time distribution of GBIF records to explicit that.
-Finally, we have improved the methods and the discussion sections to include more detailed descriptions of the data being used and to give more context to the results.
-We detail specific changes below (line numbers refer to the clean, revised PDF file).
+We have also addressed reviewer's concerns about the GBIF data (see below): our
+investigations show that most of the data we were using are recent (from the
+last 20 years). We describe the time distribution of GBIF records to explicit
+that. Finally, we have improved the methods and the discussion sections to
+include more detailed descriptions of the data being used and to give more
+context to the results. We detail specific changes below (line numbers refer to
+the clean, revised PDF file).
 
->*"1.
-In the extent of the study, the authors mention that they “restricted the rasters a spatial extent comprised between latitudes 35°S and 40°N and longitudes 20°W and 55°E.
-“ – which is the whole of Africa.
-Since the study uses a dataset from Tanzania (Serengeti food web dataset), roughly 3% of the continent, how did the authors deal with the presence of putative prey items in other parts of the continent that are absent from the Serengeti food web dataset?
-For example Papio ursinus, Sylvicapra caffra and S.
-grimmia don't occur in Tanzania but are prey items to many carnivores in Africa."*
+>*"1. In the extent of the study, the authors mention that they “restricted the
+>rasters a spatial extent comprised between latitudes 35°S and 40°N and
+>longitudes 20°W and 55°E. “ – which is the whole of Africa. Since the study
+>uses a dataset from Tanzania (Serengeti food web dataset), roughly 3% of the
+>continent, how did the authors deal with the presence of putative prey items in
+>other parts of the continent that are absent from the Serengeti food web
+>dataset? For example Papio ursinus, Sylvicapra caffra and S. grimmia don't
+>occur in Tanzania but are prey items to many carnivores in Africa."*
 
->*"5.
-Taxonomic groups: Carnivores feed on a diversity of items, beyond herbivores.
-Their diet might include birds, fish, reptiles, amphibians, and even invertebrates.
-How did the authors account for the fact that despite missing the herbivores from Serengeti, there were other sources of protein that could sustain the species in the continent?"*
+>*"5. Taxonomic groups: Carnivores feed on a diversity of items, beyond
+>herbivores. Their diet might include birds, fish, reptiles, amphibians, and
+>even invertebrates. How did the authors account for the fact that despite
+>missing the herbivores from Serengeti, there were other sources of protein that
+>could sustain the species in the continent?"*
 
-We have found that these two comments address the same issue: the representativity of the Serengeti foodweb.
-First, we would like to emphasize that our analysis is meant to be a proof of concept, showing the consequences of data limitation.
-Therefore, rather than trying to gather an exhaustive foodweb dataset - with information for all possible interactions for all occurring mammals in the African continent -, we looked for a very complete, readily available, widely used and well known dataset which could represent the main interactions in that area.
-Interaction data is difficult to collect, especially at broad scales.
-Because of that, we expected that no foodweb would be complete, and we are aware of the biases of our interactions data.
-However, the goal of this paper is to investigate precisely what happens if we need to deal with incomplete and biased datasets, because we believe that this might lead us to describe unrealistic ecological communities at the local scale.
-More than that, we believe that data incompleteness is not a limitation of our study, but one of its strengths, because we present a simple method to identify and describe these limitations.
+We have found that these two comments address the same issue: the
+representativity of the Serengeti foodweb. First, we would like to emphasize
+that our analysis is meant to be a proof of concept, showing the consequences of
+data limitation. Therefore, rather than trying to gather an exhaustive foodweb
+dataset - with information for all possible interactions for all occurring
+mammals in the African continent -, we looked for a very complete, readily
+available, widely used and well known dataset which could represent the main
+interactions in that area. Interaction data is difficult to collect, especially
+at broad scales. Because of that, we expected that no foodweb would be complete,
+and we are aware of the biases of our interactions data. However, the goal of
+this paper is to investigate precisely what happens if we need to deal with
+incomplete and biased datasets, because we believe that this might lead us to
+describe unrealistic ecological communities at the local scale. More than that,
+we believe that data incompleteness is not a limitation of our study, but one of
+its strengths, because we present a simple method to identify and describe these
+limitations.
 
-That being said, the foodweb database that we chose is known for being representative for these animals on the whole African continent (as we can see, for example, in de Visser, Freymann and Olff, 2011).
-Although our dataset miss a few links, again, it was not our goal to make a comprehensive analysis of all the area where a predator would miss a prey based on all the knowledge available or not, but rather demonstrate what can happen if we deal with incomplete datasets, highlight the importance of accounting for uncertainty when dealing with species distribution data, and call to attention the need to make more interaction data open.
-Moreover, many of the prey items on Baskerville's dataset were also found outside the Serengeti park area, and our method only needed one link connecting a predator to a herbivore to "keep" a pixel from a predator's range.
-Therefore, the impact of the missing links on the foodweb should be of great magnitude to invalidate our methods.
+That being said, the foodweb database that we chose is known for being
+representative for these animals on the whole African continent (as we can see,
+for example, in de Visser, Freymann and Olff, 2011). Although our dataset miss a
+few links, again, it was not our goal to make a comprehensive analysis of all
+the area where a predator would miss a prey based on all the knowledge available
+or not, but rather demonstrate what can happen if we deal with incomplete
+datasets, highlight the importance of accounting for uncertainty when dealing
+with species distribution data, and call to attention the need to make more
+interaction data open. Moreover, many of the prey items on Baskerville's dataset
+were also found outside the Serengeti park area, and our method only needed one
+link connecting a predator to a herbivore to "keep" a pixel from a predator's
+range. Therefore, the impact of the missing links on the foodweb should be of
+great magnitude to invalidate our methods.
 
-Finally, some of the results we highlight would not change with the addition of new prey items.
-For example, the *Canis aureus* results are due mainly to an apparent taxonomic disagreement - which is indeed connected to its interaction data, but this would not change with a more complete list of preys for this species.
+Finally, some of the results we highlight would not change with the addition of
+new prey items. For example, the *Canis aureus* results are due mainly to an
+apparent taxonomic disagreement - which is indeed connected to its interaction
+data, but this would not change with a more complete list of preys for this
+species.
 
-To emphasize and clarify these points, we have changed lines XX, XX and XX on the manuscript.
+To emphasize and clarify these points, we have changed lines XX, XX and XX on
+the manuscript.
 

### 2022-11-23 response-letter.md
Questions 2 and 4 [Review_02] response letter #89

@@
 
+>*"4. The gbif records for large mammals are especially problematic. Did the
+>authors include observations as well? iNaturalist for instance now feeds data
+>directly to GBIF. Having museum specimens of lions and other large/medium
+>mammals are especially problematic and difficult to achieve nowadays. Many
+>countries such as Malawi and Mozambique conduct very little research and many
+>areas are not documented, not even on GBIF. Therefore the occurrences we see on
+>GBIF are biased towards countries that have available data. How did the authors
+>account for this? See https://doi.org/10.1093/sysbio/syaa090"*
+
+Similar to the questions above, this one is also about incompleteness of data.
+As we stated on our previous review letter, "we didn't perform any [...] data
+cleaning procedures because this could hinder the goals of the paper, which was
+to investigate the characteristics of the data available for research. As we
+needed to compare two sets of raw data, and data cleaning protocols are
+dependent on the use objectives, we chose to avoid data manipulation both for
+GBIF and IUCN datasets". For that reason, our query for the GBIF data did not
+include any filters other than the ones described on the paper for the reasons
+described above.
+
+Additionally, we could add a plethora of other datasets both on
+interactions and occurrences, but we decided to use only the IUCN, the GBIF and
+the Baskerville's data to keep the analysis simple (although not simplistic),
+straightforward, and reflective of the volume of data generally used by
+ecologists.
+
+Finally, the fact that many data are still to be made open is precisely the
+major motivation of this paper. As computational ecologists and open data
+creators/managers/advocates, we are very aware of the biases produced by
+undocumented data. We expect to call attention about this issue with our proof
+of concept, as it demonstrates that we gain a lot of uncertainty when we miss a
+link because of an information that is not accessible. The implications of this
+complex issue for conservation are multifold, and we believe that more open data
+is one of the possible solutions.
+
+>*"2.    The resolution: it is well studied that IUCN range maps should not be
+>converted to grids smaller than 50km due to commission errors. This becomes a
+>major problem when dealing with widespread species such as the ones used in
+>this study: African large and medium mammals. See
+>https://doi.org/10.1111/1365-2664.12771 and
+>https://doi.org/10.1073/pnas.070446910"*
+
+We agree and we have updated our rasters to be now at 50km of resolution. Our
+overall results did not change with that (see lines XX, XX and XX).
+
+>*"3. Gbif records: using records from any period in time from gbif will include
+>historical relics from extinct populations. Many large and medium mammals,
+>especially large carnivores have suffered major declines in the last decades in
+>Africa. How did the authors deal with the fact that records from a species
+>recorded 50 years ago may represent extinct populations?"*
+
 We hope our revised manuscript is now more appropriate for publishing at PeerJ.

### 2022-11-23 code/09-GBIF_data.jl
✨ replace JLD2 files by reproducible GBIF query ones

@@ -1,106 +1,34 @@
 include("A1_required.jl")
 
-# Getting taxa codes
-sp_codes = taxon.(mammals, rank = :SPECIES)
-
-# Bounding box
-lat, lon = (bounding_box.bottom, bounding_box.top), (bounding_box.left, bounding_box.right)
-
-# Getting observations
-#=
-## Start query
-occ = occurrences.(
-    sp_codes,
-    "hasCoordinate" => "true",
-    "decimalLatitude" => lat,
-    "decimalLongitude" => lon,
-)
-## Loop to get all occurrences
-Threads.@threads for o in occ
-    while length(o) < size(o)
-        occurrences!(o)
-    end
-    @info "$(o.occurrences[1].taxon.name) occurrences returned ($(length(o))/$(size(o)))"
-end
-# Export to JLD2 for faster reload
-
-@save joinpath("data", "clean", "gbif-occurrences.jld2") occ
-=#
-@load joinpath("data", "clean", "gbif-occurrences.jld2") occ
-
-
-## Create DataFrame
-
-# Make Data Frames
-occ_df = DataFrame.(occ)
-occ_df = reduce(vcat, occ_df)
-select!(occ_df, :species, :longitude, :latitude)
-occ_df.species = replace.(occ_df.species, " " => "_")
-
-# Remove observations with coordinates around (0.0, 0.0) which are outside mainland
-filter!(x -> !(x.latitude > -2.0 && x.latitude < 2.0 && x.longitude > -2.0 && x.longitude < 2.0), occ_df)
-
-# Make sure the species names match
-isequal(unique(occ_df.species), mammals) # not the same
-setdiff(unique(occ_df.species), mammals) # Taurotragus oryx is the difference
-
-id_mismatch = filter(x -> !(x.species in mammals), occ_df)
-unique(id_mismatch.species) # Yep it's only Taurotragus oryx
-# The GBIF website agrees it's a synonym of Tragelaphus oryx, citing IUCN as source, so we're good
-
-replace!(occ_df.species, "Taurotragus_oryx" => "Tragelaphus_oryx")
-isequal(unique(occ_df.species), mammals) # true
-
-# Save as CSV
-CSV.write(joinpath("data", "clean", "gbif_occurrences.csv"), occ_df)
-
-## Investigate difference with original query with Africa as continent
-# Load datasets
[…]

### 2022-11-23 code/A3_gbif_query.jl
✨ create main script to easily re-run all analyses

@@ -4,7 +4,16 @@ include("A1_required.jl")
 
 ## 1. GBIF Query ###
 
-# Bounding box
+# Create the query to the GBIF download API to retrieve the species occurrences.
+# Note that this is the exact code we used to create our query on November 22nd
+# 2022. Re-run this 1st part only if you want to create a new query for yourself
+# as it will be different from ours as soon as new species observations are
+# added.
+
+# In contrast, the 2nd part of this script will always download the exact same
+# set of occurrences generated by our own query.
+
+# Create bounding box
 lat, lon = (bounding_box.bottom, bounding_box.top), (bounding_box.left, bounding_box.right)
 left, right, bottom, top = bounding_box
 
@@ -60,6 +69,9 @@ end
 # ⚠️ DO NOT COMMIT THE FILES WITH YOUR USERNAME, EMAIL, OR PASSWORD ⚠️
 
 ## 2. Download dataset ####
+
+# The following parts of this script can be re-ran at any time and will always
+# download the exact same set of occurrences generated by our own query.
 
 # Download & extract dataset if absent
 csv_file = joinpath("data", "gbif_occurrences_query.csv")

### 2022-11-23 code/main.jl

@@ -1,0 +1,57 @@
+#### Main analysis script ####
+
+# Uncommented `include` statements allow reproducing the main analyses without
+# re-running any part multiple time. Commented statements will re-run
+# intermediate analysis steps or preparation steps that only need to be run
+# once.
+
+# 0. Get the IUCN rasters
+
+# Run this ONLY if you want to download the IUCN rasters for the first time.
+# We do not recommended running this script if you already have the rasters used
+# in our analyses as the files may change, for instance if there is a new
+# assessment for a species.
+
+# include("00_get_rasters.jl")
+
+# 1. Network and range update analysis
+
+# The following files all depend on each other, therefore running the last one
+# will also re-run all the previous ones. This is because the intermediate
+# objects are too big to be easily exported and version-controlled. Note that
+# you can still run script 03, for example, and it will run scripts 01 and 02
+# as required.
+
+# include("01-load_rasters.jl")
+# include("02-get_networks.jl")
+# include("03-analyse_cooccurrence.jl")
+# include("04-ranges_diff.jl")
+# include("05-degrees.jl")
+include("06-scatterplots.jl")
+
+# 2. Summary of range update analyses
+
+# These scripts compute summary statistics, plots, and tables of the previous
+# analyses. They can be run independently without re-running the previous
+# scripts.
+
+include("07-updated_ranges.jl")
+include("08-export_table.jl")
+
+# 3. GBIF analyses
+
+# The following script will create the query to the GBIF download API to
+# retrieve the species occurrences. Re-running the 1st part will allow you to
+# create a new query for yourself but it will be different from ours as soon as
+# new species observations are added.
+
+# In contrast, the 2nd part of this script will always download the exact same
+# set of occurrences generated by our own query.
+
+# include("A3_gbif_query.jl")
+
+# Next, the GBIF analysis steps can all be re-ran independently.
+
+include("09-GBIF_data.jl")
+include("10-GBIF_comparison.jl")
+include("11-GBIF_doublecheck.jl")

### 2022-11-25 draft.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@307af17afc7bd5c52cabd15da04e6a5711587f30 🚀

@@
 For each species in the dataset we collated point observation data from
-GBIF (www.gbif.org). We restricted our queries to the data with spatial
-coordinates and which were inside the spatial extent of our rasters. We
-did not use continental or date filters to retrieve as much data as
-possible. However, a few observations were localized in the ocean near
-latitude 0° and longitude 0°. We assumed these were errors and removed
-all observations falling in the extent between latitudes 2°S and 2°N and
-longitudes 2°W and 2°E to keep only mainland sites.
+GBIF (www.gbif.org). We used the GBIF download API to retrieve all
+species occurrences on November 22nd 2022 (GBIF.org 2022). We restricted
+our query to the data with spatial coordinates and which were inside the
+spatial extent of our rasters. We did not use continental or date
+filters to retrieve as much data as possible. However, a few
+observations were localized in the ocean near latitude 0° and longitude
+0°. We assumed these were errors and removed all observations falling in
+the extent between latitudes 2°S and 2°N and longitudes 2°W and 2°E to
+keep only mainland sites.
 
@@
 manipulate the interaction networks, and \texttt{GBIF.jl} (Dansereau and
-Poisot 2021) to retrieve the species occurrences from GBIF. We also used
-\emph{GDAL} (GDAL/OGR contributors 2021) to rasterize the IUCN range
-maps (initially available as shapefiles from the Spatial Data Download
-portal). All the scripts required to reproduce the analyses are
-available at https://doi.org/10.5281/zenodo.6842861.
+Poisot 2021) to reconcile species names with the GBIF backbone taxonomy
+(GBIF Secretariat 2021). We also used \emph{GDAL} (GDAL/OGR contributors
+2021) to rasterize the IUCN range maps (initially available as
+shapefiles from the Spatial Data Download portal). All the scripts
+required to reproduce the analyses are available at
+https://doi.org/10.5281/zenodo.6842861.
 
@@
 
+\leavevmode\hypertarget{ref-GBIF.org2022GbiOcc}{}%
+GBIF.org. 2022. {``GBIF Occurrence Download.''} The Global Biodiversity
+Information Facility. \url{https://doi.org/10.15468/DL.PF4586}.
+
+\leavevmode\hypertarget{ref-GBIFSecretariat2021GbiBac}{}%
+GBIF Secretariat. 2021. {``GBIF Backbone Taxonomy.''}
+\url{https://doi.org/10.15468/39omei}.
+
 \leavevmode\hypertarget{ref-GDALux2fOGRcontributors2021GdaOgr}{}%

### 2022-11-25 draft.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@44cf0d87cc5a83ee9702e8b4b9bbcfb9c91ec7a3 🚀

@@
 allows us to detect areas of potential misestimation of species'
-distribution data (more precisely range maps) based on interaction data,
-considering the basic assumption that predators can only be present in
-regions where they are connected to at least one herbivore - and thus
-indirectly connected to primary producers. We used a Serengeti food web
-dataset (Baskerville et al. 2011) (which comprises carnivores,
-herbivores, and plants from Tanzania) to demonstrate how a mismatch
-between occurrence and interaction data can highlight significant
-uncertainty areas in IUCN range maps. Finally, we add the GBIF
-occurrence points for the Serengeti species to the investigation,
-discuss the mechanisms that can lead to the lack of agreement between
-data, and build from that a vision for the next steps, reinforcing the
-importance of geographically explicit interaction data.
+distribution data (more precisely range maps) based on interaction data.
+This method is based on the assumption that organisms cannot persist in
+an area unless they are directly or indirectly connected to a primary
+producer within their associated food web (Power 1992). Thus, given that
+herbivores are the main connection between plant resources (directly
+limited by environmental conditions) and predators (Dobson 2009; Scott
+et al. 2018), the range of a predator (omnivore or carnivore) depends on
+the overlapping ranges of its herbivore preys. If sections of a
+predator's range does not overlap with at least one of its prey it will
+become disconnected from primary producers, and therefore we would not
+expect the predator to occur in this area.
+
+This mismatch can be the result of different mechanisms, like the
+misestimation of both the predator's and the preys' ranges (Ladle and
+Hortal 2013; Rondinini et al. 2006), taxonomic errors (Isaac, Mallet,
+and Mace 2004; Ladle and Hortal 2013), or the lack of information about
+trophic links (i.e., the lack of connection between the ranges of a
+predator and a primary producer may be due a third species we don't know
+is connected to both). Here we discuss the mechanisms that can lead to
+the lack of agreement between data, and build from that a vision for the
+next steps, reinforcing the importance of geographically explicit
+interaction data.
 
@@
 
-Organisms cannot persist unless they are directly or indirectly
-connected to a primary producer within their associated food web (Power
-1992). Therefore, the range of a predator (omnivore or carnivore)
-depends on the overlapping ranges of its preys. If sections of a
-predator's range does not overlap with at least one of its prey it will
-become disconnected from primary producers, and therefore we would not
-expect the predator to occur in this area. This mismatch can be the
-result of different mechanisms, like the misestimation of both the
-predator's and the preys' ranges (Ladle and Hortal 2013; Rondinini et
-al. 2006), taxonomic errors (Isaac, Mallet, and Mace 2004; Ladle and
-Hortal 2013), or the lack of information about trophic links (i.e., the
-lack of connection between the ranges of a predator and a primary
-producer may be due a third species we don't know is connected to both).
-Thus, given that herbivores are the main connection between plant
-resources (directly limited by environmental conditions) and predators
-(Dobson 2009; Scott et al. 2018), here we adjusted the ranges of
-predators based on a simple rule: we removed any part of a predator's
-range that did not intersect with the range of at least one prey
-herbivore species. So, unless the range of the predator overlapped with
-at least one prey item, which in turn is directly connected to a primary
-producer (plants), we removed that section of the predator's range.
-Finally, we calculated the difference in range size between the original
-IUCN ranges and those adjusted based on species interaction data.
-
-\hypertarget{data}{%
-\subsection{Data}\label{data}}
+We indentified areas of uncertainty on the ranges of predators based on
+a simple rule: we removed any part of a predator's range that did not
+intersect with the range of at least one prey herbivore species, which
+in turn is directly connected to a primary producer (plants). To do
+that, we used a Serengeti food web dataset (Baskerville et al. 2011)
+(which comprises carnivores, herbivores, and plants from Tanzania) and
+its species ranges from IUCN. Then, we calculated the difference in
+range sizes between the original IUCN ranges of predators and those
+without the areas where they would be alone, based on species
+interaction data. Finally, we added the GBIF occurrence points for the
+Serengeti species to investigate whether the results would be different
+if we used another source of distribution data. \#\# Data
 
@@
 (www.iucnredlist.org/resources/spatial-data-download), which we
-rasterized at 10 arc-minute resolution (\textasciitilde18 km at the
-equator). We restricted the rasters a spatial extent comprised between
-latitudes 35°S and 40°N and longitudes 20°W and 55°E. We then combined
-interaction data from the metaweb and cooccurrence data generated from
-species ranges to create networks for each raster pixel. This generated
-a total of 84,244 pixel-level networks. These networks describe
-potential predation, not actual interactions: the former is derived
-information from the metaweb, and the latter is contingent on the
-presence of herbivores.
+rasterized at a 0.5 degrees resolution (\textasciitilde50 km at the
+equator). We restricted the rasters to a spatial extent comprised
+between latitudes 35°S and 40°N and longitudes 20°W and 55°E. We then
+combined interaction data from the metaweb and cooccurrence data
+generated from species ranges to create networks for each raster pixel.
+This generated a total of 11,308 pixel-level networks. These networks
+describe potential predation, not actual interactions: the former is
+derived information from the metaweb, and the latter is contingent on
+the presence of herbivores.
 

### 2022-11-28 draft.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@281f7033735c759bbd6895f8b283e9e1e1155977 🚀

@@
 occurrences) and ecological interactions to identify mismatches between
-datasets.
+datasets and areas of data deficit.
 
@@
 (Alhajeri and Fourcade 2019). As for ecological data, a complete
-assessment is difficult and is aggravated by biased sampling methods and
-data aggregation (Poisot et al. 2020; Hortal et al. 2015). Nevertheless,
-we have witnessed an increase in the availability of biodiversity data
-in the last decades, including those collected through community science
-projects (Callaghan et al. 2019; Pocock et al. 2015) and dedicated
-databases, such as Mangal (Poisot et al. 2016). This provides an
-opportunity to merge species distribution and ecological interaction
-data to improve our predictions of where a species may be found across
-large spatial scales (e.g., continental and global).
+assessment is difficult and is aggravated by biased sampling methods,
+data aggregation (Poisot et al. 2020; Hortal et al. 2015) and by the
+fact that interactions are very often events that occur in a narrow
+window of time. Nevertheless, we have witnessed an increase in the
+availability of biodiversity data in the last decades, including those
+collected through community science projects (Callaghan et al. 2019;
+Pocock et al. 2015) and dedicated databases, such as Mangal (Poisot et
+al. 2016). This provides an opportunity to merge species distribution
+and ecological interaction data to improve our predictions of where a
+species may be found across large spatial scales.
 
@@
 likely to be true and which dataset better represent the actual
-distribution of species. In this context, we elaborate a method that
+distribution of a species. In this context, we elaborate a method that
 allows us to detect areas of potential misestimation of species'
@@
 predator and a primary producer may be due a third species we don't know
-is connected to both). Here we discuss the mechanisms that can lead to
-the lack of agreement between data, and build from that a vision for the
-next steps, reinforcing the importance of geographically explicit
-interaction data.
+is connected to both). Here in this proof of concept, we investigate the
+disagreements between available data for species that compose a
+well-known foodweb in the African continent, discuss the mechanisms that
+can lead to this, and reinforce the importance of open geographically
+explicit interaction data.
 
@@
 
-We indentified areas of uncertainty on the ranges of predators based on
-a simple rule: we removed any part of a predator's range that did not
+We indentified areas of data deficits on the ranges of predators based
+on a simple rule: we removed any part of a predator's range that did not
 intersect with the range of at least one prey herbivore species, which
@@
 our query to the data with spatial coordinates and which were inside the
-spatial extent of our rasters. We did not use continental or date
-filters to retrieve as much data as possible. However, a few
-observations were localized in the ocean near latitude 0° and longitude
-0°. We assumed these were errors and removed all observations falling in
-the extent between latitudes 2°S and 2°N and longitudes 2°W and 2°E to
-keep only mainland sites.
+spatial extent of our rasters. A few observations were localized in the
+ocean near latitude 0° and longitude 0°. We assumed these were errors
+and removed all observations falling in the extent between latitudes 2°S
+and 2°N and longitudes 2°W and 2°E to keep only mainland sites. We did
+not use any additional geographical filters to retrieve as much data as
+possible. Being mindful of the recent and remarkable anthropogenic
+impact on African megafauna, we decided to restrict the occurrences used
+on the validation step to those recorded after the year 2000 (and,
+therefore, only records with date information). This decision was made
+after evaluating the overall temporal distribution of the GBIF records.
 
@@
 Mammal species found in the Serengeti food web are widespread in Africa,
-especially in grasslands and savannahs (first panel of
-fig.~\ref{fig:richness}). However, most local networks (83.2\%) built
-using the original IUCN range maps had at least one mammal species
-without a path to a primary producer (second panel of
-fig.~\ref{fig:richness}). On average, local food webs had almost the
-third of their mammal species (mean = 30.5\%, median = 14.3\%)
-disconnected from basal species. In addition, many networks (16.6\%)
-only had disconnected mammals; these networks however all had a very low
-number of mammal species, specifically between 1 and 4 (from a total of
-32). As expected, the proportion of carnivores with a path to a primary
-producer was conditional on the total number of mammal species in each
-local network (third panel of fig.~\ref{fig:richness}).
+especially in grasslands and savannahs (panel \emph{(a)} of
+fig.~\ref{fig:richness}). From our analysis, most local networks
+(69.07\%) built using the original IUCN range maps had at least one
+mammal species with a path to a primary producer (panel \emph{(b)} of
+fig.~\ref{fig:richness}), which reinforces that the interactions we
+observe in the Serengeti foodweb is representative of the interactions
+for these mammals in the whole African continent. On average, local food
+webs had almost half of their mammal species disconnected from basal
+species (mean = 46.2\%, median = 33.3\%). In addition, 16.6\% of the
+networks only had disconnected mammals, and the number of mammal species
+varied from 1 to 28, with a mean of 6.7. As expected, the proportion of
+carnivores with a path to a primary producer was conditional on the
+total number of mammal species in each local network (third panel of
+fig.~\ref{fig:richness}).
 
@@
 
-\hypertarget{specialized-predators-lose-more-range}{%
-\subsection{Specialized predators lose more
-range}\label{specialized-predators-lose-more-range}}
+\hypertarget{specialized-predators-have-higher-rates-of-range-mismatch}{%
+\subsection{Specialized predators have higher rates of range
+mismatch}\label{specialized-predators-have-higher-rates-of-range-mismatch}}
 
@@
 \caption{Negative relationship between the out degree of predator
-species and their relative range loss. More specialized predators lose a
-higher proportion of their ranges due to mismatches with the ranges of
-their preys.}\label{fig:degree}
+species and their relative range mismatch. More specialized predators
+``lose'' a higher proportion of their ranges due to mismatches with the
+ranges of their preys.}\label{fig:degree}
 }
@@
 
-Predators with fewer prey lose more range with our method
-(fig.~\ref{fig:degree}). For instance, both \emph{Leptailurus serval}
-and \emph{Canis mesomelas} have only one prey in the Serengeti food web
-(tbl.~\ref{tbl:everyone}), each of them with a very small range compared
-to those of their predator. This discrepancy between range sizes
-promotes significant range loss. On the other hand, predators of the
-genus \emph{Panthera} are some of the most connected species, and they
-also lose the least proportion of their ranges. This mismatch between
-predators and preys can also be a result of taxonomic disagreement
-between the geographical and ecological data. Although \emph{Canis
-aureus} has the same number of prey as \emph{Caracal caracal}, none of
-the prey taxa of the former occurs inside its original range
-(tbl.~\ref{tbl:everyone}), which results in complete range loss.
+If we consider that we can not use areas where there are no
+superposition between predators and prey on ecological analyses, we lose
+more range area for predators with fewer prey (fig.~\ref{fig:degree}).
+For instance, both \emph{Leptailurus serval} and \emph{Canis mesomelas}
+have only one prey in the Serengeti food web (tbl.~\ref{tbl:everyone}),
+each of them with a very small range compared to those of their
+predator. This discrepancy between range sizes promotes significant
+range loss. On the other hand, predators of the genus \emph{Panthera}
+are some of the most connected species, and they also lose the least
+proportion of their ranges. This mismatch between predators and preys
+can also be a result of taxonomic disagreement between the geographical
+and ecological data. Although \emph{Canis aureus} has the same number of
+prey as \emph{Caracal caracal}, none of the prey taxa of the former
+occurs inside its original range (tbl.~\ref{tbl:everyone}), which
+results in complete range loss.
 
@@
 The proportion of GBIF pixels (pixels with at least one GBIF occurrence)
-falling within the IUCN ranges varied from low to high depending on the
-species (fig.~\ref{fig:gbif}, left). The lowest proportions occurred for
-species with small ranges. Amongst herbivores, \emph{Rhabdomys pumilio}
-has a proportion of 22.6\% of its presence pixels within its IUCN range,
-while predators have this proportion above 55\% (such as \emph{Lycaon
-pictus}, with 55.1\%, and \emph{Canis aureus}, with 56.2\%).
-Nevertheless, some species with smaller ranges showed high data overlap
-(such as \emph{Canis mesomelas}, with 94.9\%, and many herbivores).
-Overall, predators and preys displayed similar overlap variations, and
-species with median and large ranges had higher proportions of
-occurrences falling into their IUCN range.
-
-The proportion of GBIF pixels in updated ranges can only be equal to or
+matching the IUCN ranges varied a lot for species with small ranges and
+way less for species with large ranges (fig.~\ref{fig:gbif}, left). This
+means that species with large ranges had more area where their datasets
+for ecological and geographical information agreed. The lowest
+proportions of GBIF pixels occurred for species with small ranges.
+Amongst herbivores, \emph{Rhabdomys pumilio} has a proportion of 25.6\%
+of its presence pixels within its IUCN range, while predators have this
+proportion above 47\% (such as \emph{Lycaon pictus}, with 47.6\%, and
+\emph{Panthera leo}, with 49.3\%). Nevertheless, some species with
+smaller ranges showed high data overlap (such as \emph{Canis mesomelas},
+with 94.1\%, and many herbivores). Overall, predators and preys
+displayed similar overlap variations, and species with median and large
+ranges had higher proportions of agreement between GBIF, IUCN and
+interaction datasets.
+
+The proportion of GBIF pixels in revised ranges can only be equal to or
 lower than that of the original ranges, as our analysis removes pixels
@@
 original IUCN ranges for most predator species (fig.~\ref{fig:gbif}).
-Two species showed no difference in proportion while four species showed
-only small differences (\emph{Crocuta crocuta} lost 1.3\% of the
-original data overlap; \emph{Acinonyx jubatus} lost 1.9\%;
-\emph{Panthera pardus} lost 8.8\%; and \emph{Caracal caracal} lost
-12.3\%). On the other hand, three species, \emph{Canis aureus},
-\emph{Canis mesomelas}, and \emph{Leptailurus serval} showed very high
-differences, with overlaps lowered by 100\%, 57.4\%, and 100\%
-respectively. These last two species are also the only predators with a
-single prey in our metaweb. \emph{Canis aureus} has four preys, but it
-has one of the smallest ranges in IUCN, which is not covered by any of
-its preys. This result reinforces the concern raised in the literature
-on the use of IUCN range maps for species that are not well known
-(Herkt, Skidmore, and Fahr 2017), demonstrating how small range species
-are likely to have their distribution underestimated in the IUCN
-database. Additionally, the fact that \emph{Canis aureus} had such a
-conspicuous mismatch between both the original and updated IUCN range
-maps, and between GBIF and IUCN data, may indicate a taxonomic
+Two species showed no difference in proportion (\emph{Lycaon pictus} and
+\emph{Panthera leo}) while four species showed only small differences
+(\emph{Crocuta crocuta} lost 0.4\% of the original data overlap;
+\emph{Caracal caracal} lost 3.4\%; \emph{Acinonyx jubatus} and
+\emph{Panthera pardus} lost 6.2\%). On the other hand, three species,
+\emph{Canis aureus}, \emph{Canis mesomelas}, and \emph{Leptailurus
+serval} showed very high differences, with overlaps lowered by 100\%,
+58.4\%, and 100\% respectively. These last two species are also the only
+predators with a single prey in our metaweb. \emph{Canis aureus} has
+four preys, but it has one of the smallest ranges in IUCN, which is not
+covered by any of its preys. This result reinforces the concern raised
+in the literature on the use of IUCN range maps for species that are not
+well known (Herkt, Skidmore, and Fahr 2017), demonstrating how small
+range species are likely to have their distribution underestimated in
+the IUCN database. Additionally, the fact that \emph{Canis aureus} had
+such a conspicuous discrepancy between its original IUCN range and those
+of its preys, and between GBIF and IUCN data, may indicate a taxonomic
 incongruency between the three databases used here, which we explore in
@@
 does not necessarily aggravates this dissimilarity, but it is relevant
-for species with little ecological information or specialists.
+for species about which we have little ecological information or for
+specialists groups.
 
@@
 \caption{Left panel: Distribution of the proportion of GBIF pixels
-(pixels with at least one occurrence in GBIF) falling into the IUCN
-range for different range sizes. Right panel: Differences between the
-proportion of GBIF pixels falling into the IUCN and the updated ranges
-for every predator species. Arrows go from the proportion inside the
-original range to the proportion inside the updated range, which can
-only be equal or lower. Overlapping markers indicate no difference
-between the types of layers. Species markers are the same on both
-figures, with predators presented in distinct colored markers and all
-herbivores grouped in a single grey marker. Pixels represent a
-resolution of 10 arc-minutes.}\label{fig:gbif}
+(pixels with at least one occurrence in GBIF) supperposed by the IUCN
+range data for different range sizes. Right panel: Differences between
+the proportion of GBIF pixels matching the original and cropped IUCN
+range maps for every predator species. Arrows go from the proportion
+inside the original range to the proportion inside the revised range,
+which can only be equal or lower. Overlapping markers indicate no
+difference between the types of layers. Species markers are the same on
+both figures, with predators presented in distinct colored markers and
+all herbivores grouped in a single grey marker. Pixels represent a
+resolution of 0.5 degrees.}\label{fig:gbif}
 }
@@
 al. 2021; Stoyanov 2020). This debate probably influenced our results:
-with originally only 56.2\% of the GBIF pixels of the golden jackal
+with originally only 64.9\% of the GBIF pixels of the golden jackal
 overlapping with its IUCN data, we suspect that many of the GBIF
@@
 First, \emph{Panthera leo} was one of the species with no difference
-between ranges before and after our analysis, but 40.7\% of the GBIF
-occurrences for this species fell outside its IUCN range
+between ranges before and after our analysis, but 50.7\% of its IUCN
+range map is not covered by the GBIF occurrences for this species, and
+26.4\% of the GBIF point data does not overlap with its IUCN range map
 (fig.~\ref{fig:gbif}). In this particular case, the IUCN maps seem to
@@
 the IUCN and the GBIF databases is concerning and suggests that the IUCN
-maps might underestimate the lion's distribution.
+maps might overestimate the lion's distribution.
 
@@
 also some of the species with the higher proportion of GBIF occurrences
-inside IUCN range maps (fig.~\ref{fig:gbif}). This indicates that the
-information we are missing for these two species is related to either an
-additional interaction or to the presence of interacting species. To
-illustrate that, we mapped the GBIF data for the prey
-of~\emph{Leptailurus serval}, with a mobility buffer around each point
-(fig.~\ref{fig:serval}). When considering GBIF data, approximately 42\%
-of the prey's occurrences are within the portion of the predator's range
-that was divergent from its original IUCN data. With the buffer area,
-this corresponds to 15\% of the mismatched area. By adding GBIF
-information for the prey, we could therefore reduce the discrepancy of
-the range (or information) for the predator by 15\% since its
-distribution is conditional on the occurrence of its preys. In other
-words, the range mismatch was exagerated because we were missing
+inside their original IUCN range maps (fig.~\ref{fig:gbif}). This
+indicates that the information we are missing for these two species is
+related to either an additional interaction or to the presence of
+external interacting species. To illustrate that, we mapped the GBIF
+data for the prey of~\emph{Leptailurus serval}, with a mobility buffer
+around each point (fig.~\ref{fig:serval}). When considering GBIF data,
+approximately 36\% of the prey's occurrences are within the portion of
+the predator's range that was divergent from its original IUCN data.
+With the buffer area, this corresponds to 5.57\% of the mismatched area.
+By adding GBIF information for the prey, we could therefore reduce the
+discrepancy of the range (or information) for the predator by 5.57\%
+since its distribution is conditional on the occurrence of its preys. In
+other words, the range mismatch was exagerated because we were missing
 information on the presence of an interacting species (i.e., this also
@@
 
-Here we demonstrated how we can detect uncertainty in species
+Here we demonstrated how we can detect areas of data deficit in species
 distribution data using ecological interactions. Knowing where
@@
 can improve model outputs by diminishing the error propagation (Draper
-1995). For instance, we believe this is a way to account for ecological
-interactions in habitat suitability models without making the models
-more complex, but by making sure (not assuming) that the input data -
-the species occurrence - actually accounts for ecological interactions.
+1995). For instance, we believe our method is a way to account for
+ecological interactions in habitat suitability models without making the
+models more complex, but by making sure (not assuming) that the input
+data - the species occurrence - actually accounts for ecological
+interactions. Another application of this method is mapping areas where
+data are deficient and helping to indicate priority sampling locations
+for interaction data, which can, in turn, reduce uncertainty in network
+prediction. For example, if a certain pixel confirms the presence of a
+species both with IUCN and GBIF data, but lacks connection between
+species, this pixel has a high potential to hide an unobserved
+interaction and should therefore be a priority sample location.\\
 It is important to notice, however, that the quality and usefulness of
@@
 Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak nations. We
-thank the editor and reviewer for their thoughtful comments, which
+thank the editor and reviewers for their thoughtful comments, which
 considerably improved this manuscript.

### 2022-11-28 response-letter.md
added line numbers

@@
 investigations show that most of the data we were using are recent (from the
-last 20 years). We describe the time distribution of GBIF records to explicit
-that. Finally, we have improved the methods and the discussion sections to
-include more detailed descriptions of the data being used and to give more
+last 20 years). We decided to add a threshold on the year 2000 and restrict the
+time extension of our query the same way we do for the geographical extension -
+not as a filtering step in terms of Ecology, but of likelyhood of getting the
+most accurate data. Any refined filtering other than that would hinder the goals
+of our paper. Finally, we have improved the methods and the discussion sections
+to include more detailed descriptions of the data being used and to give more
 context to the results. We detail specific changes below (line numbers refer to
@@
 
-To emphasize and clarify these points, we have changed lines XX, XX and XX on
+To emphasize and clarify these points, we have changed lines 83-86 and 171-175 on
 the manuscript.
@@
 include any filters other than the ones described on the paper for the reasons
-described above.
+listed above.
 
@@
 We agree and we have updated our rasters to be now at 50km of resolution. Our
-overall results did not change with that (see lines XX, XX and XX).
+overall results did not change with that (see line 125 and Results section,
+especially Table 1).
 
@@
 
+This is a very interesting comment and we have explored the temporal
+distribution of the GBIF records we have retrieved. As you can see below, most
+of the data is recent, from after the year 2000. This means that our previous
+results are very likely to represent our current state of biodiversity
+(considering a temporal autocorrelation effect). However, we agree that extinct
+populations could be a real problem for the validation step of our method, and
+therefore we decided to add a temporal restriction to our query. We have then
+re-run our analyses with only GBIF occurrences registered after the year 2000.
+Still, our results are overall the same. We have updated the absolute values on
+lines 212-215, 225-228, 259, 274-275, and 285-289.
+
+![](figures/GBIF_years_prop_nb_2000.png)
+
 We hope our revised manuscript is now more appropriate for publishing at PeerJ.

### 2022-11-28 code/00_get_rasters.jl
Squashed commit of the following:
commit 35da05d50653b26d918f0fb464c1c9d688b9c8e2
Merge: 44cf0d8 ce6380f
Author: Gracielle Higino <graciellehigino@hotmail.com>
Date:   Sat Nov 26 21:20:31 2022 -0800

    Merge pull request #93 from graciellehigino/gbif_dates

    ✨ More on GBIF dates

commit ce6380f0052526615ef2590c2b30ab9900f82dc6
Author: Francis Banville <francis.banville@umontreal.ca>
Date:   Fri Nov 25 15:08:06 2022 -0500

    ✨ minor fixes

commit 47763fd76ffaf71606f16243bfc2afed75061fb8
Merge: 0324763 44cf0d8
Author: Francis Banville <francis.banville@umontreal.ca>
Date:   Fri Nov 25 15:

@@ -1,8 +1,4 @@
-import Pkg; Pkg.activate(".")
-
-using SimpleSDMLayers
-using CSV
-using DataFrames
+include("A1_required.jl")
 
 # I store my IUCN data in the same location, so adapt this to where your files are
 const IUCNPATH = expanduser(joinpath("~", ".data", "iucn"))
@@ -15,8 +11,10 @@ ispath("rasters") || mkpath("rasters")
 bounding_box = (left=-20.0, right=55.0, bottom=-35.0, top=40.0)
 
 # Get the list of hosts
-speciespool = readlines(joinpath("data", "species.csv"))
-filter!(!endswith(" spp."), speciespool) # Species with spp. at the end are plants, so we can remove them
+# We remove plant species to focus only on mammals
+speciespool = DataFrame(CSV.File(joinpath("data", "species_code.csv")))
+filter!(:type => !=("plant"), speciespool)
+speciespool = speciespool[:,:species]
 
 # Rename species following IUCN taxonomy
 replace!(speciespool, "Damaliscus korrigum" => "Damaliscus lunatus", "Taurotragus oryx" => "Tragelaphus oryx")
@@ -29,7 +27,7 @@ Threads.@threads for i in 1:length(speciespool)
     @info "Extracting $(sp) on thread $(Threads.threadid())"
     fname = joinpath("rasters", replace(sp, " " => "_")*".tif")
     try
-        query = `gdal_rasterize -l "$(IUCNDB)" -a presence $(IUCNPATH)/$(IUCNDB)/$(IUCNDB).shp $(fname) -where "binomial LIKE '$(sp)'" -tr 0.1666666666666666574 0.1666666666666666574 -te -180.0 -90.0 180.0 90.0`
+        query = `gdal_rasterize -l "$(IUCNDB)" -a presence $(IUCNPATH)/$(IUCNDB)/$(IUCNDB).shp $(fname) -where "binomial LIKE '$(sp)'" -tr 0.5 0.5 -te -180.0 -90.0 180.0 90.0`
         run(query)
         mp = convert(Float64, geotiff(SimpleSDMResponse, fname; bounding_box...))
         replace!(mp, zero(eltype(mp)) => nothing)

### 2022-11-28 code/01-load_rasters.jl

@@ -1,9 +1,4 @@
-import Pkg; Pkg.activate("."); Pkg.instantiate()
-
-using SimpleSDMLayers
-using Plots
-using Shapefile
-using DataFrames
+include("A1_required.jl")
 
 # This is the bounding box we care about
 bounding_box = (left=-20.0, right=55.0, bottom=-35.0, top=40.0)
@@ -15,16 +10,11 @@ mammals = readlines(joinpath("data", "clean", "mammals.csv"))
 ranges = [geotiff(SimpleSDMPredictor, joinpath("data", "clean", "stack.tif"), i) for i in eachindex(mammals)]
 
 # Get species richness
-#= # Write to tif file
 richness = mosaic(sum, ranges)
 geotiff(joinpath("data", "clean", "richness.tif"), richness)
-=#
-# Read from tif file
-richness = geotiff(SimpleSDMPredictor, joinpath("data", "clean", "richness.tif"))
 
 # Map the richness
-include("shapefile.jl")
-plot(; 
+plot(;
     frame=:box,
     xlim=extrema(longitudes(richness)),
     ylim=extrema(latitudes(richness)),

### 2022-11-28 code/02-get_networks.jl

@@ -1,12 +1,5 @@
 # Load required scripts and packages
 include("01-load_rasters.jl") # range maps of Serengeti mammals
-include("shapefile.jl") # mapping functions
-
-import CSV
-using DataFrames
-using EcologicalNetworks
-using SparseArrays
-using Statistics
 
 #### Build metawebs
 
@@ -38,9 +31,13 @@ vals = ones(Bool, L)
 M = sparse(rows, cols, vals, S, S)
 M = UnipartiteNetwork(Matrix(M), sp.species)
 
+# Export trophic levels for later use
+trophic_df = DataFrame(species = collect(keys(trophic_level(M))), level = collect(values(trophic_level(M))))
+CSV.write(joinpath("data", "clean", "trophic_levels.csv"), trophic_df)
+
 # Get list of plants and mammals (carnivores and herbivores)
 plants = sp.species[sp.type .== "plant"]
-mammals = sp.species[sp.type .!== "plant"]
+mammals = sp.species[sp.type .!= "plant"]
 herbivores = sp.species[sp.type .== "herbivore"]
 carnivores = sp.species[sp.type .== "carnivore"]
 
@@ -52,13 +49,18 @@ end
 # Build metaweb of mammals (subnetwork of metaweb of mammals and plants)
 MM = M[mammals]
 
+# Export metaweb as DataFrame
+interactions_df = DataFrame(interactions(MM))
+rename!(interactions_df, :from => :pred, :to => :prey)
+CSV.write(joinpath("data", "clean", "metaweb.csv"), interactions_df)
+
 # Count the number of plants that are eaten by each herbivores
 M_plants_herb = M[vcat(plants, herbivores)]
 
 kout_plants_herb = collect(values(degree(M_plants_herb, dims = 1))) # out-degree of herbivores and plants
 kout_herb = kout_plants_herb[kout_plants_herb .!= 0] # out-degree of herbivores
 kout_herb_avg = mean(kout_herb) # mean out-degree of herbivores
-kout_herb_sd = std(kout_herb) 
+kout_herb_sd = std(kout_herb)
 kout_herb_ext = extrema(kout_herb)
 
 #### Build spatially-explicit networks of mammals and remove carnivores with no paths to an herbivore
@@ -194,6 +196,8 @@ Sxy_layer = SimpleSDMPredictor(Sxy_df, :Sxy, ranges[1])
[…]

### 2022-11-28 code/03-analyse_cooccurrence.jl

@@ -1,10 +1,5 @@
 include("02-get_networks.jl")
 
-using Combinatorics
-
-# Mammals in the Serengeti ecosystem
-mammals = readlines(joinpath("data", "clean", "mammals.csv"))
-
 # Subset subnetwork using this list of mammals
 MM = MM[mammals]
 

### 2022-11-28 code/06-GBIF_data.jl

@@ -1,98 +1,0 @@
-# Load required scripts and packages
-include("01-load_rasters.jl") # range maps of Serengeti mammals
-include("shapefile.jl") # mapping functions
-
-using CSV
-using GBIF
-using DataFramesMeta
-
-# Getting taxa codes
-sp_codes = taxon.(mammals, rank = :SPECIES)
-
-# Bounding box
-lat, lon = (bounding_box.bottom, bounding_box.top), (bounding_box.left, bounding_box.right)
-
-# Getting observations
-## Start query
-occ = occurrences.(
-    sp_codes,
-    "hasCoordinate" => "true",
-    "decimalLatitude" => lat,
-    "decimalLongitude" => lon,
-)
-## Loop to get all occurrences
-Threads.@threads for o in occ
-    while length(o) < size(o)
-        occurrences!(o)
-    end
-    @info "$(o.occurrences[1].taxon.name) occurrences returned ($(length(o))/$(size(o)))"
-end
-# Export to JLD2 for faster reload
-#=
-using JLD2
-@save joinpath("data", "clean", "gbif-occurrences.jld2") occ
-@load joinpath("data", "clean", "gbif-occurrences.jld2") occ
-=#
-
-## Create DataFrame
-
-# Make Data Frames
-occ_df = DataFrame.(occ)
-occ_df = reduce(vcat, occ_df)
-select!(occ_df, :species, :longitude, :latitude)
-occ_df.species = replace.(occ_df.species, " " => "_")
-
-# Remove observations with coordinates around (0.0, 0.0) which are outside mainland
-filter!(x -> !(x.latitude > -2.0 && x.latitude < 2.0 && x.longitude > -2.0 && x.longitude < 2.0), occ_df)
-
-# Make sure the species names match
-isequal(unique(occ_df.species), mammals) # not the same
-setdiff(unique(occ_df.species), mammals) # Taurotragus oryx is the difference
-
-id_mismatch = filter(x -> !(x.species in mammals), occ_df)
-unique(id_mismatch.species) # Yep it's only Taurotragus oryx
-# The GBIF website agrees it's a synonym of Tragelaphus oryx, citing IUCN as source, so we're good
-
-replace!(occ_df.species, "Taurotragus_oryx" => "Tragelaphus_oryx")
-isequal(unique(occ_df.species), mammals) # true
-
-# Save as CSV
-CSV.write(joinpath("data", "clean", "gbif_occurrences.csv"), occ_df)
-
[…]

### 2022-11-28 code/06-scatterplots.jl

@@ -1,8 +1,4 @@
-using Base: get_preferences
-using Plots.PlotMeasures
-
 include("05-degrees.jl")
-include("07-GBIF_comparison.jl")
 
 # Remove underscores
 ranges_degrees_df.species = replace.(ranges_degrees_df.species, "_" => " ")
@@ -90,7 +86,7 @@ scatter(
     xlabel="predator to prey geographic similarity",
     ylabel="prey to predator geographic similarity",
     group=ranges_degrees_df[0.0 .< ranges_degrees_df.Rbb .< 1.0, :species],
-    markershape=[:circle :star5 :diamond :star4 :cross :xcross :utriangle :ltriangle],
+    markershape=[:circle :star5 :diamond :star4 :pentagon :star7 :utriangle :ltriangle],
     markersize=6,
     palette = cgrad(:seaborn_colorblind)[[1, 3:9...]],
     markerstrokewidth=0,
@@ -145,7 +141,7 @@ scatter(
     ylabel="Relative loss of range",
     ylimits=(0,1.05),
     group=ranges_degrees_df.species,
-    markershape=[:circle :rect :star5 :diamond :star4 :cross :xcross :utriangle :ltriangle],
+    markershape=[:circle :rect :star5 :diamond :star4 :pentagon :star7 :utriangle :ltriangle],
     markersize=8,
     palette=:seaborn_colorblind,
     markerstrokewidth=0,
@@ -192,11 +188,11 @@ savefig(joinpath("figures", "outdegree-orig_range.png"))
 # Number of preys vs. original range - only predators
 scatter(
     ranges_degrees_df.degree,
-    ranges_degrees_df.old_range ./ 10^4;
+    ranges_degrees_df.old_range ./ 10^3;
     xlabel="Out degree of predators",
-    ylabel="Original range (x 10^4)",
+    ylabel="Original range (x 10³)",
     group=ranges_degrees_df.species,
-    markershape=[:circle :rect :star5 :diamond :star4 :cross :xcross :utriangle :ltriangle],
+    markershape=[:circle :rect :star5 :diamond :star4 :pentagon :star7 :utriangle :ltriangle],
     markersize=4,
     palette=:seaborn_colorblind,
     markerstrokewidth=0,
@@ -220,7 +216,7 @@ scatter(
     marker_z=log.(ranges_degrees_df.old_range),
     markercolor=:sun,
[…]

### 2022-11-28 code/07-updated_ranges.jl

@@ -1,13 +1,13 @@
-include("02-get_networks.jl")
+include("A1_required.jl")
 
 ## Load required data
 
 # Get ranges
 ranges = [geotiff(SimpleSDMPredictor, joinpath("data", "clean", "stack.tif"), i) for i in eachindex(mammals)]
+ranges_updated = [geotiff(SimpleSDMPredictor, joinpath("data", "clean", "ranges_updated.tif"), i) for i in eachindex(mammals)]
 
-# List interactions in DataFrame
-interactions_df = DataFrame(interactions(MM))
-rename!(interactions_df, :from => :pred, :to => :prey)
+# Get list interactions in DataFrame
+interactions_df = CSV.read(joinpath("data", "clean", "metaweb.csv"), DataFrame)
 
 # Separate predators & preys
 predators = unique(interactions_df.pred)
@@ -75,7 +75,7 @@ preds_updated = [ranges_updated_dict[sp] for sp in predators]
 
 # Get prey ranges
 preys_original = [ranges_dict[sp] for sp in preys]
-preys_updated = [update_range(ranges_dict, interactions_df, sp, :prey) for sp in preys]
+preys_updated = [update_range(ranges_dict, interactions_df, sp, :prey) for sp in string.(preys)]
 
 ## Produce table
 
@@ -110,9 +110,10 @@ missing_species_df = DataFrame(
 append!(results, missing_species_df; cols=:union)
 
 # Sort by trophic level
-results = leftjoin(results, DataFrame(species = species(M), trophic_levels = floor.(values(trophic_level(M)))), on = :species)
-sort!(results, :trophic_levels, rev=true)
-results = results[!, Not(:trophic_levels)]
+trophic_df = CSV.read(joinpath("data", "clean", "trophic_levels.csv"), DataFrame)
+results = leftjoin(results, trophic_df, on = :species)
+sort!(results, :level, rev=true)
+results = results[!, Not(:level)]
 
 # Export to CSV
 CSV.write(joinpath("data", "clean", "range_proportions.csv"), results)
@@ -131,8 +132,6 @@ plot(richness_updated, c=:turku)
 richness_diff = richness_original - replace(richness_updated, nothing => 0.0)
 
 plot(replace(richness_diff, 0.0 => nothing), c=:turku)
-plot(delta_Sxy_layer, c=:turku)
-replace(richness_diff, 0.0 => nothing) == delta_Sxy_layer # true if intermediate predators filtered earlier
 
 # Export nicer plot
 plot(;

### 2022-11-28 code/09-GBIF_data.jl

@@ -1,0 +1,125 @@
+include("A1_required.jl")
+
+# Load data
+occ_df = CSV.read(joinpath("data", "clean", "gbif_occurrences.csv"), DataFrame)
+
+
+## Keep recent GBIF occurrences only 
+year_recent = 2000 # all observations before this year will be discarded 
+
+# Get years
+occ_with_dates = dropmissing(occ_df, :date)
+occ_with_dates.year = year.(occ_with_dates.date)
+
+# Keep recent observations 
+occ_df_recent = subset(occ_with_dates, :year => ByRow(>(year_recent)))
+
+
+## Create layers
+
+# Create background layer
+bglayer = SimpleSDMPredictor(WorldClim, BioClim, 1; resolution=10.0, bounding_box...)
+bglayer = coarsen(bglayer, mean, (3, 3))
+
+# Create presence-absence layers
+gbif_ranges = fill(similar(bglayer), length(mammals))
+for i in eachindex(mammals)
+    spdf = filter(:species => ==(mammals[i]), occ_df_recent)
+    splayer = mask(bglayer, spdf, Bool)
+    replace!(splayer, false => nothing)
+    gbif_ranges[i] = convert(Float32, splayer)
+end
+gbif_ranges
+
+# Export to tif file
+geotiff(joinpath("data", "clean", "gbif_ranges.tif"), gbif_ranges)
+
+
+## Explore year distribution
+
+# Calculate median per species
+group_species = groupby(occ_with_dates, :species)
+median_species = combine(group_species, :year => StatsBase.median)
+
+
+# Plot the distribution of the occurrences' year of record for each species
+p = plot(layout = 32, size = (1200, 800), dpi= 600)
+
+for i in 1:32
+    plot!(group_species[i].year, subplot = i, title = replace(levels(occ_df.species)[i], "_" => " "), titlefontsize = 7,
+    seriestype = :histogram, legends = :none, fillcolor = "black", bins = :scott, xlims = extrema(occ_with_dates.year))
+    vline!([transpose(median_species.year_median)], linecolor = :red)
+end
+p
+
+savefig(joinpath("figures", "GBIF_years_total.png"))
+
+
+# Distribution of the occurrences' year > 1900 for each species
+occ_with_dates_1900 = subset(occ_with_dates, :year => ByRow(>(1900)))
+
+group_species_1900 = groupby(occ_with_dates_1900, :species)
[…]

### 2022-11-28 code/10-GBIF_comparison.jl

@@ -1,27 +1,6 @@
-## Load required scripts and packages
-import Pkg; Pkg.activate("."); Pkg.instantiate()
-
-using CSV
-using DataFrames
-using DataFramesMeta
-using GBIF
-using Latexify
-using Plots
-using Plots.PlotMeasures
-using Shapefile
-using Statistics
-using StatsPlots
-using SimpleSDMLayers
-
-include("shapefile.jl") # mapping functions
+include("A1_required.jl")
 
 ## Load required data
-
-# This is the bounding box we care about
-bounding_box = (left=-20.0, right=55.0, bottom=-35.0, top=40.0)
-
-# Get the list of mammals
-mammals = readlines(joinpath("data", "clean", "mammals.csv"))
 
 # Species list with types
 sp = DataFrame(CSV.File(joinpath("data", "species_code.csv")))
@@ -36,10 +15,19 @@ ranges_updated = [geotiff(SimpleSDMPredictor, joinpath("data", "clean", "ranges_
 occ_df = CSV.read(joinpath("data", "clean", "gbif_occurrences.csv"), DataFrame)
 gbif_ranges = [geotiff(SimpleSDMPredictor, joinpath("data", "clean", "gbif_ranges.tif"), i) for i in eachindex(mammals)]
 
+# Keep recent GBIF occurrences only 
+year_recent = 2000
+
+occ_with_dates = dropmissing(occ_df, :date)
+occ_with_dates.year = year.(occ_with_dates.date)
+
+occ_df_recent = subset(occ_with_dates, :year => ByRow(>(year_recent)))
+
+
 ## Get IUCN range values at GBIF occurrences
 
 # Separate occurrences per species
-spp_df = [filter(:species => ==(m), occ_df) for m in mammals];
+spp_df = [filter(:species => ==(m), occ_df_recent) for m in mammals];
 
 # Get values from IUCN layers at corresponding GBIF coordinates
 for (i, df) in enumerate(spp_df)
@@ -48,16 +36,16 @@ for (i, df) in enumerate(spp_df)
 end
 
 # Reassemble in single DataFrame
-occ_df = reduce(vcat, spp_df)
+occ_df_recent = reduce(vcat, spp_df)
 
 # Replace nothings by zeros before performing sum
-replace!(occ_df.IUCN, nothing => 0.0)
-replace!(occ_df.IUCN_updated, nothing => 0.0)
[…]

### 2022-11-28 code/11-GBIF_doublecheck.jl

@@ -1,15 +1,6 @@
-using SimpleSDMLayers
-using Plots
-using Plots.PlotMeasures
-using Shapefile
-using DataFramesMeta
-using GBIF
-using CSV
-using Statistics
-using StatsPlots
+include("A1_required.jl")
 
 # Load IUCN ranges
-mammals = readlines(joinpath("data", "clean", "mammals.csv"))
 ranges = [geotiff(SimpleSDMPredictor, joinpath("data", "clean", "stack.tif"), i) for i in eachindex(mammals)]
 ranges_updated = [geotiff(SimpleSDMPredictor, joinpath("data", "clean", "ranges_updated.tif"), i) for i in eachindex(mammals)]
 
@@ -63,7 +54,6 @@ prey_mismatch = similar(serval_loss)
 prey_mismatch[_prey_sites] = fill(1.0, length(_prey_sites))
 
 # Map the mismatch
-include("shapefile.jl")
 begin
     plot(;
         frame=:box,
@@ -83,6 +73,7 @@ savefig(joinpath("figures", "serval_prey_mismatch.png"))
 # Get the sites where the prey has GBIF observations _on land_
 _prey_sites2 = keys(prey_gbif_range)
 reference_layer = SimpleSDMPredictor(WorldClim, BioClim, 1; boundingbox(serval)...)
+reference_layer = coarsen(reference_layer, mean, (3, 3))
 prey_mismatch2 = similar(reference_layer)
 prey_mismatch2[_prey_sites2] = fill(1.0, length(_prey_sites2))
 
@@ -110,10 +101,10 @@ end
 savefig(joinpath("figures", "serval_prey_mismatch_buffered.png"))
 
 # What percentage of the range loss does the buffered range represent?
-sum(buffered)/length(buffered) # ~ 15%
+sum(buffered)/length(buffered) # ~ 6%
 
 # What percentage of the prey's GBIF observations are within the range loss?
-length(_prey_sites)/length(prey_gbif_range) # ~ 42%
+length(_prey_sites)/length(prey_gbif_range) # ~ 36%
 
 ## GBIF figure with the serval and it's prey only
 
@@ -134,7 +125,7 @@ options = (
     ylim=(-0.03, 1.0),
     xlim=(-0.2, 7),
     xticks=0:1:7,
-    markershape=[:cross :circle],
+    markershape=[:pentagon :circle],
     markersize=6,
     color=[cgrad(:seaborn_colorblind)[6] :lightgrey],
     markerstrokewidth=0,

### 2022-11-28 code/A1_required.jl

@@ -1,0 +1,30 @@
+## Load required scripts and packages
+import Pkg; Pkg.activate("."); Pkg.instantiate()
+
+using Combinatorics
+using CSV
+using DataFramesMeta
+using Dates
+using EcologicalNetworks
+using GBIF
+using GLM
+using JLD2
+using Latexify
+using Plots
+using Plots.PlotMeasures
+using Shapefile
+using SimpleSDMLayers
+using SparseArrays
+using Statistics
+using StatsBase
+using StatsPlots
+
+include("A2_shapefile.jl") # mapping functions
+
+## Objects needed in most scripts
+
+# This is the bounding box we care about
+bounding_box = (left=-20.0, right=55.0, bottom=-35.0, top=40.0);
+
+# Get the list of mammals
+mammals = readlines(joinpath("data", "clean", "mammals.csv"));

### 2022-11-28 response-letter.md
Squashed commit of the following:
commit 35da05d50653b26d918f0fb464c1c9d688b9c8e2
Merge: 44cf0d8 ce6380f
Author: Gracielle Higino <graciellehigino@hotmail.com>
Date:   Sat Nov 26 21:20:31 2022 -0800

    Merge pull request #93 from graciellehigino/gbif_dates

    ✨ More on GBIF dates

commit ce6380f0052526615ef2590c2b30ab9900f82dc6
Author: Francis Banville <francis.banville@umontreal.ca>
Date:   Fri Nov 25 15:08:06 2022 -0500

    ✨ minor fixes

commit 47763fd76ffaf71606f16243bfc2afed75061fb8
Merge: 0324763 44cf0d8
Author: Francis Banville <francis.banville@umontreal.ca>
Date:   Fri Nov 25 15:

@@
 
-Thank you for the inviting a specialist on large scale biodiversity patterns of
-Africa to review our manuscript. We were happy to see that the first reveiwer
+Thank you for inviting a specialist on large scale biodiversity patterns of
+Africa to review our manuscript. We were happy to see that the first reviewer
 was satisfied with our response, and that the second reviewer also saw value in
@@
 
-We have also addressed reviewer's concerns about the GBIF data (see below): our
+We have also addressed the reviewer's concerns about the GBIF data (see below): our
 investigations show that most of the data we were using are recent (from the
 last 20 years). We decided to add a threshold on the year 2000 and restrict the
-time extension of our query the same way we do for the geographical extension -
-not as a filtering step in terms of Ecology, but of likelyhood of getting the
+time extension of our query the same way we did for the geographical extension -
+not as a filtering step in terms of Ecology, but of likelihood of getting the
 most accurate data. Any refined filtering other than that would hinder the goals
-of our paper. Finally, we have improved the methods and the discussion sections
-to include more detailed descriptions of the data being used and to give more
+of our paper. Finally, we have improved the methods and discussion sections
+by including more detailed descriptions of the data being used and by giving more
 context to the results. We detail specific changes below (line numbers refer to
@@
 We have found that these two comments address the same issue: the
-representativity of the Serengeti foodweb. First, we would like to emphasize
+representativity of the Serengeti food web. First, we would like to emphasize
 that our analysis is meant to be a proof of concept, showing the consequences of
-data limitation. Therefore, rather than trying to gather an exhaustive foodweb
+data limitation. Therefore, rather than trying to gather an exhaustive food web
 dataset - with information for all possible interactions for all occurring
-mammals in the African continent -, we looked for a very complete, readily
+mammals in the African continent -, we looked for a complete, readily
 available, widely used and well known dataset which could represent the main
 interactions in that area. Interaction data is difficult to collect, especially
-at broad scales. Because of that, we expected that no foodweb would be complete,
+at broad scales. Because of that, we expected that no food web would be complete,
 and we are aware of the biases of our interactions data. However, the goal of
@@
 
-That being said, the foodweb database that we chose is known for being
+That being said, the food web dataset that we chose is known for being
 representative for these animals on the whole African continent (as we can see,
-for example, in de Visser, Freymann and Olff, 2011). Although our dataset miss a
-few links, again, it was not our goal to make a comprehensive analysis of all
-the area where a predator would miss a prey based on all the knowledge available
-or not, but rather demonstrate what can happen if we deal with incomplete
-datasets, highlight the importance of accounting for uncertainty when dealing
-with species distribution data, and call to attention the need to make more
+for example, in de Visser, Freymann and Olff, 2011). Even though our dataset misses a
+few interactions, again, it was not our goal to conduct a comprehensive analysis of all
+the areas where a predator would miss a prey based on all the knowledge available. Our goal was rather to demonstrate what can happen if we deal with incomplete
+datasets, to highlight the importance of accounting for uncertainty when dealing
+with species distribution data, and to call to attention the need to make more
 interaction data open. Moreover, many of the prey items on Baskerville's dataset
@@
 link connecting a predator to a herbivore to "keep" a pixel from a predator's
-range. Therefore, the impact of the missing links on the foodweb should be of
-great magnitude to invalidate our methods.
+range. Therefore, the impact of missing interactions on the food web should be of
+great magnitude to invalidate our method.
 
@@
 Similar to the questions above, this one is also about incompleteness of data.
-As we stated on our previous review letter, "we didn't perform any [...] data
+As we stated in our previous review letter, "we didn't perform any [...] data
 cleaning procedures because this could hinder the goals of the paper, which was
@@
 GBIF and IUCN datasets". For that reason, our query for the GBIF data did not
-include any filters other than the ones described on the paper for the reasons
+include any filters other than the ones described in the paper for the reasons
 listed above.
 
-Additionally, we could add a plethora of other datasets both on
+Additionally, we could have added a plethora of other datasets both on
 interactions and occurrences, but we decided to use only the IUCN, the GBIF and
@@
 undocumented data. We expect to call attention about this issue with our proof
-of concept, as it demonstrates that we gain a lot of uncertainty when we miss a
-link because of an information that is not accessible. The implications of this
+of concept, as it demonstrates that we gain a lot of uncertainty when we miss interactions because of inaccessible information. The implications of this
 complex issue for conservation are multifold, and we believe that more open data
@@
 
-We agree and we have updated our rasters to be now at 50km of resolution. Our
-overall results did not change with that (see line 125 and Results section,
+We agree and we have updated our rasters to be at 50km of resolution. Our
+overall results did not change qualitatively after fixing the resolution (see line 125 and Results section,
 especially Table 1).
@@
 distribution of the GBIF records we have retrieved. As you can see below, most
-of the data is recent, from after the year 2000. This means that our previous
-results are very likely to represent our current state of biodiversity
+of our data is recent, from after the year 2000. This means that our previous
+results are likely to represent the current state of biodiversity
 (considering a temporal autocorrelation effect). However, we agree that extinct
@@
 We hope our revised manuscript is now more appropriate for publishing at PeerJ.
-Reiterating our appreciation for yours and the reviewer's thoughtful comments,
+Reiterating our appreciation for yours and the reviewers' thoughtful comments,
 we are available to answer any further questions.

### 2022-11-28 draft.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@e2706f4558e88565b6a05ee9c0ed8967a5f7c59c 🚀
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@095143c312750503d13a65306e709771a9f87a1b 🚀

@@
 Serengeti food web of mammals and plants as our case study, and provide
-updated range maps for all predators by taking into account food-web
+updated range maps for all predators by taking into account food web
 structure. We then used occurrence data from the Global Biodiversity
@@
 Serengeti species to investigate whether the results would be different
-if we used another source of distribution data. \#\# Data
+if we used another source of distribution data.
+
+\hypertarget{data}{%
+\subsection{Data}\label{data}}
 

### 2022-11-28 preprint.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@e2706f4558e88565b6a05ee9c0ed8967a5f7c59c 🚀
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@095143c312750503d13a65306e709771a9f87a1b 🚀

@@
 mammals and plants as our case study, and provide updated range maps for
-all predators by taking into account food-web structure. We then used
+all predators by taking into account food web structure. We then used
 occurrence data from the Global Biodiversity Information Facility (GBIF)

### 2022-11-28 draft.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@d8c7546198bb9888afe23f7790b6b7e9dd3277a6 🚀

@@
 primary producers. \textbf{Methodology.} We used the well-described
-Serengeti food web of mammals and plants as our case study, and provide
-updated range maps for all predators by taking into account food web
-structure. We then used occurrence data from the Global Biodiversity
-Information Facility (GBIF) to investigate where data is most lacking.
-\textbf{Results.} We found that most predator ranges comprised large
-areas without any overlapping distribution of their preys. However, many
-of these areas contained GBIF occurrences of the predator.
-\textbf{Conclusions.} Our results suggest that the mismatch between both
-data sources could be due either to the lack of information about
-ecological interactions or the geographical occurrence of preys. We
-finally discuss general guidelines to help identify defective data among
-distributions and interactions data, and we recommend this method as a
-valuable way to assess whether the occurrence data that are being used,
-even if incomplete, are ecologically accurate.
+Serengeti food web of mammals and plants as our case study, and identify
+areas of data mismatch within predators' range maps by taking into
+account food web structure. We then used occurrence data from the Global
+Biodiversity Information Facility (GBIF) to investigate where data is
+most lacking. \textbf{Results.} We found that most predator ranges
+comprised large areas without any overlapping distribution of their
+preys. However, many of these areas contained GBIF occurrences of the
+predator. \textbf{Conclusions.} Our results suggest that the mismatch
+between both data sources could be due either to the lack of information
+about ecological interactions or the geographical occurrence of preys.
+We finally discuss general guidelines to help identify defective data
+among distributions and interactions data, and we recommend this method
+as a valuable way to assess whether the occurrence data that are being
+used, even if incomplete, are ecologically accurate.
 \vfill
@@
 approximate coordinates or lack of documentation about their accuracy),
-or sampling biases (e.g.~data clustered near roads or research centers)
+or sampling biases (e.g., data clustered near roads or research centers)
 (Ladle and Hortal 2013; Hortal et al. 2015; Poisot et al. 2021). One way
@@
 the overlapping ranges of its herbivore preys. If sections of a
-predator's range does not overlap with at least one of its prey it will
+predator's range do not overlap with at least one of its prey it will
 become disconnected from primary producers, and therefore we would not
@@
 disagreements between available data for species that compose a
-well-known foodweb in the African continent, discuss the mechanisms that
-can lead to this, and reinforce the importance of open geographically
-explicit interaction data.
+well-known food web in the African continent, discuss the mechanisms
+that can lead to this, and reinforce the importance of open
+geographically explicit interaction data.
 
@@
 
-We indentified areas of data deficits on the ranges of predators based
-on a simple rule: we removed any part of a predator's range that did not
+We identified areas of data deficits within the ranges of predators
+based on a simple rule: any part of a predator's range that did not
 intersect with the range of at least one prey herbivore species, which
-in turn is directly connected to a primary producer (plants). To do
-that, we used a Serengeti food web dataset (Baskerville et al. 2011)
-(which comprises carnivores, herbivores, and plants from Tanzania) and
-its species ranges from IUCN. Then, we calculated the difference in
-range sizes between the original IUCN ranges of predators and those
-without the areas where they would be alone, based on species
-interaction data. Finally, we added the GBIF occurrence points for the
-Serengeti species to investigate whether the results would be different
-if we used another source of distribution data.
+in turn is directly connected to a primary producer (plants), was
+considered data deficient. To do that, we used a Serengeti food web
+dataset (Baskerville et al. 2011) (which comprises carnivores,
+herbivores, and plants from Tanzania) and its species ranges from IUCN.
+Then, we calculated the difference in range sizes between the original
+IUCN ranges of predators and those without the areas where they would be
+disconnected from their food webs, based on species interaction data.
+Finally, we added the GBIF occurrence points for the Serengeti species
+to investigate whether the results would be different if we used another
+source of distribution data.
 
@@
 specialization (i.e., number of prey items per predator) affects the
-extent to which the ranges of the species were altered. One would assume
-that predators with a greater number of prey taxa (i.e., a higher
-generality) are less likely to have significant changes in their range
-as it is more likely that at least one prey species is present across
-most of their range.
+extent to which the ranges of the species comprised areas of data
+deficits. One would assume that predators with a greater number of prey
+taxa (i.e., a higher generality) are less likely to have large areas of
+data mismatch within their range as it is more likely that at least one
+prey species is present across most of their range.
 
@@
 We then converted the occurrence data into raster format by determining
-which pixels had a least one GBIF occurrence. This allowed us to remove
+which pixels had at least one GBIF occurrence. This allowed us to remove
 the effect of repeated sampling in some locations. These data were used
-to validate the range adjustments made based on species interactions
-(see beginning of Methods section). To do so, we calculated the
-proportion of GBIF presence pixels occurring within both the original
-IUCN species range and the adjusted one. We then compared these
-proportions for the predators to verify if the range adjustments removed
-locations with GBIF observations, hence likely true habitats.
+to validate the areas identified as being ecologically unrealistic based
+on species interactions and occurrence data (see beginning of Methods
+section). To do so, we calculated the proportion of GBIF presence pixels
+occurring within both the original IUCN species range and the adjusted
+one (i.e., the one without unrealistic food webs). We then compared
+these proportions for all predators to verify if the areas of data
+mismatch contained locations with GBIF observations, hence likely true
+habitats.
 
@@
 fig.~\ref{fig:richness}), which reinforces that the interactions we
-observe in the Serengeti foodweb is representative of the interactions
+observe in the Serengeti food web is representative of the interactions
 for these mammals in the whole African continent. On average, local food
@@
 \emph{Caracal caracal} lost 3.4\%; \emph{Acinonyx jubatus} and
-\emph{Panthera pardus} lost 6.2\%). On the other hand, three species,
-\emph{Canis aureus}, \emph{Canis mesomelas}, and \emph{Leptailurus
-serval} showed very high differences, with overlaps lowered by 100\%,
-58.4\%, and 100\% respectively. These last two species are also the only
-predators with a single prey in our metaweb. \emph{Canis aureus} has
-four preys, but it has one of the smallest ranges in IUCN, which is not
-covered by any of its preys. This result reinforces the concern raised
-in the literature on the use of IUCN range maps for species that are not
-well known (Herkt, Skidmore, and Fahr 2017), demonstrating how small
-range species are likely to have their distribution underestimated in
-the IUCN database. Additionally, the fact that \emph{Canis aureus} had
-such a conspicuous discrepancy between its original IUCN range and those
-of its preys, and between GBIF and IUCN data, may indicate a taxonomic
-incongruency between the three databases used here, which we explore in
-the Discussion section. Our results delineate how a mismatch between
-GBIF and IUCN databases differ greatly with small changes in herbivore
-species ranges, and it is somewhat positively related to range size for
-predator species. Moreover, we show that accounting for interactions
-does not necessarily aggravates this dissimilarity, but it is relevant
-for species about which we have little ecological information or for
-specialists groups.
+\emph{Panthera pardus} lost 6.2\%).
+
+On the other hand, three species, \emph{Canis aureus}, \emph{Canis
+mesomelas}, and \emph{Leptailurus serval} showed very high differences,
+with overlaps lowered by 100\%, 58.4\%, and 100\% respectively. These
+last two species are also the only predators with a single prey in our
+metaweb. \emph{Canis aureus} has four preys, but it has one of the
+smallest ranges in IUCN, which is not covered by any of its preys. This
+result reinforces the concern raised in the literature on the use of
+IUCN range maps for species that are not well known (Herkt, Skidmore,
+and Fahr 2017), demonstrating how small range species are likely to have
+their distribution underestimated in the IUCN database. Additionally,
+the fact that \emph{Canis aureus} had such a conspicuous discrepancy
+between its original IUCN range and those of its preys, and between GBIF
+and IUCN data, may indicate a taxonomic incongruency between the three
+databases used here, which we explore in the Discussion section. Our
+results delineate how a mismatch between GBIF and IUCN databases differ
+greatly with small changes in herbivore species ranges, and it is
+somewhat positively related to range size for predator species.
+Moreover, we show that accounting for interactions does not necessarily
+aggravates this dissimilarity, but it is relevant for species about
+which we have little ecological information or for specialists groups.
 
@@
 interactions when estimating the range of a species. Although this type
-of data mismatch can result of actual ecological processes, outdated
+of data mismatch can be result of actual ecological processes, outdated
 occurrence data, taxonomic errors and more, we argue that, here, they
@@
 First, \emph{Panthera leo} was one of the species with no difference
-between ranges before and after our analysis, but 50.7\% of its IUCN
-range map is not covered by the GBIF occurrences for this species, and
-26.4\% of the GBIF point data does not overlap with its IUCN range map
-(fig.~\ref{fig:gbif}). In this particular case, the IUCN maps seem to
-agree with species interaction data. However, the disagreement between
-the IUCN and the GBIF databases is concerning and suggests that the IUCN
-maps might overestimate the lion's distribution.
+between ranges before and after our analysis, but 50.7\% of its GBIF
+pixels did not superpose with the IUCN range (fig.~\ref{fig:gbif}). In
+this particular case, the IUCN maps seem to agree with species
+interaction data. However, the disagreement between the IUCN and the
+GBIF databases is concerning and suggests that the IUCN maps might
+underestimate the lion's distribution.
 
@@
 \includegraphics{figures/serval_mismatch_combined.png}
-\caption{Mismatch between serval's range loss and GBIF occurrence of its
-prey. The left panel shows the reduction of serval's range when we
-consider the IUCN data on its prey. On the right panel, we added GBIF
+\caption{Mismatch between servals' range loss and GBIF occurrence of its
+prey. The left panel shows the reduction of servals' range when we
+consider the IUCN data of its prey. On the right panel, we added GBIF
 data on both serval and its prey, with a buffer for the prey to account
@@
 interactions. Another application of this method is mapping areas where
-data are deficient and helping to indicate priority sampling locations
+data are deficient, thus helping to identify priority sampling locations
 for interaction data, which can, in turn, reduce uncertainty in network
@@
 species, this pixel has a high potential to hide an unobserved
-interaction and should therefore be a priority sample location.\\
+interaction and should therefore be a priority sampling location.\\
 It is important to notice, however, that the quality and usefulness of
@@
 A promising avenue that adds to our method is the prediction of networks
-and interactions in large scales (Strydom et al. 2021; Windsor et al.
+and interactions at large scales (Strydom et al. 2021; Windsor et al.
 2022), for they can add valuable information about ecological

### 2022-11-28 preprint.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@d8c7546198bb9888afe23f7790b6b7e9dd3277a6 🚀

@@
 \textbf{Methodology.} We used the well-described Serengeti food web of
-mammals and plants as our case study, and provide updated range maps for
-all predators by taking into account food web structure. We then used
-occurrence data from the Global Biodiversity Information Facility (GBIF)
-to investigate where data is most lacking. \textbf{Results.} We found
-that most predator ranges comprised large areas without any overlapping
-distribution of their preys. However, many of these areas contained GBIF
-occurrences of the predator. \textbf{Conclusions.} Our results suggest
-that the mismatch between both data sources could be due either to the
-lack of information about ecological interactions or the geographical
-occurrence of preys. We finally discuss general guidelines to help
-identify defective data among distributions and interactions data, and
-we recommend this method as a valuable way to assess whether the
-occurrence data that are being used, even if incomplete, are
-ecologically accurate.
+mammals and plants as our case study, and identify areas of data
+mismatch within predators' range maps by taking into account food web
+structure. We then used occurrence data from the Global Biodiversity
+Information Facility (GBIF) to investigate where data is most lacking.
+\textbf{Results.} We found that most predator ranges comprised large
+areas without any overlapping distribution of their preys. However, many
+of these areas contained GBIF occurrences of the predator.
+\textbf{Conclusions.} Our results suggest that the mismatch between both
+data sources could be due either to the lack of information about
+ecological interactions or the geographical occurrence of preys. We
+finally discuss general guidelines to help identify defective data among
+distributions and interactions data, and we recommend this method as a
+valuable way to assess whether the occurrence data that are being used,
+even if incomplete, are ecologically accurate.
 
